### 2018-06-21 prelim/outline.tex
working on prelim outline

\documentclass{article}
\usepackage{graphicx}
\usepackage{color}
\title{Prelim Outline (ROUGH)}
\author{Shivesh Pathak}

\begin{document}
\maketitle

\color{red} Red \color{black} is incomplete preliminary work.
\color{blue} Blue \color{black} is work for the future.

\section{Motivation/Background}
\begin{enumerate}
\item People want to construct an accurate low-energy model Hamiltonian for the cuprates.
\item Hole doped cuprates have been studied for a long time and have many degrees of freedom: O p and Cu d orbitals both play roles.
\item Electron doped cuprates are less studied and we believe they are simpler since only the Cu d orbitals play a major role.
\item We plan on building an low-energy model for the electron doped cuprate SrCuO$_2$ using a density-matrix downfolding method and accurate many-body QMC calculations.
\end{enumerate}

\section{Preliminary SCF calculations}
\subsection{Undoped (x=0)}
\begin{enumerate}
\item We did eight unit cell PBE0 calculations to calculate the energies of states with singly occupied Cu d$_{x^2-y^2}$ orbitals but with different spin textures.

\item We mapped these states onto spin-1/2 local moment states and used to fit to an AFM Heisenberg model:
$$H_m = J\sum_{ij} \frac{1}{2} \vec{S_i}\cdot\vec{S_j} $$

\item The results of this fitting on seven different spin textures yields good results for two different basis sets (BFD Cutoff, BFD PBC 0.2)

\item The high $R^2$ values of these fits indicate that a simple AFM Heisenberg model should be sufficient to capture the low-energy behavior of the undoped cuprates.
\end{enumerate}

\includegraphics[width=0.5\textwidth]{../undoped/PBE0_8/J_fit_naive.pdf}
\includegraphics[width=0.5\textwidth]{../undoped/PBE0_8/J_fit_naive_BFD0p2.pdf}

\subsection{Overdoped (x=0.25)}
\begin{enumerate}
\item We similarly did seventeen x=0.25 doped calculations in PBE0, from we got four low energy states. Here low-energy is defined as states with energy less than 0.3 eV from the lowest energy state we had, a collinear doped state.

\item We then used the band structures and energies of these four low energy states to fit to a naive model with $t, t^\prime, K, J$ parameters: NN-hopping, NNN-hopping, NN-Kondo term, and NN-Heisenberg-AFM term

$$H_m =  -t\sum_{\langle i, j \rangle, \sigma} (c_{i\sigma} ^\dagger c_{j\sigma} + h.c.) + 
t^\prime\sum_{\langle\langle i, j \rangle\rangle, \sigma} (c_{i\sigma} ^\dagger c_{j\sigma} + h.c.) + $$ 
$$K \sum_{\langle i, j \rangle} \vec{S_i} \cdot c_{j\alpha}^\dagger \vec{\sigma}_{\alpha \beta} c_{j\beta} + J\sum_{ij} \frac{1}{2} \vec{S_i}\cdot\vec{S_j} $$

\item The presence of $t, t^\prime$ parameters were necessary to get the correct curvature of bands near the Fermi level, and the $K, J$ parameters were necessary to get both the spacing between bands (K) and the total energies (K,J).

\item We map each of the PBE0 states into the model Hilbert space by breaking the occupied bands into a) fully occupied and b) partially occupied. The orbitals from a) then build a spin density that defines the variables $\vec{S_i}$ and the orbitals from b) define the variables $c_i^\dagger$.

\item We can therefore create a single body  Hamiltonian where we treat the spins $\vec{S_i}$ as a fixed background upon which the itenerant $c_i^\dagger$ electrons can move. We can solve this model Hamiltonian and fit to the PBE0 band structure, and also compare the total energy of the model to the PBE0 total energy.

\item We use a prior where $J$ is held as the undoped value. This is because in a metallic/superconducting doped state, there are charge fluctuations locally. Therefore we expect that on average the total charge locally between nearest neighbors will be the undoped value, and since the Heisenberg model only has local coupling we don't imagine $J$ should change too much.

\item Since we are fitting to two different quantities (total energy and band structure) we used a Pareto efficiency analysis to get the best balance between a fit to total energy and a fit to band structure. The cost function is shown below, and $w_E$ varies in the plot shown even lower for the two different basis sets from before.

$$Cost = w_E|E_m - E_{PBE0}|^2 + \sum_{|k|\le k_F} |e_{m,k} - e_{PBE0,k}|^2$$

\item We find that the most efficient point is at the blue square on the Pareto plot. Below we plot the fit to the band structure and comparison of the model and PBE0 total energies.

\includegraphics[width=0.5\textwidth]{../doped_fv/PBE0_8/tb_fit/pareto4.pdf}
\linebreak
\color{red} Need to include plot for PBC 0.2 basis set.

\color{black}

\item For the BFD cutoff basis set we get the parameter values $t,t^\prime,K,J=  1.04, 0.53, -0.15, 0.18 eV$

\item The two basis sets do not agree quantitatively, but this isn't too unexpected because it's such a rough fitting method, but qualitatively they do: AFM J, FM K, repulsive NNN hopping, attractive NN hopping.

\includegraphics[width=\textwidth]{../doped_fv/PBE0_8/tb_fit/pareto4_high.pdf}
\color{red} Need to include plot for PBC 0.2 basis set.
\end{enumerate}

\subsection{Optimally doped (x=0.125)}
\color{red} Need to do these calculations, but analysis is identical to above.

\color{black}
\section{Density matrix downfolding (DMD) calculations}
\subsection{Basis}

\begin{enumerate}
\item In order to do our DMD calculations we need a single particle basis to evaluate the density matrix on.  We use intrinsic atomic orbitals (IAOs) as our one particle basis. Justification for this choice is provided below.

\item \textbf{Undoped (x=0)}]
\begin{enumerate}
\item Shown below are the occupations of different IAOs for the checkerboard spin texture for the BFD Cutoff and BFD PBC 0.2 basis sets.

\item Clearly the IAOs show that the primary variation between occupation is in the $3d_{x^2-y^2}$ orbital, namely the spin changes from site to site. The oxygen orbitals do not play a significant role, indicating that this basis captures the qualitative features that we expect from the undoped state.

\item Another important feature is that for each copper atom there are TWO $3d_{x^2-y^2}$ IAOs: one for the occupied spin and one of the unoccupied spin.

\end{enumerate}
\includegraphics[width=0.5\textwidth]{../undoped/PBE0_8/CHK/dens_iao2_cu.pdf}
\linebreak
\color{red} Need to include plot for PBC 0.2 basis set.

\color{black}
\item \textbf{Overdoped (x=0.25)}
\begin{enumerate}
\item For the doped calculation, we did the same IAO analysis as for the x=0 case. We found that again the $3d_{x^2-y^2}$ orbital has the primary variation in occupation.

\item Unlike the x=0 case, once doped the occupation number changes as well as the spin. Below is shown the difference in occupation of the spin-down and spin-up $3d_{x^2-y^2}$ orbitals of the doped collinear state compared to the UNDOPED collinear state.

\item We see that the occupation of the dominant primary channel does not vary, and we can therefore attribute those orbitals to the fixed magnetic moments, and the secondary spin channel does vary and we can attribute those orbitals to the itinerant electrons.

\includegraphics[width=0.5\textwidth]{../doped_fv/PBE0_8/COL0/iao/sub_occd.pdf}
\linebreak
\color{red} Need to include plot for PBC 0.2 basis set.

\color{black}
\item Therefore we see that the basis elements we will be constructing our DM out of are the two different $3d_{x^2-y^2}$ IAOs: the orbital corresponding to the primary spin channel will be used to calculate DM elements of the fixed spin moments $\vec{S_i}$ and the secondary spin channel IAO will be used to calculate DM elements of the itinerant electrons $c_i^\dagger$
\end{enumerate}

\item \textbf{Optimally doped (x=0.125)}
\color{red} Need to do this, should be identical analysis to x=0.25.
\end{enumerate}

\color{blue}
\subsection{States}
\begin{enumerate}
\item \textbf{Undoped (x=0)} For the undoped calculations, we have seven different spin textures. We can just use these for the model fitting since we will be fitting to a single parameter, $J$.

\item \textbf{Overdoped (x=0.25)}
\begin{enumerate}
\item We have four low energy states for x=0.25. We will use these four states, as well as states that are singles (maybe double) excitations above these four states. Only states with energy lower than our cutoff will be used.
\item We can also take linear combinations of states with singles and double excitations. This can help us generate many more states and also increase our fitting efficiency since we can then make use of parameter derivatives w.r.t the determinant coefficients.
\end{enumerate}

\color{red}
\item \textbf{Optimally doped (x=0.125)}
\begin{enumerate}
\item Need to do this, should be similar.
\end{enumerate}
\color{blue}
\end{enumerate}

\subsection{K-points}
\begin{enumerate}
\item \textbf{Undoped (x=0)} For the undoped calculations, a $\Gamma$ point calculation should be sufficient to resolve any finite size effects because we have a large unit cell for calculation and the system is strongly insulating.

\item \textbf{Doped (x=0.25, 0.125)}
\begin{enumerate}
\item For the doped calculations our first goal will be to do calculations just on the $\Gamma$ point, since this should give us a good sense of whether the model we are interested in makes sense or not.

\item We can consider doing other k-point (twist boundary) calculations if we think that the finite size errors on the calculations at a single twist are too large.
\end{enumerate}
\end{enumerate}

\subsection{QMC workflow}
for x=0, 0.125, 0.25 \\
\indent for k-points from section (3) \\ 
\indent \indent for states from section (2) \\
\indent \indent \indent Take lowest energy Slater det, variance optimize Jastrow;\\
\indent \indent \indent use this Jastrow for all following calculations
\\

\indent \indent \indent Calculate 1/2-RDM and quantities for parameter derivative fitting \\ 
\indent \indent \indent using FN-DMC for basis elements in section (1)\\

\noindent Conduct fitting to $t,t^\prime, K,J$ model using DMD method with parameter derivative fitting. \\

\noindent Alter k-points, states from sections (3) and (2) as necessary for calculation.

\end{document}

### 2018-07-17 prelim/outline.tex
Outline cleaned, ready to discuss with lucas

@@
 \usepackage{color}
-\title{Prelim Outline (ROUGH)}
+\title{Prelim Outline}
 \author{Shivesh Pathak}
@@
 
-\color{red} Red \color{black} is incomplete preliminary work.
-\color{blue} Blue \color{black} is work for the future.
+Text in \color{blue} blue \color{black} are things that need to be planned.
 
@@
 \begin{enumerate}
-\item People want to construct an accurate low-energy model Hamiltonian for the cuprates.
-\item Hole doped cuprates have been studied for a long time and have many degrees of freedom: O p and Cu d orbitals both play roles.
-\item Electron doped cuprates are less studied and we believe they are simpler since only the Cu d orbitals play a major role.
+\item We want to construct an accurate low-energy model Hamiltonian for the cuprates.
+\item Hole doped cuprates have been studied for a long time, and the relevant degrees of freedom are both O p and Cu d orbitals. 
+\item Electron doped cuprates are less studied and we believe they are simpler since the O p orbitals should play a much smaller role.
 \item We plan on building an low-energy model for the electron doped cuprate SrCuO$_2$ using a density-matrix downfolding method and accurate many-body QMC calculations.
@@
 
-\section{Preliminary SCF calculations}
+\section{Preliminary calculations: DFT}
 \subsection{Undoped (x=0)}
 \begin{enumerate}
-\item We did eight unit cell PBE0 calculations to calculate the energies of states with singly occupied Cu d$_{x^2-y^2}$ orbitals but with different spin textures.
+\item We did eight unit cell DFT calculations with a PBE0 functional to calculate the energies of states with singly occupied Cu d$_{x^2-y^2}$ orbitals but with different spin textures.
 
@@
 
-\item The results of this fitting on seven different spin textures yields good results for two different basis sets (BFD Cutoff, BFD PBC 0.2)
+\item The results of this fitting on seven different spin textures yields good results for two different basis sets (BFD Cutoff, BFD PBC 0.2).
 
-\item The high $R^2$ values of these fits indicate that a simple AFM Heisenberg model should be sufficient to capture the low-energy behavior of the undoped cuprates.
+\item For every SCF calculation done the BFD PBC 0.2 basis set had higher total energy than the BFD Cutoff, so I will only present results for the Cutoff basis set.
+
+\item The high $R^2$ values of the fit indicates that a simple AFM Heisenberg model should be sufficient to capture the low-energy behavior of undoped SrCuO$_2$.
 \end{enumerate}
@@
 \includegraphics[width=0.5\textwidth]{../undoped/PBE0_8/J_fit_naive.pdf}
-\includegraphics[width=0.5\textwidth]{../undoped/PBE0_8/J_fit_naive_BFD0p2.pdf}
 
@@
 \begin{enumerate}
-\item We similarly did seventeen x=0.25 doped calculations in PBE0, from we got four low energy states.
-Here low-energy is defined as states with energy less than 0.3 eV from the lowest energy state we had, a collinear doped state.
+\item We similarly did seventeen x=0.25 doped calculations in PBE0, from which we got four low energy states.
 
-\item We then used the band structures and energies of these four low energy states to fit to a naive model with $t, t^\prime, K, J$ parameters: NN-hopping, NNN-hopping, NN-Kondo term, and NN-Heisenberg-AFM term
+\item Similarly to the x=0 calculations, the x=0.25 PBE0 calculations yielded lower total energy for the BFD Cutoff basis. All results shown are for that basis.
+
+\item Low-energy is defined as states with energy less than 0.3 eV from the lowest energy state we had, a collinear doped state.
+
+\item We used the band structures and total energies of these four low energy states to fit to a naive model with $t, t^\prime, K, J$ parameters: NN-hopping, NNN-hopping, NN-Kondo term, and NN-Heisenberg-AFM term
 
@@
 
-\item The presence of $t, t^\prime$ parameters were necessary to get the correct curvature of bands near the Fermi level, and the $K, J$ parameters were necessary to get both the spacing between bands (K) and the total energies (K,J).
+\item We map each of the PBE0 states into the model Hilbert space by breaking the occupied bands into a) fully occupied and b) partially occupied.
 
-\item We map each of the PBE0 states into the model Hilbert space by breaking the occupied bands into a) fully occupied and b) partially occupied.
-The orbitals from a) then build a spin density that defines the variables $\vec{S_i}$ and the orbitals from b) define the variables $c_i^\dagger$.
+\item The orbitals from a) then build a spin density that defines the variables $\vec{S_i}$ and the orbitals from b) define the variables $c_i^\dagger$.
 
-\item We can therefore create a single body  Hamiltonian where we treat the spins $\vec{S_i}$ as a fixed background upon which the itenerant $c_i^\dagger$ electrons can move.
-We can solve this model Hamiltonian and fit to the PBE0 band structure, and also compare the total energy of the model to the PBE0 total energy.
+\item We then create a single body  Hamiltonian where we treat the spins $\vec{S_i}$ as a fixed background upon which the itinerant $c_i^\dagger$ electrons can move.
 
-\item We use a prior where $J$ is held as the undoped value.
-This is because in a metallic/superconducting doped state, there are charge fluctuations locally.
-Therefore we expect that on average the total charge locally between nearest neighbors will be the undoped value, and since the Heisenberg model only has local coupling we don't imagine $J$ should change too much.
+\item We solve this model Hamiltonian and fit to the PBE0 band structure and further compare the total energy of the model to the PBE0 total energy.
 
-\item Since we are fitting to two different quantities (total energy and band structure) we used a Pareto efficiency analysis to get the best balance between a fit to total energy and a fit to band structure.
-The cost function is shown below, and $w_E$ varies in the plot shown even lower for the two different basis sets from before.
+\item Since we are fitting to two different quantities we used a Pareto efficiency analysis to get the best balance between a fit to total energy and a fit to band structure.
+
+\item The cost function is shown below, and $w_E$ varies in the plot shown below.
 
@@
 
+\item In the fitting we hold the value of $J=0.178$ eV fixed as a prior, which is the optimal value from the x=0 fit. \textcolor{red}{Why?}
+
 \item We find that the most efficient point is at the blue square on the Pareto plot. Below we plot the fit to the band structure and comparison of the model and PBE0 total energies.
 
-\includegraphics[width=0.5\textwidth]{../doped_fv/PBE0_8/tb_fit/pareto4.pdf}
+\includegraphics[width=0.5\textwidth]{../doped_fv/PBE0_8/tb_fit_0p25/pareto4.pdf}
 \linebreak
-\color{red} Need to include plot for PBC 0.2 basis set.
 
@@
 
-\item For the BFD cutoff basis set we get the parameter values $t,t^\prime,K,J=  1.04, 0.53, -0.15, 0.18 eV$
+\item The parameter values at this point on the Pareto plot are $t,t^\prime,K,J=  1.04, 0.53, -0.15, 0.178 $eV.
 
-\item The two basis sets do not agree quantitatively, but this isn't too unexpected because it's such a rough fitting method, but qualitatively they do: AFM J, FM K, repulsive NNN hopping, attractive NN hopping.
+\item Below is a figure with a fit to the total energies and band structure.
 
-\includegraphics[width=\textwidth]{../doped_fv/PBE0_8/tb_fit/pareto4_high.pdf}
-\color{red} Need to include plot for PBC 0.2 basis set.
+\includegraphics[width=0.7\textwidth]{../doped_fv/PBE0_8/tb_fit_0p25/pareto4_low.pdf}
 \end{enumerate}
 
-\subsection{Optimally doped (x=0.125)}
-\color{red} Need to do these calculations, but analysis is identical to above.
+\subsection{(Near) optimally doped (x=0.125)}
+\begin{enumerate}
+\item The fitting for x=0.125 is identical to x=0.25 except that the states in PBE0 we use are different.
 
-\color{black}
+\item As we had for the x=0.25 calculation, we got four low energy states for x=0.125, and all results below are for the BFD Cutoff basis.
+
+\item Below is the Pareto efficiency plot using the four low energy x=0.125 states and using the cost function from before. The blue square is the point we chose as most efficient.
+
+\includegraphics[width=0.5\textwidth]{../doped_fv/PBE0_8/tb_fit_0p125/pareto4.pdf}
+\linebreak
+
+\item The parameter values at this point on the Pareto plot are $t,t^\prime,K,J=  1.15,  0.39, -0.29, 0.18 $eV.
+
+\item Below is a figure with a fit to the total energies and band structure.
+
+\includegraphics[width=0.7\textwidth]{../doped_fv/PBE0_8/tb_fit_0p125/pareto4_sel.pdf}
+\end{enumerate}
+
+\subsection{Conclusions}
+\begin{enumerate}
+\item Fitting to our PBE0 results provides some evidence that our low energy model with four terms $t, t^\prime, K, J$ may describe the low energy Hilbert space of SrCuO$_2$ accurately.
+
+\item The table below shows the variation in the model parameters under doping, in eV.
+
+\begin{center}
+\begin{tabular}{ c c c c c }
+Doping & t & t$^\prime$ & K & J \\ 
+\hline
+x=0 & 0 & 0 & 0 & 0.178 \\
+x=0.125& 1.15&  0.39& -0.29& 0.178 \\
+x=0.25 & 1.04& 0.53& -0.15&0.178 \\
+\end{tabular}
+\end{center}
+
+\item This fitting was preliminary and is not a systematic or rigorous fitting procedure.
+
+\item My thesis project will be based to use the density matrix downfolding procedure to conduct a more rigorous version of model fitting.
+\end{enumerate}
+
 \section{Density matrix downfolding (DMD) calculations}
@@
 \begin{enumerate}
-\item In order to do our DMD calculations we need a single particle basis to evaluate the density matrix on.
-We use intrinsic atomic orbitals (IAOs) as our one particle basis.
-Justification for this choice is provided below.
+\item In order to do our DMD calculations we need a single particle basis to evaluate the density matrix on.  We use intrinsic atomic orbitals (IAOs) as our one particle basis.
 
@@
 \begin{enumerate}
-\item Shown below are the occupations of different IAOs for the checkerboard spin texture for the BFD Cutoff and BFD PBC 0.2 basis sets.
+\item Shown below are the occupations of different IAOs for the checkerboard spin textured PBE0 state.
 
-\item Clearly the IAOs show that the primary variation between occupation is in the $3d_{x^2-y^2}$ orbital, namely the spin changes from site to site.
-The oxygen orbitals do not play a significant role, indicating that this basis captures the qualitative features that we expect from the undoped state.
+\item The IAOs show that the primary variation between occupation is in the spin of an unpaired electron in the $3d_{x^2-y^2}$ orbital.
 
-\item Another important feature is that for each copper atom there are TWO $3d_{x^2-y^2}$ IAOs: one for the occupied spin and one of the unoccupied spin.
+\item The oxygen orbitals do not play a significant role.
+
+\item Another important feature is that for each copper atom there are TWO $3d_{x^2-y^2}$ IAOs: one for the majority spin and one of the minority spin.
 
@@
 \linebreak
-\color{red} Need to include plot for PBC 0.2 basis set.
 
-\color{black}
 \item \textbf{Overdoped (x=0.25)}
 \begin{enumerate}
-\item For the doped calculation, we did the same IAO analysis as for the x=0 case. We found that again the $3d_{x^2-y^2}$ orbital has the primary variation in occupation.
+\item For the doped calculation, we did the same IAO analysis as for the x=0 case.
 
 \item Unlike the x=0 case, once doped the occupation number changes as well as the spin.
-Below is shown the difference in occupation of the spin-down and spin-up $3d_{x^2-y^2}$ orbitals of the doped collinear state compared to the UNDOPED collinear state.
 
-\item We see that the occupation of the dominant primary channel does not vary, and we can therefore attribute those orbitals to the fixed magnetic moments, and the secondary spin channel does vary and we can attribute those orbitals to the itinerant electrons.
+\item Below is shown the difference in occupation of the spin-down and spin-up $3d_{x^2-y^2}$ orbitals of the doped collinear state MINUS to the undoped collinear state.
+
+\item The occupation of the dominant primary channel does not vary but that of the the secondary spin channel does.
+
+\item We can therefore attribute the prior orbitals to to the fixed magnetic moments and the latter to the itinerant electrons.
 
 \includegraphics[width=0.5\textwidth]{../doped_fv/PBE0_8/COL0/iao/sub_occd.pdf}
+
+\item We find that the majority spin IAOs relax in a localized manner with on site $d_{x^2-y^2}$ character, while the minority spin IAOs relax with $O p$ character across the calculation cell.
+
+\includegraphics[width=0.5\textwidth]{../doped_fv/PBE0_8/COL0/iao/DIFF_0_10.pdf} 
 \linebreak
-\color{red} Need to include plot for PBC 0.2 basis set.
 
-\color{black}
-\item Therefore we see that the basis elements we will be constructing our DM out of are the two different $3d_{x^2-y^2}$ IAOs: the orbital corresponding to the primary spin channel will be used to calculate DM elements of the fixed spin moments $\vec{S_i}$ and the secondary spin channel IAO will be used to calculate DM elements of the itinerant electrons $c_i^\dagger$
+\includegraphics[width=0.5\textwidth]{../doped_fv/PBE0_8/COL0/iao/DIFF_0_810.pdf}
+
+\item The orbital corresponding to the primary spin channel will be used to calculate DM elements of the fixed spin moments $\vec{S_i}$ and the secondary spin channel IAO will be used to calculate DM elements of the itinerant electrons $c_i^\dagger$
 \end{enumerate}
@@
 \item \textbf{Optimally doped (x=0.125)}
-\color{red} Need to do this, should be identical analysis to x=0.25.
+\begin{enumerate}
+\item The IAO analysis yields the same conclusions as the overdoped case.
+
+\item Shown below is the difference in occupation of the spin-down and spin-up 3$d_{x^2-y^2}$ orbitals of the doped flip state MINUS the undoped flip state.
+
+\includegraphics[width=0.5\textwidth]{../doped_fv/PBE0_8/FLP1/iao/sub_occd.pdf}
+\linebreak
+
+\includegraphics[width=0.5\textwidth]{../doped_fv/PBE0_8/FLP1/iao/DIFF_0_50.pdf} 
+\linebreak
+
+\includegraphics[width=0.5\textwidth]{../doped_fv/PBE0_8/FLP1/iao/DIFF_0_850.pdf}
+
+\end{enumerate}
 \end{enumerate}
@@
 \color{blue}
-\subsection{States}
+\subsection{Low energy states}
 \begin{enumerate}
@@
 
-\color{red}
-\item \textbf{Optimally doped (x=0.125)}
+\item \textbf{(Near) optimally doped (x=0.125)}
 \begin{enumerate}
-\item Need to do this, should be similar.
+\item Same as x=0.25.
 \end{enumerate}
-\color{blue}
 \end{enumerate}

### 2018-07-17 doped_fv/PBE0_8/tb_fit_0p25/tb_fit.py
Outline cleaned, ready to discuss with lucas

@@ -632,7 +632,7 @@ print(r23j(t,tt,K,J,b))
 
 ################################################################################3
 #FOUR STATE ENERGY RUN
-
+'''
 constraints=({'type':'eq','fun':lambda p: p[3]-0.18})
 res=scipy.optimize.minimize(lambda p: cost4j(p[0],p[1],p[2],p[3],p[4]),(2.0,1.0,-0.5,0.18,0.0),constraints=constraints)
 #res=scipy.optimize.minimize(lambda p: cost4j(p[0],p[1],p[2],p[3],p[4]),(2.0,1.0,0.01,0.40,0.0))
@@ -641,6 +641,7 @@ print(res.x)
 print(r24j(t,tt,K,J,b))
 plot4j(t,tt,K,J,b)
 plt.show()
+'''
 
 #BEST ENERGY, NO PRIOR; R2=1.0
 #t,tt,K,J,b=[ 1.99316482,  1.10664349 ,-0.15530005 , 0.34752776  ,0.        ]
@@ -961,8 +962,8 @@ pareto5=np.array(pareto5)
 
 
 plt.plot(pareto4[:,0],pareto4[:,1],'go')
-plt.plot(pareto5[:,0],pareto5[:,1],'ro')
-plt.plot(0.636712023352, 0.993108294582,'bs')
+#plt.plot(pareto5[:,0],pareto5[:,1],'ro')
+#plt.plot(0.636712023352, 0.993108294582,'bs')
 plt.plot(0.939456821809, 0.915352293528,'bs')
 plt.title("4-state Pareto")
 plt.xlabel("R^2 band")

### 2018-07-31 prelim/outline.tex
Prelim outline for introduction and methods complete

--- 2018-06-21 prelim/outline.tex
@@
 \documentclass{article}
-\usepackage{graphicx}
-\usepackage{color}
-\title{Prelim Outline (ROUGH)}
+\title{Prelim Outline}
 \author{Shivesh Pathak}
-
+\usepackage[margin=1.0in]{geometry}
 \begin{document}
@@
 
-\color{red} Red \color{black} is incomplete preliminary work.
-\color{blue} Blue \color{black} is work for the future.
+\section{Introduction and Methods}
+\textit{The goal of the introduction is to show the reader that the project is valuable. Should be x pages, other 5-x page will be methods.}
+\paragraph{Overall goal}
+We want to understand the low energy behavior of the cuprate superconductors.
+\\
+\textit{This paragraph will be outlining the various phenomenon attributed with the cuprates, e.g. the many phases.}
 
-\section{Motivation/Background}
-\begin{enumerate}
-\item People want to construct an accurate low-energy model Hamiltonian for the cuprates.
-\item Hole doped cuprates have been studied for a long time and have many degrees of freedom: O p and Cu d orbitals both play roles.
-\item Electron doped cuprates are less studied and we believe they are simpler since only the Cu d orbitals play a major role.
-\item We plan on building an low-energy model for the electron doped cuprate SrCuO$_2$ using a density-matrix downfolding method and accurate many-body QMC calculations.
-\end{enumerate}
+\paragraph{Barrier to achieving goal}
+The strong coupling between magnetic, charge, and lattice degrees of freedom in the cuprates makes writing down an accurate low energy effective theory very challenging.
+\\
+\textit{This paragraph will outline the many experiments that show the strong coupling between these many degrees of freedom.}
 
-\section{Preliminary SCF calculations}
-\subsection{Undoped (x=0)}
-\begin{enumerate}
-\item We did eight unit cell PBE0 calculations to calculate the energies of states with singly occupied Cu d$_{x^2-y^2}$ orbitals but with different spin textures.
+\paragraph{Current state of the art}
+Many theoretical approaches to generating a low energy model for the cuprates have been attempted with varying degrees of success.
+\\
+\textit{This paragraph will outline the various approaches people have tried to generate effective theories.
+Hole doped, electron doped, pen and paper, computational, energetics, one- and two-body properties.}
 
-\item We mapped these states onto spin-1/2 local moment states and used to fit to an AFM Heisenberg model:
-$$H_m = J\sum_{ij} \frac{1}{2} \vec{S_i}\cdot\vec{S_j} $$
+\paragraph{Advancement to the state of the art}
+We propose that a density matrix downfolding approach using \textit{ab initio} quantum Monte Carlo calculations can generate an effective model for the infinite layer electron-doped cuprates at zero temperature which can accurately describe low-energy properties and energetics.
+\\
+\textit{This paragraph will describe in detail each of the conditions in the thesis sentence.}
 
-\item The results of this fitting on seven different spin textures yields good results for two different basis sets (BFD Cutoff, BFD PBC 0.2)
+\paragraph{Density matrix down folding} 
+The density matrix downfolding method allows us to downfold a first-principles Hamiltonian into a low-energy effective theory by mapping the downfolding problem to a linear regression problem which uses \textit{ab-initio} energies and reduced density matrices of wave functions sampled from a low-energy subspace of the full Hilbert space.
+\\
+\textit{This paragraph should outline the details of the DMD method. No reference to QMC yet.}
 
-\item The high $R^2$ values of these fits indicate that a simple AFM Heisenberg model should be sufficient to capture the low-energy behavior of the undoped cuprates.
-\end{enumerate}
-
-\includegraphics[width=0.5\textwidth]{../undoped/PBE0_8/J_fit_naive.pdf}
-\includegraphics[width=0.5\textwidth]{../undoped/PBE0_8/J_fit_naive_BFD0p2.pdf}
-
-\subsection{Overdoped (x=0.25)}
-\begin{enumerate}
-\item We similarly did seventeen x=0.25 doped calculations in PBE0, from we got four low energy states.
-Here low-energy is defined as states with energy less than 0.3 eV from the lowest energy state we had, a collinear doped state.
-
-\item We then used the band structures and energies of these four low energy states to fit to a naive model with $t, t^\prime, K, J$ parameters: NN-hopping, NNN-hopping, NN-Kondo term, and NN-Heisenberg-AFM term
-
-$$H_m =  -t\sum_{\langle i, j \rangle, \sigma} (c_{i\sigma} ^\dagger c_{j\sigma} + h.c.) + 
-t^\prime\sum_{\langle\langle i, j \rangle\rangle, \sigma} (c_{i\sigma} ^\dagger c_{j\sigma} + h.c.) + $$ 
-$$K \sum_{\langle i, j \rangle} \vec{S_i} \cdot c_{j\alpha}^\dagger \vec{\sigma}_{\alpha \beta} c_{j\beta} + J\sum_{ij} \frac{1}{2} \vec{S_i}\cdot\vec{S_j} $$
-
-\item The presence of $t, t^\prime$ parameters were necessary to get the correct curvature of bands near the Fermi level, and the $K, J$ parameters were necessary to get both the spacing between bands (K) and the total energies (K,J).
-
-\item We map each of the PBE0 states into the model Hilbert space by breaking the occupied bands into a) fully occupied and b) partially occupied.
-The orbitals from a) then build a spin density that defines the variables $\vec{S_i}$ and the orbitals from b) define the variables $c_i^\dagger$.
-
-\item We can therefore create a single body  Hamiltonian where we treat the spins $\vec{S_i}$ as a fixed background upon which the itenerant $c_i^\dagger$ electrons can move.
-We can solve this model Hamiltonian and fit to the PBE0 band structure, and also compare the total energy of the model to the PBE0 total energy.
-
-\item We use a prior where $J$ is held as the undoped value.
-This is because in a metallic/superconducting doped state, there are charge fluctuations locally.
-Therefore we expect that on average the total charge locally between nearest neighbors will be the undoped value, and since the Heisenberg model only has local coupling we don't imagine $J$ should change too much.
-
-\item Since we are fitting to two different quantities (total energy and band structure) we used a Pareto efficiency analysis to get the best balance between a fit to total energy and a fit to band structure.
-The cost function is shown below, and $w_E$ varies in the plot shown even lower for the two different basis sets from before.
-
-$$Cost = w_E|E_m - E_{PBE0}|^2 + \sum_{|k|\le k_F} |e_{m,k} - e_{PBE0,k}|^2$$
-
-\item We find that the most efficient point is at the blue square on the Pareto plot. Below we plot the fit to the band structure and comparison of the model and PBE0 total energies.
-
-\includegraphics[width=0.5\textwidth]{../doped_fv/PBE0_8/tb_fit/pareto4.pdf}
-\linebreak
-\color{red} Need to include plot for PBC 0.2 basis set.
-
-\color{black}
-
-\item For the BFD cutoff basis set we get the parameter values $t,t^\prime,K,J=  1.04, 0.53, -0.15, 0.18 eV$
-
-\item The two basis sets do not agree quantitatively, but this isn't too unexpected because it's such a rough fitting method, but qualitatively they do: AFM J, FM K, repulsive NNN hopping, attractive NN hopping.
-
-\includegraphics[width=\textwidth]{../doped_fv/PBE0_8/tb_fit/pareto4_high.pdf}
-\color{red} Need to include plot for PBC 0.2 basis set.
-\end{enumerate}
-
-\subsection{Optimally doped (x=0.125)}
-\color{red} Need to do these calculations, but analysis is identical to above.
-
-\color{black}
-\section{Density matrix downfolding (DMD) calculations}
-\subsection{Basis}
-
-\begin{enumerate}
-\item In order to do our DMD calculations we need a single particle basis to evaluate the density matrix on.
-We use intrinsic atomic orbitals (IAOs) as our one particle basis.
-Justification for this choice is provided below.
-
-\item \textbf{Undoped (x=0)}]
-\begin{enumerate}
-\item Shown below are the occupations of different IAOs for the checkerboard spin texture for the BFD Cutoff and BFD PBC 0.2 basis sets.
-
-\item Clearly the IAOs show that the primary variation between occupation is in the $3d_{x^2-y^2}$ orbital, namely the spin changes from site to site.
-The oxygen orbitals do not play a significant role, indicating that this basis captures the qualitative features that we expect from the undoped state.
-
-\item Another important feature is that for each copper atom there are TWO $3d_{x^2-y^2}$ IAOs: one for the occupied spin and one of the unoccupied spin.
-
-\end{enumerate}
-\includegraphics[width=0.5\textwidth]{../undoped/PBE0_8/CHK/dens_iao2_cu.pdf}
-\linebreak
-\color{red} Need to include plot for PBC 0.2 basis set.
-
-\color{black}
-\item \textbf{Overdoped (x=0.25)}
-\begin{enumerate}
-\item For the doped calculation, we did the same IAO analysis as for the x=0 case. We found that again the $3d_{x^2-y^2}$ orbital has the primary variation in occupation.
-
-\item Unlike the x=0 case, once doped the occupation number changes as well as the spin.
-Below is shown the difference in occupation of the spin-down and spin-up $3d_{x^2-y^2}$ orbitals of the doped collinear state compared to the UNDOPED collinear state.
-
-\item We see that the occupation of the dominant primary channel does not vary, and we can therefore attribute those orbitals to the fixed magnetic moments, and the secondary spin channel does vary and we can attribute those orbitals to the itinerant electrons.
-
-\includegraphics[width=0.5\textwidth]{../doped_fv/PBE0_8/COL0/iao/sub_occd.pdf}
-\linebreak
-\color{red} Need to include plot for PBC 0.2 basis set.
-
-\color{black}
-\item Therefore we see that the basis elements we will be constructing our DM out of are the two different $3d_{x^2-y^2}$ IAOs: the orbital corresponding to the primary spin channel will be used to calculate DM elements of the fixed spin moments $\vec{S_i}$ and the secondary spin channel IAO will be used to calculate DM elements of the itinerant electrons $c_i^\dagger$
-\end{enumerate}
-
-\item \textbf{Optimally doped (x=0.125)}
-\color{red} Need to do this, should be identical analysis to x=0.25.
-\end{enumerate}
-
-\color{blue}
-\subsection{States}
-\begin{enumerate}
-\item \textbf{Undoped (x=0)} For the undoped calculations, we have seven different spin textures. We can just use these for the model fitting since we will be fitting to a single parameter, $J$.
-
-\item \textbf{Overdoped (x=0.25)}
-\begin{enumerate}
-\item We have four low energy states for x=0.25.
-We will use these four states, as well as states that are singles (maybe double) excitations above these four states.
-Only states with energy lower than our cutoff will be used.
-\item We can also take linear combinations of states with singles and double excitations.
-This can help us generate many more states and also increase our fitting efficiency since we can then make use of parameter derivatives w.r.t the determinant coefficients.
-\end{enumerate}
-
-\color{red}
-\item \textbf{Optimally doped (x=0.125)}
-\begin{enumerate}
-\item Need to do this, should be similar.
-\end{enumerate}
-\color{blue}
-\end{enumerate}
-
-\subsection{K-points}
-\begin{enumerate}
-\item \textbf{Undoped (x=0)} For the undoped calculations, a $\Gamma$ point calculation should be sufficient to resolve any finite size effects because we have a large unit cell for calculation and the system is strongly insulating.
-
-\item \textbf{Doped (x=0.25, 0.125)}
-\begin{enumerate}
-\item For the doped calculations our first goal will be to do calculations just on the $\Gamma$ point, since this should give us a good sense of whether the model we are interested in makes sense or not.
-
-\item We can consider doing other k-point (twist boundary) calculations if we think that the finite size errors on the calculations at a single twist are too large.
-\end{enumerate}
-\end{enumerate}
-
-\subsection{QMC workflow}
-for x=0, 0.125, 0.25 \\
-\indent for k-points from section (3) \\ 
-\indent \indent for states from section (2) \\
-\indent \indent \indent Take lowest energy Slater det, variance optimize Jastrow;\\
-\indent \indent \indent use this Jastrow for all following calculations
+\paragraph{Fixed node diffusion Monte Carlo}
+We will use fixed node diffusion Monte Carlo (FN-DMC) to generate wave functions in our chosen low-energy subspace and to accurately calculate \textit{ab-initio} energies and reduced density matrices.
 \\
-
-\indent \indent \indent Calculate 1/2-RDM and quantities for parameter derivative fitting \\ 
-\indent \indent \indent using FN-DMC for basis elements in section (1)\\
-
-\noindent Conduct fitting to $t,t^\prime, K,J$ model using DMD method with parameter derivative fitting. \\
-
-\noindent Alter k-points, states from sections (3) and (2) as necessary for calculation.
+\textit{This paragraph should outline how we will use FN-DMC (with DFT) to generate the low energy states, their energies, and their RDMs}
 

### 2018-08-07 prelim/outline.tex
.

@@
 \begin{document}
-\maketitle
 
-\section{Introduction and Methods}
+\section{Introduction and methods}
 \textit{The goal of the introduction is to show the reader that the project is valuable. Should be x pages, other 5-x page will be methods.}
@@
 \paragraph{Advancement to the state of the art}
-We propose that a density matrix downfolding approach using \textit{ab initio} quantum Monte Carlo calculations can generate an effective model for the infinite layer electron-doped cuprates at zero temperature which can accurately describe low-energy properties and energetics.
+We propose that a density matrix downfolding approach using \textit{ab initio} quantum Monte Carlo calculations can generate an effective model which can accurately describe low-energy properties and energetics for the infinite layer electron-doped cuprates at zero temperature and dopings of x=0, 0.125, 0.25.
 \\
@@
 \\
-\textit{This paragraph should outline the details of the DMD method. No reference to QMC yet.}
+\textit{This paragraph should outline the details of the DMD method, with parameter derivatives. No reference to QMC yet.}
 
@@
 \textit{This paragraph should outline how we will use FN-DMC (with DFT) to generate the low energy states, their energies, and their RDMs}
+\pagebreak
+
+\section{Preliminary results and discussion}
+\textit{The goal of the preliminary results is to indicate that I have the tools to actually complete the proposed research.}
+
+\paragraph{NO determinants: Introduction} In order to become acquainted with our code  and QMC algorithms in general I worked on implementing and testing non-orthogonal orbital optimization in QWalk. 
+\\
+\textit{This paragraph should introduce the idea of non orthogonal orbital optimization.}
+
+\paragraph{NO determinants: Work} The main work involved comparing the FN-DMC energies and single particle densities when using trial wave functions with and without non-orthogonal orbital optimization.
+\\
+\textit{This paragraph should include details about how we actually went about doing these calculations.}
+
+\paragraph{NO determinants: Results and Discussion} We found that in addition to the improvements from orthogonal optimization, non-orthogonal orbital optimization yields improvements to the ground state FN-DMC energies and single particle properties.
+\\
+\textit{This paragraph should discuss the actual results from the calculations outlined above.}
+
+\paragraph{SCO SCF: Introduction} To get a grasp on the relevant energy scales, model terms, and values for model parameters before trying the computationally expensive DMD with FN-DMC we attempted an \textit{ad hoc} fitting procedure using only DFT eigenvalues and total energies.
+\\
+\textit{This paragraph should talk about the fitting procedure that we are planning on using.}
+
+\paragraph{SCO SCF: Work} The task at hand was to generate low-energy states for the three different dopings x=0, 0.125, and 0.25 on a 2$\sqrt(2)$x2$\sqrt(2)$x1 unit cell and use them in our \textit{ad hoc} fitting procedure to generate an approximate effective model.
+\\
+\textit{This paragraph should talk about the procedural work of generating these low energy states and the mean field approximation for fitting.}
+
+\paragraph{SCO SCF: Results and discussion} We find that a four parameter model with NN hopping, NNN hopping, AF Heisenberg exchange, and a FM NN Kondo term using only Cu 3d$_{x^2-y^2}$ orbitals can accurately describe the DFT band structures and total energies of low-energy states at T=0 and x=0, 0.125 and 0.25.
+\\
+\textit{This paragraph should talk about the results of the work from above.}
+
+\paragraph{SCO DMD: Basis elements} Our first step into DMD with FN-DMC was the generation of appropriate basis elements for our effective model Hamiltonian which we handled, for all three dopings, using intrinsic atomic orbitals.
+\\
+\textit{This paragraph should talk about the IAO analysis that we have.}
+\pagebreak
+
+\section{Proposed work}
+\paragraph{SCO DMD: Low energy states} Low energy states for the x=0 system can be constructed by using DFT states with different spin textures multiplied by a 3-body Jastrow factor as trial wave functions in FN-DMC.
+\\
+\textit{This paragraph should talk about low energy states for x=0 and the DMD procedure (no parameter derivatives).}
+
+\paragraph{SCO DMD: Low energy states} For the doped systems, low energy states will be constructed using multi-determinant expansions composed of low energy DFT states and singly excited determinants multiplied by a 3-body Jastrow factor as trial wave functions in FN-DMC.
+\\
+\textit{This paragraph should talk about the linear combination states and parameter derivatives.}
+
+\paragraph{SCO: Band structure} In addition to using them in the DMD procedure, we will use these low energy multi-determinant expansions to generate effective band structures for the doped states.
+\\
+\textit{This paragraph should talk about the independent project of using parameter derivatives for band structure on large systems.}
+
+\paragraph{SCO DMD: Descriptors} After calculating the RDMs on our IAO basis using FN-DMC, the relevant descriptors in our model can be initially restricted through symmetry considerations.
+\\
+\textit{This paragraph should talk about symmetry restriction of descriptors.}
+
+\paragraph{SCO DMD: Descriptors} Further restriction of relevant descriptors will be accomplished by using a greedy selection algorithm.
+\\
+\textit{Talk about the greedy algorithm.}
+
+\paragraph{SCO DMD:  FSE and K-points} QMC calculations on solids are accompanied by finite size effects which we will deal with, if necessary, using either a supercell extrapolation, k-point (twist) averaging, or both.
+\\
+\textit{Talk about how we would be able to diagnose whether FSE is important, then talk about how each of these methods work.}
+
+ \paragraph{•}
 

### 2018-08-10 prelim/outline.tex
Outline added reach goals and conclusion/summary

@@
 \\
-\textit{This paragraph should talk about the procedural work of generating these low energy states and the mean field approximation for fitting.}
+\textit{This paragraph should talk about the procedural work of generating these low energy states and the mean field approximation for fitting. REMEMBER TO TALK ABOUT DROPPED STATES}
 
@@
 
- \paragraph{•}
+ \paragraph{SCO DMD: Reach goal} A longer term goal is to use the DMD method to generate a single low-energy model that can accurately describe the low-energy properties of both superconducting SCO and an isostructural non-super conducting nickelate.
+ \\
+ \textit{This should talk about the goal of showing that DMD is actually accurate in its predictions, and is an interesting scientific problem not just a calculation we did.}
+
+\section{Conclusion and Summary}
+\paragraph{SCO DMD} We propose that a DMD method using \textit{ab initio} QMC calculations can generate an effective model which can describe the low-energy properties of the electron doped cuprate SCO with a level of accuracy previously unattainable.
+
+\paragraph{SCO Reach goal} We hope to extend our model fitting calculation to gain insight into why materials like nickelates, which are isostructural to the cuprates, do not superconduct.
 

### 2018-08-10 prelim/outline.tex
Figures almost complete for outline, waiting on Brian for greedy

@@
 \usepackage[margin=1.0in]{geometry}
+\usepackage{graphicx}
+\usepackage{float}
 \begin{document}
@@
 \textit{The goal of the introduction is to show the reader that the project is valuable. Should be x pages, other 5-x page will be methods.}
+
 \paragraph{Overall goal}
@@
 \textit{This paragraph should outline how we will use FN-DMC (with DFT) to generate the low energy states, their energies, and their RDMs}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.6\textwidth]{Figures/I1-phase_diagram.pdf}
+\caption{\label{fig1} Phase diagram of Sr$_{1-x}$La$_x$CuO$_2$ for various electron doping \textit{x} and temperature \textit{T}. Figure taken from [ref].}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.9\textwidth]{Figures/I2-DMD_diagram.pdf}
+\caption{\label{fig2} Schematic drawing of the the density matrix downfolding method, describing how the wave function samples, total energies, and descriptor values are mapped onto a linear regression problem.}
+\end{figure}
+
 \pagebreak
@@
 \textit{This paragraph should talk about the IAO analysis that we have.}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.6\textwidth]{Figures/R1-mean_field.pdf}
+\caption{\label{fig3} Schematic diagram showing the method for mean-field approximation we used in our DFT model fitting calculations.}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.9\textwidth]{Figures/R2-pareto.pdf}
+\caption{\label{fig4} Results of the \textit{ad hoc} fitting procedure just using the DFT eigenvalues and total energies for three different dopings.}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.9\textwidth]{Figures/R3-iao_basis.pdf}
+\caption{\label{fig5} Relaxation of the IAOs for the spin majority and minority channel under doping for the eighth doped flip state.
+The majority spin IAO can be used as a basis for the fixed spin moments and the minority spin IAO for the itinerant electrons.}
+\end{figure}
 \pagebreak
@@
 
+\begin{figure}[H]
+\centering
+%\includegraphics[width=0.9\textwidth]{Figures/R2-pareto.pdf}
+\caption{\label{fig6} Results for greedy algorithm procedure for choosing descriptors showing the decrease in $R^2$ as more descriptors are added for the FeSe molecule [ref].}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.9\textwidth]{Figures/P2-Ni_Cu.pdf}
+\caption{\label{fig7} The primitive unit cells of the isostructural materials LNCO [ref] and LSCO [ref], the prior which is not super conducting all the way to temperatures of 30mK [ref].}
+\end{figure}
+\pagebreak
+
 \section{Conclusion and Summary}

### 2018-08-10 doped_fv/PBE0_8/tb_fit_0p125/tb_fit.py
Figures almost complete for outline, waiting on Brian for greedy

@@ -193,9 +193,13 @@ def plot(t,tt,K,a,state):
   d0=np.array(d0)
   dpp=dp(t,tt,K,a,state)
   
-  plt.ylabel("E-Ef, eV")
+  #plt.ylabel("E-Ef, eV")
   plt.plot(d0,'go')
   plt.plot(dpp,'b.')
+  plt.ylim([-1.0,1.5])
+  plt.yticks(np.arange(-1.0,2.0,1.0))
+  plt.xticks(np.arange(1.0,1.0,1.0))
+  plt.axhline(0,color='gray',linestyle='--')
 
 def cost3(t,tt,K,a1,a2,a3,lim):
   ret=0
@@ -417,9 +421,11 @@ def plot4j(t,tt,K,J,b,m):
   E0-=E0[0]
   plt.plot(E0,E,'bo')
   plt.plot(E0,E0,'g')
-  plt.ylabel("E_pred, eV")
-  plt.xlabel("E_PBE0, eV")
-  plt.title("Total Energy fit")
+  plt.xticks(np.arange(0,0.3,0.1))
+  plt.yticks(np.arange(0,0.3,0.1))
+  plt.ylabel("Predicted, eV")
+  plt.xlabel("DFT, eV")
+  plt.title("Total Energy")
 
 ################################################################################3
 #BOTH ENERGY AND BANDS: 3 STATES
@@ -649,17 +655,21 @@ print(r24(t,tt,K,a1,a2,a3,a4),r24j(t,tt,K,J,b,m))
 t,tt,K,J,a1,a2,a3,a4,b,m=[ 1.15170394,  0.39218111, -0.29262262 , 0.18  ,      1.69178952 , 0.95802699,
 1.89141888 , 1.71880588,  0.39999982 , 0.20994019]
 
-plt.subplot(231)
-plot4j(t,tt,K,J,b,m)
 plt.subplot(232)
+plt.title("FLP")
 plot(t,tt,K,a1,"flp1")
 plt.subplot(233)
+plt.title("CHK")
 plot(t,tt,K,a2,"chk1")
-plt.subplot(234)
-plot(t,tt,K,a3,"achn3")
 plt.subplot(235)
+plt.title("ACHN")
+plot(t,tt,K,a3,"achn3")
+plt.subplot(236)
+plt.title("COL")
 plot(t,tt,K,a4,"col1")
-plt.show()
+plt.suptitle("x=0.125 DFT fitting results")
+plt.subplot(234)
+plot4j(t,tt,K,J,b,m)
 
[…]

### 2018-08-10 doped_fv/PBE0_8/tb_fit_0p25/tb_fit.py

@@ -209,7 +209,10 @@ def plot(t,tt,K,a,state):
   d0=np.array(d0)
   dpp=dp(t,tt,K,a,state)
   
-  plt.ylabel("E-Ef, eV")
+  plt.ylim([-1.5,1.5])
+  plt.yticks(np.arange(-1.0,2.0,1.0))
+  plt.xticks(np.arange(1.0,1.0,1.0))
+  plt.axhline(0,color='gray',linestyle='--')
   plt.plot(d0,'go')
   plt.plot(dpp,'b.')
 
@@ -334,9 +337,7 @@ def sigTB(t,tt,K,state):
           e.append(w[1][k])
 
   e=sorted(e)
-  plt.plot(e,'b.')
   e=e[:2*(N-1)**2]
-  plt.plot(e,'g.')
   return np.sum(e)/((N-1)**2)
 
 def cost3j(t,tt,K,J,b):
@@ -438,9 +439,11 @@ def plot4j(t,tt,K,J,b):
   E0-=E0[0]
   plt.plot(E0,E,'bo')
   plt.plot(E0,E0,'g')
-  plt.ylabel("E_pred, eV")
-  plt.xlabel("E_PBE0, eV")
-  plt.title("Total Energy fit")
+  plt.xticks(np.arange(0,0.4,0.1))
+  plt.yticks(np.arange(0,0.4,0.1))
+  plt.ylabel("Predicted, eV")
+  plt.xlabel("DFT, eV")
+  plt.title("Total Energy")
 
 def cost5j(t,tt,K,J,b):
   #print(t,tt,K,J)
@@ -746,15 +749,23 @@ res=scipy.optimize.minimize(lambda p: cost4_both(p[0],p[1],p[2],p[3],p[4],p[5],p
 t,tt,K,J,a1,a2,a3,a4,b=res.x
 print(res.x)
 '''
-'''
-#t,tt,K,J,a1,a2,a3,a4,b=[1.49904204 , 0.89523692 ,-0.24776747 , 0.18      ,  2.08147531 , 1.79489747, 1.07267895 , 1.80422129 , 0.]
 t,tt,K,J,a1,a2,a3,a4,b=[1.03536369,  0.53250351 ,-0.15009942,  0.18  ,      1.42954778,  1.18583609, 0.67371943,  1.19444543,  0.]
-print(r24(t,tt,K,a1,a2,a3,a4),r24j(t,tt,K,J,b))
-plot4(t,tt,K,a1,a2,a3,a4)
+plt.subplot(232)
[…]

### 2018-08-29 prelim/draft.tex
First draft of prior work complte

\documentclass{article}
\usepackage[margin=1.125in]{geometry}
\usepackage{graphicx}
\usepackage{float}
\begin{document}
\section{Introduction} 
%Paragraph 1
%A major challenge in theoretical physics is the development of an accurate effective low-energy theory for the cuprate superconductors. The cuprate materials all share a common feature of repeating charge reservoir layers and CuO$_2$ planes within the conventional unit cell, with the reservoir layers providing hole or electron carriers to the CuO$_2$ planes under doping. The parent material to the cuprates are charge-transfer insulators with anti-ferromagnetic (AFM) order [ref]. The common phases shared by all cuprate materials are the AFM, pseudogap, strange metallic, normal metallic, and superconducting phases, with each phase deviating from the simple behavior we expect from  The pseudogap phase exists in the underdoped region with T$>$T$_c$ but still maintains a gap [ref]. The strange metal phase appears in the optimally doped region above T$_c$ and is a metallic phase, but has linear resistivity as opposed to the quadratic resisitivity expected from a Fermi-Landau liquid theory [ref]. The normal metal phase has Fermi-Landau like single-particle charge excitations (quasiparticle excitations), but does not have the predicted bosonic charge excitations (plasmons) [ref]. The superconducting phase has d$_{x^2-y^2}$ pairing and lives under a superconducting dome with the transition temperature T$_c$ varying with doping. 
%

%Paragraph 2
%The difficulty can be attributed in large part to the host of structural, magnetic and charge orders that exist as doping, temperature and pressure are varied. The simplest orders that are shared among all cuprates are charge transfer anti-ferromagnetic, pseudogap, strange metallic, normal metallic, and superconducting phases which stabilize as doping and temperature are varied \textbf{[ref1]}. Alongside these common orders, particular cuprate families exhibit structural phase transitions\textbf{[ref2]}, static stripe-like order\textbf{[ref3, ref4, ref5]}, and charge density wave order \textbf{[ref6]}. 
%

%Paragraph 3
%Paragraph 5

%Paragraph 4 + 6 merge 
%We propose that a density matrix downfolding approach using \textit{ab initio} Quantum Monte Carlo calculations can generate an effective model which can accurately describe low-energy properties and energetics for t%he infinite layer electron-doped cuprates at T=0 and x=0, 0.125, 0.25.

\section{Preliminary results}
In order to become acquainted with our code QWalk [ref QWalk] and QMC algorithms in general I worked on implementing and testing multi-Slater-Jastrow trial functions with optimized non-orthogonal determinants (MSJ+NO) in FN-DMC [ref my paper]. We assessed the efficiency and compactness of this new trial function by calculating the ground state energy and single particle densities of a C$_2$ molecule using FN-DMC and comparing to the results when using multi-Slater-Jastrow trial functions with optimized orthogonal determinant trial functions (MSJ+O). The workflow involved constructing the un-optimized trial wave functions, optimizing the parameters using an energy optimization method [ref], and finally using the optimized trial functions in an FN-DMC calculation. We found that the FN-DMC energy calculated using an MSJ+NO trial function with only 24 determinants was lower than the FN-DMC energy using an MSJ+O trial function with 55 determinants. Further, the FN-DMC charge density calculated using MSJ+NO trial functions had stronger bonding character than when using MSJ+O trial functions, a reasonable result as introducing correlations into trial functions allows for electrons to avoid each other while still occupying the same bonding region. Our results indicated that using non-orthogonal determinants may lead to more compact multi-Slater-Jastrow trial wave functions for small molecules.

Before moving on to the computationally expensive DMD with FN-DMC calculations on SrCuO$_2$, we attempted an \textit{ad hoc} model fitting procedure using only eigenvalues and total energies from density functional theory (DFT) to get a grasp on the relevant energy scales, model terms, and values for model parameters. A single DFT calculation provides us three pieces of information: a Slater determinant wave function with occupied single particle orbitals $|\Psi_{DFT}\rangle$, a single particle band structure which represents the DFT eigenvalues $\epsilon(\vec{k})_{DFT}$, and a total DFT energy $E_{DFT}$. Suppose we have some low-energy effective model in mind with parameters $\vec{p}$, H$_m$($\vec{p}$). We can fit the parameters in the model using only information from the DFT calculation by constructing a cost function which depends on $\vec{p}$, and then minimizing the cost. The cost function we used was:
\begin{equation}
Cost(w_E, \vec{p}) = \sum_{i=1}^{n} [\sum_{\vec{k}}(\epsilon(\vec{k})_{DFT,i} - \epsilon(\vec{k})_{m,i})^2] + w_E[E_{DFT,i} - \langle \Psi_{DFT,i}|H_m(\vec{p})| \Psi_{DFT,i} \rangle]^2
\end{equation}
where the sum over $i$ is over a sample of low-energy DFT states. The first term is the cost function for a least squares fit of the single particle eigenvalues calculated using our model $\epsilon(\vec{k})_m$ and the DFT state $|\Psi_{DFT,i}\rangle$ to the DFT eigenvalues. The second term is a cost function for a least squares fit of the total energy calculated using our model to the DFT total energy. The term $w_E$ controls the importance of minimizing the total energy cost relative to the eigenvalue cost, and is a variable parameter. The accuracy of the fit was assessed by looking at the $R^2$ value between the total energies, $R^2_E$, and between the eigenvalues, $R^2_\epsilon$. The fitting procedure then follows: choose a model Hamiltonian H$_m$, choose a sequence of $w_E$, minimize the cost function for each $w_E$ in the sequence and obtain a sequence of tuples $(\vec{p}, R^2_E, R^2_\epsilon)$. Increasing $R^2_E$ to near 1.0 will lead to a decrease in $R^2_\epsilon$ and vice versa, so the optimal model parameters are chosen by conducting a Pareto efficiency analysis on the sequence of pairs $(R^2_E, R^2_\epsilon)$. The Pareto optimal pair then gives us the optimal parameters $\vec{p}^\star$. Note that the resulting fitted effective model will not accurately reproduce the low-energy features of the \textit{ab initio} Hamiltonian H, but rather will reproduce the low-energy features of the effective Kohn-Sham theory used in our DFT calculation.

We conducted this \textit{ad hoc} fitting procedure for SrCuO$_2$ under three different dopings x=0, 0.125, and 0.25 using the PBE0 functional in DFT on a 2$\sqrt{2}$x2$\sqrt{2}$x1 unit cell. The PBE0 functional has been used within QMC in the past to yield accurate results for low-energy properties and energies on the hole-doped cuprates [ref]. The eight unit cell calculation was chosen since it is small enough to be computationally feasible even when moving to QMC, but large enough that the finite size effects are not too large. For the undoped calculations, the PBE0 ground state was a checkerboard AFM state, and the six low-energy states we considered were states with spins flipped relative to this ground state. This choice was made since the lowest energy excitations of the undoped cuprates are spin excitations as they are charge-transfer insulators. For the x=0.125 calculations, the PBE0 ground state was a flip state, and the four low-energy states we considered were states with total energy less than 0.25 eV above this ground state. One excited state in this energy range was discarded because it was insulating in character while the other four were metallic. This may have occured since PBE0 has been shown to incorrectly order states energetically for strongly correlated systems [ref]. For the x=0.25 calculations, the PBE0 ground state was a collinear state, and the four low-energy states we chose were states with total energy less than 0.30 eV above this ground state. Again one state in this range was insulating, while the other four were metallic, and this state was discarded from the fitting procedure. The model we chose to fit has four terms: 
\begin{equation}
H_m = -t \sum_{\langle i,j \rangle} c_i^\dagger c_j + h.c.
+ t^\prime\sum_{\langle \langle i.j \rangle \rangle} c_i^\dagger c_j + h.c. +\\
K\sum_{\langle i,j \rangle} \vec{S_i} \cdot c_{j,\alpha}^\dagger \vec{\sigma}_{\alpha,\beta} c_{i,\beta} + J \sum_{\langle i,j \rangle} \vec{S_i} \cdot \vec{S_j}.
\end{equation}
The operators $\vec{S_i}$ represent the spin moment on the copper sites and $c_i^\dagger$ the itinerant electrons hopping around copper sites. The last term is a Heisenberg exchange which we included since the undoped material can be modeled fairly accurately with just a nearest neighbor Heisenberg model with J = 0.18 eV [ref]. The first two terms are nearest neighbor and next-nearest neighbor hopping which are both required to capture the curvature of the PBE0 bands crossing the Fermi level for the x=0.125 and x=0.25 low-energy states. The third term is a nearest neighbor Kondo term which we included since it can help stabilize a flip state over a checkerboard state, as seen in the x=0.125 PBE0 calculations. In order to extract the band structure and total energy from this model we made a mean field approximation where we split the electrons into two groups: those which contribute to the fixed spin moments $\vec{S_i}$ on site and those which are itinerant $c_i^\dagger$. This choice was motivated by looking at the PBE0 band structures of the low-energy states. As shown in \ref{fig3} the band structure is split by a large gap on the order of 1 eV, in this case for the collinear x=0.25 state. The bands above this gap cross the Fermi level, and can be thought of as bands which contribute only itinerant electrons. The bands below this gap never cross the Fermi level, and can be thought of as bands which contribute only to the fixed spin moments on copper sites. Therefore we can treat the quantities $\vec{S_i}$ as fixed variables, the values of which are dictated by the bands below the gap for a given PBE0 calculation. In doing so, the Kondo term becomes a 1-body term and the Heinsenberg term becomes a constant value, leaving the model Hamiltonian as a 1-body Hamiltonian which we can exactly diagonalize to get the total energy and eigenvalues.

We find that the four term model above can accurately describe the PBE0 band structures and total energies of low-energy states of SrCuO$_2$ for x=0, 0.125, and 0.25. \ref{fig4} shows the results of our \textit{ad hoc} fitting procedure. For the undoped calculation no fitting to eigenvalues was necessary nor Pareto efficiency analysis since there were no itinerant electrons, leading to an optimal fit of $t=t^\prime=K=0 eV; J = 0.18 eV$. For the doped calculations, we held J fixed at the undoped value. This choice was made since doping with just one or two electrons in the unit cell means that most nearest neighbor copper atoms will not see the presence of the itinerant electron permanently, meaning that the local exchange interaction will not be too strongly affected. Computationally, holding the value of J fixed at some prior made the minimization of the cost function much more stable. For the doped calculations, the first inset figure shows the Pareto plot with the sequence of $(R^2_E, R^2_\epsilon)$, and the Pareto optimal pair as a blue square. The other five insets show the fits to the bands and total energies from DFT using our model with the Pareto optimal parameters. For the x=0.125 calculation the optimal parameters were with $t,t^\prime,K,J$=1.15, 0.39, -0.29, 0.18 eV $R^2_E$=0.98 and $R^2_\epsilon$=0.96. For the x=0.25 calculation the optimal parameters were $t,t^\prime,K,J$=1.04, 0.53, -0.15, 0.18 eV with $R^2_E$=0.91 and $R^2_\epsilon$=0.94. In both our model and PBE0, the bands which cross the Fermi level are antibonding Cu 3d$_{x^2-y^2}$ orbitals which have been relaxed via small contributions from nearest neighbor oxygen p orbitals. In PBE0 the net spin moments comprised of the bands below the Fermi level also reside on the Cu 3d$_{x^2-y^2}$ orbital, indicating that unlike the hole-doped cuprates where oxygen and copper orbitals both play an important role in the effective theories, the electron-doped cuprates may be simpler since the major players is just the Cu 3d$_{x^2-y^2}$ orbital. Therefore the fact that $t, t^\prime$ have the same sign makes sense as this is a feature arising from the symmetry of the 3d$_{x^2-y^2}$ orbital. The positive sign of $J$ indicates a preference of nearest neighbor spin moments to be anti-ferromagnetically aligned, whereas the negative sign of $K$ shows a preference for itinerant electrons to ferromagnetically align with nearby spin moments. The opposite signs of J and K, and the fact that K is larger in magnitude than J when x=0.125 can lead to the stabilization of a flip state instead of a checkerboard one in PBE0.

Our first step into DMD with FN-DMC was the generation of appropriate basis elements for our effective model Hamiltonian which we handled for all three dopings using intrinsic atomic orbitals. The \textit{ad hoc} fitting procedure we conducted provided us with a starting point for generating low-energy states for the DMD calculation, the terms in our model Hamiltonian, and parameter values, but gave us no headway on understanding which basis elements to use. Using MOs in our model is not feasible because the interactions we are looking at are local and are nearest neighbor spatially. If our interaction terms were more easily written in a momentum representation then MOs from PBE0 would be a useful basis to use. We could start with atomic orbitals, AOs, which are the building blocks of the MOs in our PBE0 calculation, but AOs in general are not orthogonal to each other. This complicates our model representation because we typically work with models where creation and annihilation operators generate orthogonal states. Therefore, what we are looking for are orbitals that are maximally localized and still orthogonal to one another, and this is precisely what the IAO is [ref]. In order to test whether the IAO basis is sufficient at spanning the space of excitations we are interested in, we looked at the 1-body reduced density matrix (1RDM) relative to the IAO basis for each x=0, 0.125 and 0.25 low-energy state chosen above. We found that the total number of electrons in the system is accounted for up to three decimal places using just the trace of the 1RDM over the minimal IAO basis. Further, we found that the primary variation between low energy states at a fixed doping was in occupation of the IAOs was of the 3$d_{x^2-y^2}$ IAO. For the undoped calculations the only variation in IAO occupation among the various states was the relative occupation of the spin-up or spin-down 3$d_{x^2-y^2}$ orbital on particular copper sites. This makes sense as the only difference between the undoped low-energy states was the configuration of local spin moments. Under doping, the primary variation in orbital occupation was found in the 3$d_{x^2-y^2}$ IAO which had the lower occupancy. This makes sense as the only place the added electron can go is in the 3$d_{x^2-y^2}$ orbital in the spin channel opposite to the local moment on the site. \ref{fig5} shows the IAOs for the majority spin IAO, which has the higher occupation, and the minority spin IAO, which has the lower spin, for a low-energy state at x=0.125. It is clear that the majority spin IAO is more tightly localized on site whereas the minority spin IAO spreads across the unit cell with contributions from oxygen p-orbitals. We therefore come to the conclusion that the majority spin IAOs should be used as a basis for the localized spin moments, $\vec{S_i}$, and the minority spin IAOs should be used as a basis for the itinerant electrons, $c_i^\dagger$.

\begin{figure}[H]
\centering
\includegraphics[width=0.6\textwidth]{Figures/R1-mean_field.pdf}
\caption{\label{fig3} Schematic diagram showing the method for mean-field approximation we used in our DFT model fitting calculations.}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{Figures/R2-pareto.pdf}
\caption{\label{fig4} Results of the \textit{ad hoc} fitting procedure just using the DFT eigenvalues and total energies for three different dopings.}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{Figures/R3-iao_basis.pdf}
\caption{\label{fig5} Relaxation of the IAOs for the spin majority and minority channel under doping for the eighth doped flip state. The majority spin IAO can be used as a basis for the fixed spin moments and the minority spin IAO for the itinerant electrons.}
\end{figure}

%\section{References}
%\begin{enumerate}
%\item https://journals.aps.org/rmp/abstract/10.1103/RevModPhys.82.2421
%\item https://journals.aps.org/prl/abstract/10.1103/PhysRevLett.62.2751
%\item https://www.nature.com/articles/375561a0
%\item https://journals.aps.org/prb/abstract/10.1103/PhysRevB.54.7489
%\item https://journals.aps.org/prb/abstract/10.1103/PhysRevB.60.3643
%\item https://www.nature.com/articles/nphys178
%\end{enumerate}

\end{document}

### 2018-09-02 prelim/draft.tex
worked on draft, finished some intro and proposed work

@@
 \usepackage{float}
+\usepackage{amsfonts}
 \begin{document}
@@
 %Paragraph 3
-%Paragraph 5
 
-%Paragraph 4 + 6 merge 
-%We propose that a density matrix downfolding approach using \textit{ab initio} Quantum Monte Carlo calculations can generate an effective model which can accurately describe low-energy properties and energetics for t%he infinite layer electron-doped cuprates at T=0 and x=0, 0.125, 0.25.
+The density matrix downfolding method (DMD) allows us to downfold a first-principles Hamiltonian into a low-energy effective theory by mapping the downfolding problem to a linear regression problem which uses ab-initio energies and reduced density matrices of wave functions sampled from a low-energy subspace of the full Hilbert space [ref].
+Consider a Hamiltonian H which acts on vectors in a Hilbert space $\mathcal{H}$ and a subset of the Hilbert space $\mathcal{LE}$ which is spanned by the lowest N energy eigenvectors of H. 
+We would like to write down an effective Hamiltonian operator which acts on vectors in $\mathcal{LE}$ such that  $$\forall |\Psi\rangle \in \mathcal{LE}, H_{eff}|\Psi \rangle = H|\Psi \rangle.$$ 
+It can be shown that this statement is equivalent to requiring that $$ E[\Psi] = E_{eff}[\Psi] + C \forall \Psi \in \mathcal{LE}$$ where we define the functional as $E[\Psi] = \frac{\langle \Psi | H | \Psi \rangle}{\langle \Psi | \Psi \rangle},E_{eff}[\Psi] = \frac{\langle \Psi | H_{eff} | \Psi \rangle}{\langle \Psi | \Psi \rangle}$ [ref].
+The obvious choice that would satisfy these constraints would simply be $H_{eff} = \sum_{i=1}^{N} E_i |\Psi_i\rangle \langle \Psi_i|$, but this would require us to be able to solve for the eigenstates and eigenvalues of the many-body Hamiltonian H, which we presumably cannot do.
+Instead, we may expand the $E_{eff}$ in terms of descriptors $d_i[\Psi]$ which much be chosen, simplifying the expression to just 
+\begin{equation}
+E_{eff} \sim \sum f_i d_i[\Psi].
+\end{equation}
+Now the task of generating an $E_{eff}$ that can satisfy the conditions outlined above can be cast into a statistical learning form.
+Generally we will begin the DMD procedure by generating low energy states $\Psi_i$ within the space $\mathcal{LE}$. 
+Generating these states is somewhat problem dependent and will be discussed later on for the specific case of SrCuO$_2$. 
+Additionally, we need to generate a set of descriptors $d_j$. 
+Typically these descriptors take the form of expectation values of 1- or 2-rdm elements, such as $\langle \Psi| c^\dagger_k c_k |\Psi \rangle$ but can generally be any functional of $\Psi$. 
+We can then use the sample states $\Psi_i$ to calculate the set of quantities $d_j[\Psi_i], E[\Psi_i]$. 
+The next step is to assess whether the set of descriptors we chose and the set of states sampled are complete or not. 
+For example, we might find that we have two states $\Psi_1, \Psi_2$ which have very similar descriptor values but very different energies (but both within the low-energy space), then it is clear that our descriptor set does not capture the variation of the energy within the space $\mathcal{LE}$ and a different descriptor must be included.
+If instead we find that we have many low-energy states with very similar energies and descriptor sets then our sampling of the low-energy space may be incomplete as we are not capturing the full variation of the descriptors we are interested in.
+In either case we may have to return to the low-energy state sampling or descriptor choosing step until we are satisfied.
+Once we have all of our low-energy states and important descriptors, we can simply conduct a linear regression to fit the coefficients of descriptors $f_i$, although other fitting approaches such as a LASSO fit can also be used [ref].
+\ref{fig1} shows the workflow of the DMD procedure. 
+We can increase the number of data points per wave function sample $\Psi_i$ by considering derivatives of the wave function and descriptors as well. 
+Insofar each wave function provides one data point for linear regression, however if we parameterize the wave function $\Psi_i(\vec{p})$ then we can generate N data points for the fitting where N is the number of parameters by simply taking a derivative of the left and right hand sides of equation (1) with respect to the parameters $p_i$.
+Therefore including parameter derivatives in our fitting procedure can increase the efficiency N fold, decreasing the number of low-energy states that need to be sampled. 
+For our situation the Hamiltonian H is the \textit{ab initio} Hamiltonian 
+\begin{equation}
+\hat{H_{ab}} = -\frac{1}{2} \sum_i \nabla_i^2 + \sum_{i<j} \frac{1}{r_{ij}} + \sum_{i\alpha} \frac{Z_\alpha}{r_{i\alpha}} + \sum_{\alpha<\beta} \frac{Z_{\alpha}Z_{\beta}}{r_{\alpha \beta}}
+\end{equation}
+where $i,j$ are electron indices, $\alpha$ is a nuclear index, with a clamped nucleus approximation and psuedo-potentials for core electrons.
+\textbf{Need to write down why it's better than other methods!}
+
+We will use fixed node diffusion Monte Carlo (FN-DMC) to generate
+wave functions in our chosen low-energy subspace and to accurately calculate ab-initio energies and reduced density matrices. 
+Diffusion Monte Carlo (DMC) is a quantum Monte Carlo method which projects out the ground state of a Hamiltonian given some initial trial wave function. 
+Consider a trial wave function $|\psi\rangle$ and a Hamiltonian $H$ with ground state $|\phi_0\rangle$. 
+We apply the projector $e^{-\tau (H-E_0)}$ as $\tau \rightarrow \infty$ to $|\psi \rangle$
+\begin{equation}
+\lim_{\tau \rightarrow \infty} e^{-\tau (H-E_0)} |\psi\rangle \propto \langle \phi_0|\psi\rangle |\phi_0\rangle,
+\end{equation}
+projecting out the ground state $|\phi_0\rangle$ of $H$ as long as the trial wave function we choose is not orthogonal to the ground state. 
+The stochastic implementation involves moving samples from the trial function $\Psi_T(R)$ using the Green function $G(R, R^\prime, \tau) = \langle R | e^{-\tau(H - E_T)} | R^\prime \rangle$. 
+Since the Hamiltonian has two parts, $H = T + V$ a Trotter expansion is used to approximate the Green function $G(R, R^\prime, \tau) = \langle R | e^{-\tau(H - E_T)} | R^\prime \rangle \sim e^{-\tau(V(R) + V(R^\prime))/2} \langle R| e^{-\tau(T - E_T)}|R^\prime \rangle + O(\tau^2) $ which leads to a time step error in the calculation if the time step between moves $\tau$ is too large.
+This implementation when used on a Hamiltonian with fermions also leads to a fermion sign problem. 
+We deal with this sign problem through a fixed-node approximation, where the nodal surface of the projected wave function is forced to match that of the initial trial wave function. 
+This approximation makes FN-DMC variational, and will only return the exact ground state of $H$ if the nodal surfaces of $|\psi\rangle$ and $|\phi_0\rangle$ are identical. 
+Therefore the FN-DMC calculation has two major systematic errors that have to be dealt with, the fixed-node error and the time-step error. 
+The time-step error is typically handled through a time-step extrapolation, where multiple FN-DMC calculations are conducted at sequentially smaller $\tau$ and the relevant expectation values are extrapolated to $\tau \rightarrow 0$ [ref].
+Fixed-node error can be managed through \textbf{do this!}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.9\textwidth]{Figures/I2-DMD_flow.png}
+\caption{\label{fig1} Schematic drawing of the workflow for the density matrix downfolding technique, taken from [ref].}
+\end{figure}
 
@@
 \end{figure}
+\pagebreak
+
+\section{Proposed work}
+In order to generate an effective low-energy model using the DMD technique we need to generate low-energy wave functions within the full \textit{ab initio} Hilbert space. 
+We will be using optimized multi-Slater-Jastrow (MSJ) as trial wave functions in FN-DMC to generate the low-energy states we are interested in. 
+The MSJ wave function form 
+\begin{equation}
+\Psi_{MSJ} = e^{J(\vec{\alpha})} \sum_I c_I |D_I{\{\phi\}}\rangle 
+\end{equation}
+has two core parts, the multi-determinant expansion with determinant coefficients $c_I$ and a 3-body Jastrow factor with some Jastrow coefficients $\alpha$. 
+These parameters will be optimized using an energy optimization method described by [ref]. 
+The determinants will be composed of single particle orbitals from the eight unit cell DFT calculations we have already completed.	
+The multi-determinant expansion will be generated using a (complete) active space (C)AS expansion using the Cu 3d and 4s bands and the O 2p bands. 
+We believe that these bands include the relevant degrees of freedom to generate an accurate low-energy model. 
+The (C)AS expansion allows us to generate many low-energy states by simply varying the coefficients $\{c_I\}_{I>0}$ within some cutoff. 
+After generating these trial wave functions we can use FN-DMC to project out a low-energy state within the \textit{ab initio} Hilbert space, calculate the total FN-DMC energy, 1- and 2-body reduced density matrices using the IAO basis that we have already generated, as well as derivatives of the total energy and the density matrices with respect to the determinant coefficients $c_I$.
+We will not consider derivatives with respect to the Jastrow coefficients because that derivative will take us outside of the low-energy space, as the Jastrow factor significantly reduces the total energy of a trial state [ref].
+
+After the data generation phase above from which we have all the information required to do our fitting, relevant descriptors have to be chosen for our low-energy model. 
+The first tool in reducing the space of relevant descriptors is through symmetry considerations.
+[ref] provides a useful manual for the terms that any 1- and 2-body Hamiltonian can have given the symmetry of the bands that are under consideration.
+From here we arrive at a basic statistics problem of generating a linear model given a potential set of descriptors. 
+A very basic approach to solving this problem is through a greedy selection algorithm. 
+This selection algorithm iteratively includes more and more descriptors to our model Hamiltonian, at each step including a term which would reduce the $R^2$ value between the \textit{ab initio} energies of our low-energy states and the model energies $\langle H_m \rangle$.
+This method does not span the space of all possible models given the symmetry constraints above, but is an efficient choice given the very large space of model Hamiltonians that could be chosen. 
+The greedy selection algorithm can then take our data and generate a sequence of models with increasing complexity, provide the best values of the model parameters for each model, and also provide a measure of the fit through the $R^2$ value.
+We can then manually choose a model which has a large $R^2$ with a relatively small model complexity. 
+This choice can also be made systematically by using an Akaike information criterion or Bayesian information criterion to measure the goodness of fit at each step of the greedy algorithm instead of a simple least-square measure of goodness.
+These two criteria penalize a model not only for the least-square measure of goodness but also for model complexity [ref].
+
+Since our initial set of calculations will be on an eight unit cell calculation cell with periodic boundary conditions, it is important to account for possible finite size errors in our FN-DMC calculations.
+If these finite size errors (FSEs) are not accounted for in FN-DMC then the model we generated may suffer from the same finite size effects as the QMC calculations. 
+Within QMC there are typically two approaches to dealing with finite size effects. 
+To deal with finite size effects affecting single particle properties a common choice is to use twist-averaging. 
+This means conducting the many-body FN-DMC calculation using various twisted boundary conditions and then averaging over the results of the single-particle expectation values [ref].
+This is equivalent to averaging over the many-body Brillouin zone. 
+To account for two-particle or higher order finite size effects, such as those affecting the Coulumb interaction term when calculating the total energy, a finite size extrapolation is required. 
+This involves conducting the FN-DMC calculations for a sequence of increasing calculation cell size, and then extrapolating the results of expectation values to the infinite cell size. 
+The extrapolation scales linearly with the cell volume [ref].
+
+After the data generation phase is complete, we will focus on other interesting problems that can be solved apart from the low-energy effective model, such as generating effective single-particle band structures.
+\textit{\textbf{Need to do this}}.
+
+Further, we will use the DMD procedure to attempt to describe the differences between the isostructural nickelate and cuprate materials. 
+Shown in \ref{fig6} are the conventional unit cells of the cuprate La$_2$CuO$_4$ and the nickelate La$_2$NiO$_4$, which are identical except that the copper atom within the cell is replaced by a nickel atom.
+While isostructural, the nickelates have been shown to not superconduct even down to temperatures of mK [ref] under doping. 
+In order to study this distinct difference in low-energy behavior, we will use the DMD procedure listed above in an identical fashion on the material SrNiO$_2$. 
+The relevant degrees of freedom are the same for both the nickelate and cuprate materials, meaning the active space used to generate low-energy states will be Cu 3d, 4s and O 2p for both cases. 
+If we consider a slightly higher energy cutoff for our low-energy theory, it may be possible that our DMD procedure generates an effective theory with identical descriptors but different model parameters.
+The reasoning behind this argument stems from the fact that effective models like the Hubbard model can yield various low-energy effective theories when considered under certain parameter regimes [ref], meaning that two materials can, at the lowest energy scales, have drastically different low-energy theories while at a higher energy scales be described accurately by similar effective theories.
+Having a single model which can describe the low-energy behavior of both of these materials would provide a big step forwards to understanding the emergence of superconductivity in the cuprates and the lack thereof in the nickelates.
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.9\textwidth]{Figures/P2-Ni_Cu.pdf}
+\caption{\label{fig6} The primitive unit cells of the isostructural materials LNCO [ref] and LSCO [ref], the prior which is not super conducting all the way to temperatures of 30mK [ref].}
+\end{figure}
 

### 2018-09-07 prelim/draft.tex
Finished 11/15 pages of prelim VERY ROUGH DRAFT. Need to do further edits this week, then Sept 14 - Sept 31 just clean up

@@
 \section{Introduction} 
-%Paragraph 1
-%A major challenge in theoretical physics is the development of an accurate effective low-energy theory for the cuprate superconductors.
-The cuprate materials all share a common feature of repeating charge reservoir layers and CuO$_2$ planes within the conventional unit cell, with the reservoir layers providing hole or electron carriers to the CuO$_2$ planes under doping.
-The parent material to the cuprates are charge-transfer insulators with anti-ferromagnetic (AFM) order [ref].
-The common phases shared by all cuprate materials are the AFM, pseudogap, strange metallic, normal metallic, and superconducting phases, with each phase deviating from the simple behavior we expect from  The pseudogap phase exists in the underdoped region with T$>$T$_c$ but still maintains a gap [ref].
-The strange metal phase appears in the optimally doped region above T$_c$ and is a metallic phase, but has linear resistivity as opposed to the quadratic resisitivity expected from a Fermi-Landau liquid theory [ref].
-The normal metal phase has Fermi-Landau like single-particle charge excitations (quasiparticle excitations), but does not have the predicted bosonic charge excitations (plasmons) [ref].
-The superconducting phase has d$_{x^2-y^2}$ pairing and lives under a superconducting dome with the transition temperature T$_c$ varying with doping.
-%
+Understanding the low energy behavior of the cuprate superconductors has been an open question in theoretical condensed matter physics for over thirty years.
+The cuprate materials all share a similar structure of repeating layers of square lattice CuO$_2$ planes and charge reservoir blocks, of which carriers on the prior exhibit the most interesting collective behavior.
+At zero doping the cuprates are antiferromagnetic charge-transfer insulators [ref].
+The theoretical challenge arises away from zero doping where the poorly understood superconducting, pseudo-gap, strange metal and "normal" metal phases appear [ref].
+\ref{fig1} shows the phase diagram of a hole- and electron-doped cuprate materials with different structures.
+The superconducting phase is d-wave in character and cannot be described by phonon-induced pairings [ref].
+In the pseudo-gap phase the d-wave gap from the superconducting state continues to exist, however the material is now metallic in character [ref] \textbf{check this!}.
+The strange metal phase is metallic but has a "strange" T-linear resistivity unlike typical metals which have quadratic-T resistivity at low temperatures [ref].
+The "normal" metallic phase exhibits the same single particle behavior expected of a Fermi-Landau-like metal, but the plasmon excitations are very different exhibiting self-similiarity in dispersion unlike the well defined plasmonic modes of the Fermi liquid [ref].
 
-%Paragraph 2
-%The difficulty can be attributed in large part to the host of structural, magnetic and charge orders that exist as doping, temperature and pressure are varied.
-The simplest orders that are shared among all cuprates are charge transfer anti-ferromagnetic, pseudogap, strange metallic, normal metallic, and superconducting phases which stabilize as doping and temperature are varied \textbf{[ref1]}.
-Alongside these common orders, particular cuprate families exhibit structural phase transitions\textbf{[ref2]}, static stripe-like order\textbf{[ref3, ref4, ref5]}, and charge density wave order \textbf{[ref6]}.
-%
+The strong coupling between magnetic, charge, and lattice degrees of freedom in the cuprates makes writing down an accurate low energy effective theory very challenging.
+For example, in La$_{2-x}$Ba$_x$CuO$_4$ (LBCO) there is a structural phase transition as doping and temperature are varied between a high temperature tetragonal phase (HTT), a low-temperature orthorhombic phase (LTO) and a low temperature tetragonal phase (LTT), and the fraction of the bulk transformed material from LTO to LTT is correlated with the bulk superconducting temperature under various dopings [ref].
+An independent study shows that in La$_{2-x}$Sr$_x$CuO$_{4-\delta}$ (LSCO) the superconducting phase transition for x $<$ 0.19 is accompanied by a structural phase transition from the HTT to LTO phase [ref].
+Further, there is evidence for static stripe phase, where antiferromagnetic stripes of copper spins are separated by periodically spaced domain walls to which the holes segregate, in La$_{1.6-x}$Nd$_{0.4}$Sr$_x$CuO$_4$ at x=0.12 which is associated with an anomalous suppression in the superconducting temperature [two refs].
+Elastic magnetic measurements on La$_2$CuO$_{4+y}$ show the superconducting phase is accompanied by a spin-density wave emergence indicating a strong correlation between the two phases [ref].
+In the undoped phase of the cuprates the magnetic dispersion across the magnetic Brillouin zone strongly resembles that of spin-waves in a square Heisenberg antiferromagnet [ref], however within the superconducting phase the magnetic dispersion takes on an "hourglass" shape which has been reproduced in experiments for LSCO at x=0.10, 0.16 [ref, ref], LBCO at x=0.125 [ref], and YBa$_2$Cu$_3$O$_{6+x}$ at x=0.5, 0.6 [ref].
 
-%Paragraph 3
+Many theoretical approaches to generating a low energy model for the cuprates which can account for the strong correlations between magnetic, lattice and charge degrees of freedom have been attempted with varying degrees of success.
+For the undoped cuprates a nearest neighbor Heisenberg model can reproduce the magnetic dispersions measured in inelastic neutron scattering experiments accurate away from the magnetic Brillouin zone boundary, but fail to capture the small effects of anomalous dispersion near the boundary [ref].
+%All refs for this part will be from Scalapino article "models"
+The simplest model for the hole-doped cuprates was suggested by Anderson and is a 2D single-band Hubbard model which only includes bands of Cu d$_{x^2-y^2}$ character, which will be hybridized with the oxygen bands to some degree [ref].
+This model is capable of producing the AFM phase at zero doping as in the strong coupling limit this model reduces to a nearest neighbor AFM Heisenberg model [ref].
+The model even exhibits a pseudo-gap like phase in the underdoped region [ref].
+Further, in the limit of $U/t \rightarrow 0$ the Hubbard model has a transition to a $d_{x^2-y^2}$ superconducting-like phase [ref].
+It has not been shown numerically that the superconducting order parameter is non-zero as the pair spacing is taken to be very large, however [ref].
+A similar model is the t-J model [ref, Elbio Dagatto] which is built on the idea that under doping there are itinerant holes which hop around the oxygen bands alongside the fixed S=1/2 moments on the copper sites which interact through a superexchange term with parameter J.
+The t-J model can be seen as an effective theory of the single band t-U model.
+This model exhibits superconductivity proper at J/t $\sim$ 3 with a density of $\langle n \rangle$ = 1/2 [ref], meaning that the pairing function does not vanish in the large spacing limit.
+While these models have fewer degrees of freedom and thus allow for quick numerical computations, it has been shown in accurate \textit{ab initio} Quantum Monte Carlo calculations that holes move to the oxygen bands under doping, indicating that an effective theory should include the oxygen bands explicitly not implicity inclusion via hybridization.
+This leads to a 2D 3-band Hubbard model which includes the Cu 3$d_{x^2-y^2}$ and O p bands [ref, Elbio Dagatto] and exhibits qualitatively similar behavior to the 1-band model.
+However, these approaches to generating a low-energy model have two inherent flaws.
+First, the model parameters are not specified with the model, meaning that seeing whether the model can accurately describe the cuprates involves mapping the entire parameter space.
+Second, there is no standard measure of effectiveness of the models under question: some cherry-picked qualitative and quantiative features of the model are compared to reality.
+
+We propose that a density matrix downfolding (DMD) approach using
+\textit{ab initio} quantum Monte Carlo calculations (QMC) can generate an effective model which can accurately describe low-energy properties and energetics for the infinite layer electron-doped cuprates at zero temperature and dopings of x=0, 0.125, 0.25.
+We choose to study the electron-doped cuprates because while they do not exhibit the exact same features as the hole-doped materials, they do have AFM,  superconducting, and "normal" metallic phases.
+Further, the electron-doped materials have fewer relevant degrees of freedom to worry, as electrons added to the x=0 CuO$_2$ plane can only fall into the unoccupied Cu 3d orbitals, allowing us to ignore the explicit inclusion of O p bands in our study.
+The choice of x=0, 0.125 and 0.25 at T=0 allows us to probe the most robust parts of the AFM, superconducting and metallic phases respectively, ignoring any thermal fluctuations or phase transitions like the LTO to LTT transition described earlier.
+The DMD downfolding approach allows us to map in a systematic way the \textit{ab initio} Hamiltonian to an effective model Hamiltonian, with specified model parameters and basis elements, in a way which ensures the model accurately reproduces the expectation value of the \textit{ab initio} Hamiltonian for states in a low-energy subspace of the full Hilbert space.
+In order to conduct the DMD procedure we require states in the low-energy subspace of the full \textit{ab initio} Hilbert space.
+These states will be sampled using fixed-node diffusion Monte Carlo, a QMC algorithm which can project out low-energy states starting with appropriate trial wave functions.
 
@@
 Once we have all of our low-energy states and important descriptors, we can simply conduct a linear regression to fit the coefficients of descriptors $f_i$, although other fitting approaches such as a LASSO fit can also be used [ref].
-\ref{fig1} shows the workflow of the DMD procedure. 
+\ref{fig2} shows the workflow of the DMD procedure. 
 We can increase the number of data points per wave function sample $\Psi_i$ by considering derivatives of the wave function and descriptors as well. 
@@
 \centering
+\includegraphics[width=0.6\textwidth]{Figures/I1-phase_diagram.pdf}
+\caption{\label{fig1} Phase diagram of Sr$_{1-x}$La$_x$CuO$_2$ for various electron doping \textit{x} and temperature \textit{T}. Figure taken from [ref]. \textbf{Add hole doped to this figure too.}}
+\end{figure}
+
+\begin{figure}[H]
+\centering
 \includegraphics[width=0.9\textwidth]{Figures/I2-DMD_flow.png}
-\caption{\label{fig1} Schematic drawing of the workflow for the density matrix downfolding technique, taken from [ref].}
+\caption{\label{fig2} Schematic drawing of the workflow for the density matrix downfolding technique, taken from [ref].}
 \end{figure}
@@
 %\begin{enumerate}
-%\item https://journals.aps.org/rmp/abstract/10.1103/RevModPhys.82.2421
+%\item https://journals.aps.org/rmp/abstract/10.1103/RevModPhys.82.2421 (Figure?)
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Introduction
+
+%Structural phase transitions
 %\item https://journals.aps.org/prl/abstract/10.1103/PhysRevLett.62.2751
+%\item https://journals.aps.org/prb/pdf/10.1103/PhysRevB.35.7191
+
+%Stripes 
 %\item https://www.nature.com/articles/375561a0
@@
 %\item https://journals.aps.org/prb/abstract/10.1103/PhysRevB.60.3643
-%\item https://www.nature.com/articles/nphys178
+
+%Magnons
+%INS - 10.1007-978-0-387-68734-6_6, Figure 6.3
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 %\end{enumerate}

### 2018-09-11 prelim/draft.tex
finished first rough ROUGH ROUGH draft, need to add references by 14th. then 2 weeks of editing before showing lucas

@@
 where $i,j$ are electron indices, $\alpha$ is a nuclear index, with a clamped nucleus approximation and psuedo-potentials for core electrons.  
-\textbf{Need to write down why it's better than other methods!}
+The DMD method allows us to generate an effective model for materials in a systematic way starting from the \textit{ab-initio} Hamiltonian with very little guess work, ensuring that each step has a physically motivated validation step.
+Also, the method comes with a built in measure of effectiveness of the low-energy model, namely the $R^2$ coefficient of determination between the \textit{ab initio} energies of low-energy states and the model energies.
+Finally, the DMD method not only generates a model, but also gives the best values for the model parameters and forms for basis elements in the model.
 
@@
 The time-step error is typically handled through a time-step extrapolation, where multiple FN-DMC calculations are conducted at sequentially smaller $\tau$ and the relevant expectation values are extrapolated to $\tau \rightarrow 0$ [ref].
-Fixed-node error can be managed through \textbf{do this!}
+Fixed-node error can be reduced by using optimized many-body trial wave functions of the (multi-)Slater-Jastrow form seen in [ref Umrigar 2007].
 
@@
 
-After the data generation phase is complete, we will focus on other interesting problems that can be solved apart from the low-energy effective model, such as generating effective single-particle band structures.
-\textit{\textbf{Need to do this}}.
-
 Further, we will use the DMD procedure to attempt to describe the differences between the isostructural nickelate and cuprate materials. 

### 2018-09-14 prelim/draft.tex
Added references, 64 so far

@@
 \usepackage{amsfonts}
+
 \begin{document}
@@
 The cuprate materials all share a similar structure of repeating layers of square lattice CuO$_2$ planes and charge reservoir blocks, of which carriers on the prior exhibit the most interesting collective behavior.
-At zero doping the cuprates are antiferromagnetic charge-transfer insulators [ref]. 
-The theoretical challenge arises away from zero doping where the poorly understood superconducting, pseudo-gap, strange metal and "normal" metal phases appear [ref]. 
+At zero doping the cuprates are antiferromagnetic charge-transfer insulators \cite{RevModPhys.78.17}. 
+The theoretical challenge arises away from zero doping where the poorly understood superconducting, pseudo-gap, strange metal phases appear \cite{RevModPhys.84.1383}. 
 \ref{fig1} shows the phase diagram of a hole- and electron-doped cuprate materials with different structures. 
-The superconducting phase is d-wave in character and cannot be described by phonon-induced pairings [ref]. 
-In the pseudo-gap phase the d-wave gap from the superconducting state continues to exist, however the material is now metallic in character [ref] \textbf{check this!}. 
-The strange metal phase is metallic but has a "strange" T-linear resistivity unlike typical metals which have quadratic-T resistivity at low temperatures [ref]. 
-The "normal" metallic phase exhibits the same single particle behavior expected of a Fermi-Landau-like metal, but the plasmon excitations are very different exhibiting self-similiarity in dispersion unlike the well defined plasmonic modes of the Fermi liquid [ref].
+The superconducting phase is d-wave in character and cannot be described by phonon-induced pairings \cite{PhysRevLett.71.2134,PhysRevLett.69.1431,PhysRevB.43.2778, PhysRevB.47.11314, PhysRevLett.70.1553, RevModPhys.67.515, RevModPhys.77.109, RevModPhys.79.353, RevModPhys.75.473}.
+In the pseudo-gap phase the d-wave gap from the superconducting state continues to partially exist, so that parts of the Fermi surface are gapped above the superconducting transition temperature \cite{ROSSATMIGNOD199186, RevModPhys.77.721, PhysRevLett.75.4114, PhysRevB.61.9752}.
+The strange metal phase in the hole doped cuprates is metallic but has a "strange" resistivity which does not depend quadratically on temperature like normal Fermi liquids \cite{PhysRevLett.69.2975}, but does have T-quadratic resitivity for the electron-doped materials \cite{1989PhyC..161..415T}.
 
 The strong coupling between magnetic, charge, and lattice degrees of freedom in the cuprates makes writing down an accurate low energy effective theory very challenging. 
-For example, in La$_{2-x}$Ba$_x$CuO$_4$ (LBCO) there is a structural phase transition as doping and temperature are varied between a high temperature tetragonal phase (HTT), a low-temperature orthorhombic phase (LTO) and a low temperature tetragonal phase (LTT), and the fraction of the bulk transformed material from LTO to LTT is correlated with the bulk superconducting temperature under various dopings [ref].
-An independent study shows that in La$_{2-x}$Sr$_x$CuO$_{4-\delta}$ (LSCO) the superconducting phase transition for x $<$ 0.19 is accompanied by a structural phase transition from the HTT to LTO phase [ref].
-Further, there is evidence for static stripe phase, where antiferromagnetic stripes of copper spins are separated by periodically spaced domain walls to which the holes segregate, in La$_{1.6-x}$Nd$_{0.4}$Sr$_x$CuO$_4$ at x=0.12 which is associated with an anomalous suppression in the superconducting temperature [two refs].
-Elastic magnetic measurements on La$_2$CuO$_{4+y}$ show the superconducting phase is accompanied by a spin-density wave emergence indicating a strong correlation between the two phases [ref]. 
-In the undoped phase of the cuprates the magnetic dispersion across the magnetic Brillouin zone strongly resembles that of spin-waves in a square Heisenberg antiferromagnet [ref], however within the superconducting phase the magnetic dispersion takes on an "hourglass" shape which has been reproduced in experiments for LSCO at x=0.10, 0.16 [ref, ref], LBCO at x=0.125 [ref], and YBa$_2$Cu$_3$O$_{6+x}$ at x=0.5, 0.6 [ref].
+For example, in La$_{2-x}$Ba$_x$CuO$_4$ (LBCO) there is a structural phase transition as doping and temperature are varied between a high temperature tetragonal phase (HTT), a low-temperature orthorhombic phase (LTO) and a low temperature tetragonal phase (LTT), and the fraction of the bulk transformed material from LTO to LTT is correlated with the bulk superconducting temperature under various dopings \cite{PhysRevLett.62.2751}.
+An independent study shows that in La$_{2-x}$Sr$_x$CuO$_{4-\delta}$ (LSCO) the superconducting phase transition for x $<$ 0.19 is accompanied by a structural phase transition from the HTT to LTO phase \cite{PhysRevB.35.7191}.
+Further, there is evidence for static stripe phase, where antiferromagnetic stripes of copper spins are separated by periodically spaced domain walls to which the holes segregate, in La$_{1.6-x}$Nd$_{0.4}$Sr$_x$CuO$_4$ at x=0.12 which is associated with an anomalous suppression in the superconducting temperature \cite{Tranquada1995, PhysRevB.54.7489}.
+Elastic magnetic measurements on La$_2$CuO$_{4+y}$ show the superconducting phase is accompanied by a spin-density wave emergence indicating a strong correlation between the two phases \cite{PhysRevB.60.3643}.
+In the undoped phase of the cuprates the magnetic dispersion across the magnetic Brillouin zone strongly resembles that of spin-waves in a square Heisenberg antiferromagnet \cite{PhysRevLett.104.077002, PhysRevLett.102.167401, PhysRevLett.105.157006}, however within the superconducting phase the magnetic dispersion takes on an "hourglass" shape which has been reproduced in experiments for LSCO at x=0.10, 0.16 \cite{PhysRevLett.93.147002}, LBCO at x=0.125 \cite{Tranquada2004}, and YBa$_2$Cu$_3$O$_{6+x}$ at x=0.5, 0.6 \cite{PhysRevB.71.024522, Hayden2004}.
 
 Many theoretical approaches to generating a low energy model for the cuprates which can account for the strong correlations between magnetic, lattice and charge degrees of freedom have been attempted with varying degrees of success.
-For the undoped cuprates a nearest neighbor Heisenberg model can reproduce the magnetic dispersions measured in inelastic neutron scattering experiments accurate away from the magnetic Brillouin zone boundary, but fail to capture the small effects of anomalous dispersion near the boundary [ref].
-%All refs for this part will be from Scalapino article "models"
-The simplest model for the hole-doped cuprates was suggested by Anderson and is a 2D single-band Hubbard model which only includes bands of Cu d$_{x^2-y^2}$ character, which will be hybridized with the oxygen bands to some degree [ref].
-This model is capable of producing the AFM phase at zero doping as in the strong coupling limit this model reduces to a nearest neighbor AFM Heisenberg model [ref]. 
-The model even exhibits a pseudo-gap like phase in the underdoped region [ref].
-Further, in the limit of $U/t \rightarrow 0$ the Hubbard model has a transition to a $d_{x^2-y^2}$ superconducting-like phase [ref].
-It has not been shown numerically that the superconducting order parameter is non-zero as the pair spacing is taken to be very large, however [ref]. 
-A similar model is the t-J model [ref, Elbio Dagatto] which is built on the idea that under doping there are itinerant holes which hop around the oxygen bands alongside the fixed S=1/2 moments on the copper sites which interact through a superexchange term with parameter J.
+For the undoped cuprates a nearest neighbor Heisenberg model can reproduce the magnetic dispersions measured in inelastic neutron scattering experiments accurate away from the magnetic Brillouin zone boundary, but fail to capture the small effects of anomalous dispersion near the boundary \cite{PhysRevB.79.155114, PhysRevLett.75.553}.
+The simplest model for the hole-doped cuprates was suggested by Anderson and is a 2D single-band Hubbard model which only includes bands of Cu d$_{x^2-y^2}$ character, which will be hybridized with the oxygen bands to some degree.
+In the strong coupling limit at half filling and T=0 this model reduces to a nearest neighbor Heisenberg model with long-range AFM order \cite{doi:10.1139/p78-120, PhysRevB.38.316}.
+The model even exhibits a pseudo-gap like phase in the underdoped region \cite{PhysRevLett.94.156404,PhysRevB.74.024508}. 
+Further, numerical studies on the Hubbard model show the existence of a $d_{x^2-y^2}$ superconducting-like phase \cite{PhysRevB.81.224505, PhysRevB.70.054504}. 
+A similar model is the t-J model  which is built on the idea that under doping there are itinerant holes which hop around the oxygen bands alongside the fixed S=1/2 moments on the copper sites which interact through a superexchange term with parameter J.
 The t-J model can be seen as an effective theory of the single band t-U model. 
-This model exhibits superconductivity proper at J/t $\sim$ 3 with a density of $\langle n \rangle$ = 1/2 [ref], meaning that the pairing function does not vanish in the large spacing limit. 
+This model exhibits superconductivity at J/t $\sim$ 3 with a density of $\langle n \rangle$ = 1/2 \cite{PhysRevB.45.5744, PhysRevLett.70.682}.
 While these models have fewer degrees of freedom and thus allow for quick numerical computations, it has been shown in accurate \textit{ab initio} Quantum Monte Carlo calculations that holes move to the oxygen bands under doping, indicating that an effective theory should include the oxygen bands explicitly not implicity inclusion via hybridization.
-This leads to a 2D 3-band Hubbard model which includes the Cu 3$d_{x^2-y^2}$ and O p bands [ref, Elbio Dagatto] and exhibits qualitatively similar behavior to the 1-band model. 
+This leads to a 2D 3-band Hubbard model which includes the Cu 3$d_{x^2-y^2}$ and O p bands \cite{PhysRevLett.58.2794, VARMA1987681} and exhibits qualitatively similar behavior to the 1-band model. 
 However, these approaches to generating a low-energy model have two inherent flaws. 
@@
 
-We propose that a density matrix downfolding (DMD) approach using
-\textit{ab initio} quantum Monte Carlo calculations (QMC) can generate an effective model which can accurately describe low-energy properties and energetics for the infinite layer electron-doped cuprates at zero temperature and dopings of x=0, 0.125, 0.25.
+We propose that a density matrix downfolding (DMD) \cite{10.3389/fphy.2018.00043, doi:10.1063/1.4927664} using \textit{ab initio} quantum Monte Carlo calculations (QMC) can generate an effective model which can accurately describe low-energy properties and energetics for the infinite layer electron-doped cuprates at zero temperature and dopings of x=0, 0.125, 0.25.
 We choose to study the electron-doped cuprates because while they do not exhibit the exact same features as the hole-doped materials, they do have AFM,  superconducting, and "normal" metallic phases. 
@@
 In order to conduct the DMD procedure we require states in the low-energy subspace of the full \textit{ab initio} Hilbert space. 
-These states will be sampled using fixed-node diffusion Monte Carlo, a QMC algorithm which can project out low-energy states starting with appropriate trial wave functions.
+These states will be sampled using fixed-node diffusion Monte Carlo, a QMC algorithm which can project out low-energy states starting with appropriate trial wave functions \cite{RevModPhys.73.33}.
 
-The density matrix downfolding method (DMD) allows us to downfold a first-principles Hamiltonian into a low-energy effective theory by mapping the downfolding problem to a linear regression problem which uses ab-initio energies and reduced density matrices of wave functions sampled from a low-energy subspace of the full Hilbert space [ref].
+The density matrix downfolding method (DMD) allows us to downfold a first-principles Hamiltonian into a low-energy effective theory by mapping the downfolding problem to a linear regression problem which uses ab-initio energies and reduced density matrices of wave functions sampled from a low-energy subspace of the full Hilbert space \cite{10.3389/fphy.2018.00043}.
 Consider a Hamiltonian H which acts on vectors in a Hilbert space $\mathcal{H}$ and a subset of the Hilbert space $\mathcal{LE}$ which is spanned by the lowest N energy eigenvectors of H. 
 We would like to write down an effective Hamiltonian operator which acts on vectors in $\mathcal{LE}$ such that  $$\forall |\Psi\rangle \in \mathcal{LE}, H_{eff}|\Psi \rangle = H|\Psi \rangle.$$ 
-It can be shown that this statement is equivalent to requiring that $$ E[\Psi] = E_{eff}[\Psi] + C \forall \Psi \in \mathcal{LE}$$ where we define the functional as $E[\Psi] = \frac{\langle \Psi | H | \Psi \rangle}{\langle \Psi | \Psi \rangle},E_{eff}[\Psi] = \frac{\langle \Psi | H_{eff} | \Psi \rangle}{\langle \Psi | \Psi \rangle}$ [ref].
+It can be shown that this statement is equivalent to requiring that $$ E[\Psi] = E_{eff}[\Psi] + C \forall \Psi \in \mathcal{LE}$$ where we define the functional as $E[\Psi] = \frac{\langle \Psi | H | \Psi \rangle}{\langle \Psi | \Psi \rangle},E_{eff}[\Psi] = \frac{\langle \Psi | H_{eff} | \Psi \rangle}{\langle \Psi | \Psi \rangle}$.
 The obvious choice that would satisfy these constraints would simply be $H_{eff} = \sum_{i=1}^{N} E_i |\Psi_i\rangle \langle \Psi_i|$, but this would require us to be able to solve for the eigenstates and eigenvalues of the many-body Hamiltonian H, which we presumably cannot do.
@@
 Generally we will begin the DMD procedure by generating low energy states $\Psi_i$ within the space $\mathcal{LE}$. 
-Generating these states is somewhat problem dependent and will be discussed later on for the specific case of SrCuO$_2$. 
 Additionally, we need to generate a set of descriptors $d_j$. 
@@
 In either case we may have to return to the low-energy state sampling or descriptor choosing step until we are satisfied.
-Once we have all of our low-energy states and important descriptors, we can simply conduct a linear regression to fit the coefficients of descriptors $f_i$, although other fitting approaches such as a LASSO fit can also be used [ref].
+Once we have all of our low-energy states and important descriptors, we can simply conduct a linear regression to fit the coefficients of descriptors $f_i$, although other fitting approaches such as a LASSO fit can also be used \cite{10.2307/2346178}.
 \ref{fig2} shows the workflow of the DMD procedure. 
@@
 Therefore the FN-DMC calculation has two major systematic errors that have to be dealt with, the fixed-node error and the time-step error. 
-The time-step error is typically handled through a time-step extrapolation, where multiple FN-DMC calculations are conducted at sequentially smaller $\tau$ and the relevant expectation values are extrapolated to $\tau \rightarrow 0$ [ref].
-Fixed-node error can be reduced by using optimized many-body trial wave functions of the (multi-)Slater-Jastrow form seen in [ref Umrigar 2007].
+The time-step error is typically handled through a time-step extrapolation, where multiple FN-DMC calculations are conducted at sequentially smaller $\tau$ and the relevant expectation values are extrapolated to $\tau \rightarrow 0$ \cite{Needs2010}.
+Fixed-node error can be reduced by using optimized many-body trial wave functions of the (multi-)Slater-Jastrow form seen in \cite{PhysRevLett.98.110201}.
 
@@
 \centering
-\includegraphics[width=0.6\textwidth]{Figures/I1-phase_diagram.pdf}
-\caption{\label{fig1} Phase diagram of Sr$_{1-x}$La$_x$CuO$_2$ for various electron doping \textit{x} and temperature \textit{T}. Figure taken from [ref]. \textbf{Add hole doped to this figure too.}}
+\includegraphics[width=0.6\textwidth]{Figures/I1-phase_diagram.png}
+\caption{\label{fig1} Phase diagrams of the hole-doped cuprate LSCO and electron-doped cuprate family R$_{2-x}$Ce$_{x}$CuO$_4$\textit{x} and temperature \textit{T}.
+Figure taken from \cite{Armitage2010}.
+}
 \end{figure}
@@
 \includegraphics[width=0.9\textwidth]{Figures/I2-DMD_flow.png}
-\caption{\label{fig2} Schematic drawing of the workflow for the density matrix downfolding technique, taken from [ref].}
+\caption{\label{fig2} Schematic drawing of the workflow for the density matrix downfolding technique, taken from \cite{10.3389/fphy.2018.00043}.}
 \end{figure}
@@
 \section{Preliminary results}
-In order to become acquainted with our code QWalk [ref QWalk] and QMC algorithms in general I worked on implementing and testing multi-Slater-Jastrow trial functions with optimized non-orthogonal determinants (MSJ+NO) in FN-DMC [ref my paper].
+In order to become acquainted with our code QWalk \cite{WAGNER20093390} and QMC algorithms in general I worked on implementing and testing multi-Slater-Jastrow trial functions with optimized non-orthogonal determinants (MSJ+NO) in FN-DMC \cite{Pathak2018}.
 We assessed the efficiency and compactness of this new trial function by calculating the ground state energy and single particle densities of a C$_2$ molecule using FN-DMC and comparing to the results when using multi-Slater-Jastrow trial functions with optimized orthogonal determinant trial functions (MSJ+O).
-The workflow involved constructing the un-optimized trial wave functions, optimizing the parameters using an energy optimization method [ref], and finally using the optimized trial functions in an FN-DMC calculation.
+The workflow involved constructing the un-optimized trial wave functions, optimizing the parameters using an energy optimization method \cite{Toulouse2007}, and finally using the optimized trial functions in an FN-DMC calculation.
 We found that the FN-DMC energy calculated using an MSJ+NO trial function with only 24 determinants was lower than the FN-DMC energy using an MSJ+O trial function with 55 determinants. 
@@
 We conducted this \textit{ad hoc} fitting procedure for SrCuO$_2$ under three different dopings x=0, 0.125, and 0.25 using the PBE0 functional in DFT on a 2$\sqrt{2}$x2$\sqrt{2}$x1 unit cell. 
-The PBE0 functional has been used within QMC in the past to yield accurate results for low-energy properties and energies on the hole-doped cuprates [ref]. 
+The PBE0 functional has been used within QMC in the past to yield accurate results for low-energy properties and energies on the hole-doped cuprates \cite{Wagner2015,Narayan2017,Wagner2014}. 
 The eight unit cell calculation was chosen since it is small enough to be computationally feasible even when moving to QMC, but large enough that the finite size effects are not too large. 
@@
 One excited state in this energy range was discarded because it was insulating in character while the other four were metallic. 
-This may have occured since PBE0 has been shown to incorrectly order states energetically for strongly correlated systems [ref]. 
+This may have occured since PBE0 has been shown to incorrectly order states energetically for strongly correlated systems.
 For the x=0.25 calculations, the PBE0 ground state was a collinear state, and the four low-energy states we chose were states with total energy less than 0.30 eV above this ground state. 
@@
 The operators $\vec{S_i}$ represent the spin moment on the copper sites and $c_i^\dagger$ the itinerant electrons hopping around copper sites. 
-The last term is a Heisenberg exchange which we included since the undoped material can be modeled fairly accurately with just a nearest neighbor Heisenberg model with J = 0.18 eV [ref]. 
+The last term is a Heisenberg exchange which we included since the undoped material can be modeled fairly accurately with just a nearest neighbor Heisenberg model with J = 0.18 eV \cite{Wagner2014}. 
 The first two terms are nearest neighbor and next-nearest neighbor hopping which are both required to capture the curvature of the PBE0 bands crossing the Fermi level for the x=0.125 and x=0.25 low-energy states.
@@
 This complicates our model representation because we typically work with models where creation and annihilation operators generate orthogonal states. 
-Therefore, what we are looking for are orbitals that are maximally localized and still orthogonal to one another, and this is precisely what the IAO is [ref]. 
+Therefore, what we are looking for are orbitals that are maximally localized and still orthogonal to one another, and this is precisely what the IAO is \cite{doi:10.1021/ct400687b}. 
 In order to test whether the IAO basis is sufficient at spanning the space of excitations we are interested in, we looked at the 1-body reduced density matrix (1RDM) relative to the IAO basis for each x=0, 0.125 and 0.25 low-energy state chosen above.
@@
 has two core parts, the multi-determinant expansion with determinant coefficients $c_I$ and a 3-body Jastrow factor with some Jastrow coefficients $\alpha$. 
-These parameters will be optimized using an energy optimization method described by [ref]. 
+These parameters will be optimized using an energy optimization method described by \cite{Toulouse2007}. 
 The determinants will be composed of single particle orbitals from the eight unit cell DFT calculations we have already completed.	
@@
 After generating these trial wave functions we can use FN-DMC to project out a low-energy state within the \textit{ab initio} Hilbert space, calculate the total FN-DMC energy, 1- and 2-body reduced density matrices using the IAO basis that we have already generated, as well as derivatives of the total energy and the density matrices with respect to the determinant coefficients $c_I$.
-We will not consider derivatives with respect to the Jastrow coefficients because that derivative will take us outside of the low-energy space, as the Jastrow factor significantly reduces the total energy of a trial state [ref].
+We will not consider derivatives with respect to the Jastrow coefficients because that derivative will take us outside of the low-energy space, as the Jastrow factor significantly reduces the total energy of a trial state \cite{PhysRevLett.75.3870}.
 
@@
 The first tool in reducing the space of relevant descriptors is through symmetry considerations.
-[ref] provides a useful manual for the terms that any 1- and 2-body Hamiltonian can have given the symmetry of the bands that are under consideration.
+Coury \textit{et al} \cite{Coury2016} provides a useful manual for the terms that any 1- and 2-body Hamiltonian can have given the symmetry of the bands that are under consideration.
 From here we arrive at a basic statistics problem of generating a linear model given a potential set of descriptors. 
@@
 We can then manually choose a model which has a large $R^2$ with a relatively small model complexity. 
-This choice can also be made systematically by using an Akaike information criterion or Bayesian information criterion to measure the goodness of fit at each step of the greedy algorithm instead of a simple least-square measure of goodness.
-These two criteria penalize a model not only for the least-square measure of goodness but also for model complexity [ref].
+This choice can also be made systematically by using an Akaike information criterion \cite{ref591} or Bayesian information criterion \cite{schwarz1978} to measure the goodness of fit at each step of the greedy algorithm instead of a simple least-square measure of goodness.
+These two criteria penalize a model not only for the least-square measure of goodness but also for model complexity.
 
@@
 To deal with finite size effects affecting single particle properties a common choice is to use twist-averaging. 
-This means conducting the many-body FN-DMC calculation using various twisted boundary conditions and then averaging over the results of the single-particle expectation values [ref].
+This means conducting the many-body FN-DMC calculation using various twisted boundary conditions and then averaging over the results of the single-particle expectation values \cite{Lin2001, PhysRevB.78.125106}.
 This is equivalent to averaging over the many-body Brillouin zone. 
-To account for two-particle or higher order finite size effects, such as those affecting the Coulumb interaction term when calculating the total energy, a finite size extrapolation is required. 
+To account for two-particle or higher order finite size effects, such as those affecting the Coulomb interaction term when calculating the total energy, a finite size extrapolation is required. 
 This involves conducting the FN-DMC calculations for a sequence of increasing calculation cell size, and then extrapolating the results of expectation values to the infinite cell size. 
-The extrapolation scales linearly with the cell volume [ref].
+The extrapolation scales linearly with the cell volume \cite{PhysRevB.78.125106}.
 
@@
 Shown in \ref{fig6} are the conventional unit cells of the cuprate La$_2$CuO$_4$ and the nickelate La$_2$NiO$_4$, which are identical except that the copper atom within the cell is replaced by a nickel atom.
-While isostructural, the nickelates have been shown to not superconduct even down to temperatures of mK [ref] under doping. 
+While isostructural, the nickelates have been shown to not superconduct even down to temperatures of mK \cite{PhysRevB.43.1229} under doping. 
 In order to study this distinct difference in low-energy behavior, we will use the DMD procedure listed above in an identical fashion on the material SrNiO$_2$. 
@@
 If we consider a slightly higher energy cutoff for our low-energy theory, it may be possible that our DMD procedure generates an effective theory with identical descriptors but different model parameters.
-The reasoning behind this argument stems from the fact that effective models like the Hubbard model can yield various low-energy effective theories when considered under certain parameter regimes [ref], meaning that two materials can, at the lowest energy scales, have drastically different low-energy theories while at a higher energy scales be described accurately by similar effective theories.
+The reasoning behind this argument stems from the fact that effective models like the Hubbard model can yield various low-energy effective theories when considered under certain parameter regimes, meaning that two materials can, at the lowest energy scales, have drastically different low-energy theories while at a higher energy scales be described accurately by similar effective theories.
 Having a single model which can describe the low-energy behavior of both of these materials would provide a big step forwards to understanding the emergence of superconductivity in the cuprates and the lack thereof in the nickelates.
@@
 \includegraphics[width=0.9\textwidth]{Figures/P2-Ni_Cu.pdf}
-\caption{\label{fig6} The primitive unit cells of the isostructural materials LNCO [ref] and LSCO [ref], the prior which is not super conducting all the way to temperatures of 30mK [ref].}
+\caption{\label{fig6} The primitive unit cells of the isostructural materials LNCO \cite{PhysRevB.92.205114} and LSCO \cite{Scalapino2012}, the prior which is not super conducting all the way to temperatures of 30mK.}
 \end{figure}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Introduction
-
-%Structural phase transitions
-%\item https://journals.aps.org/prl/abstract/10.1103/PhysRevLett.62.2751
-%\item https://journals.aps.org/prb/pdf/10.1103/PhysRevB.35.7191
-
-%Stripes 
-%\item https://www.nature.com/articles/375561a0
-%\item https://journals.aps.org/prb/abstract/10.1103/PhysRevB.54.7489
-%\item https://journals.aps.org/prb/abstract/10.1103/PhysRevB.60.3643
-
-%Magnons
-%INS - 10.1007-978-0-387-68734-6_6, Figure 6.3
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 %\end{enumerate}
 
+\bibliographystyle{unsrt}
+\bibliography{biblio}
+
 \end{document}

### 2018-09-19 prelim/draft.tex
Prelim draft intro looking good, need to do last 2 paragraphs;

@@
 \section{Introduction} 
-Understanding the low energy behavior of the cuprate superconductors has been an open question in theoretical condensed matter physics for over thirty years. 
+\textbf{Understanding the low energy behavior of the cuprate superconductors has been an open question in theoretical condensed matter physics for over thirty years.}
 The cuprate materials all share a similar structure of repeating layers of square lattice CuO$_2$ planes and charge reservoir blocks, of which carriers on the prior exhibit the most interesting collective behavior.
 At zero doping the cuprates are antiferromagnetic charge-transfer insulators \cite{RevModPhys.78.17}. 
-The theoretical challenge arises away from zero doping where the poorly understood superconducting, pseudo-gap, strange metal phases appear \cite{RevModPhys.84.1383}. 
-\ref{fig1} shows the phase diagram of a hole- and electron-doped cuprate materials with different structures. 
+The theoretical challenge arises away from zero doping where the poorly understood superconducting, pseudo-gap, and strange metal phases appear \cite{RevModPhys.84.1383}. 
+\ref{fig1} shows the phase diagram of hole- and electron-doped cuprate materials with different structures. 
 The superconducting phase is d-wave in character and cannot be described by phonon-induced pairings \cite{PhysRevLett.71.2134,PhysRevLett.69.1431,PhysRevB.43.2778, PhysRevB.47.11314, PhysRevLett.70.1553, RevModPhys.67.515, RevModPhys.77.109, RevModPhys.79.353, RevModPhys.75.473}.
@@
 
-The strong coupling between magnetic, charge, and lattice degrees of freedom in the cuprates makes writing down an accurate low energy effective theory very challenging. 
-For example, in La$_{2-x}$Ba$_x$CuO$_4$ (LBCO) there is a structural phase transition as doping and temperature are varied between a high temperature tetragonal phase (HTT), a low-temperature orthorhombic phase (LTO) and a low temperature tetragonal phase (LTT), and the fraction of the bulk transformed material from LTO to LTT is correlated with the bulk superconducting temperature under various dopings \cite{PhysRevLett.62.2751}.
+\textbf{The strong coupling between magnetic, charge, and lattice degrees of freedom in the cuprates makes writing down a compact and accurate low energy effective theory which can describe the breadth of phenomenon related to these degrees of freedom very challenging.}
+As an example of strong coupling, consider the structural phase transitions in cuprates which accompany the superconducting transition.
+In La$_{2-x}$Ba$_x$CuO$_4$ (LBCO) structural phase transitions occur as doping and temperature are varied between a high temperature tetragonal phase (HTT), a low-temperature orthorhombic phase (LTO) and a low temperature tetragonal phase (LTT), and the fraction of the bulk transformed material from LTO to LTT is correlated with the bulk superconducting temperature under various dopings \cite{PhysRevLett.62.2751}.
 An independent study shows that in La$_{2-x}$Sr$_x$CuO$_{4-\delta}$ (LSCO) the superconducting phase transition for x $<$ 0.19 is accompanied by a structural phase transition from the HTT to LTO phase \cite{PhysRevB.35.7191}.
-Further, there is evidence for static stripe phase, where antiferromagnetic stripes of copper spins are separated by periodically spaced domain walls to which the holes segregate, in La$_{1.6-x}$Nd$_{0.4}$Sr$_x$CuO$_4$ at x=0.12 which is associated with an anomalous suppression in the superconducting temperature \cite{Tranquada1995, PhysRevB.54.7489}.
+Similarly, changes in magnetic phases and properties appear to be correlated with the superconducting phase, again providing evidence for strong coupling of microscopic degrees of freedom.
+For example, there is evidence for a static stripe phase, where antiferromagnetic stripes of copper spins are separated by periodically spaced domain walls to which the holes segregate, in La$_{1.6-x}$Nd$_{0.4}$Sr$_x$CuO$_4$ at x=0.12 which is associated with an anomalous suppression in the superconducting temperature \cite{Tranquada1995, PhysRevB.54.7489}.
 Elastic magnetic measurements on La$_2$CuO$_{4+y}$ show the superconducting phase is accompanied by a spin-density wave emergence indicating a strong correlation between the two phases \cite{PhysRevB.60.3643}.
 In the undoped phase of the cuprates the magnetic dispersion across the magnetic Brillouin zone strongly resembles that of spin-waves in a square Heisenberg antiferromagnet \cite{PhysRevLett.104.077002, PhysRevLett.102.167401, PhysRevLett.105.157006}, however within the superconducting phase the magnetic dispersion takes on an "hourglass" shape which has been reproduced in experiments for LSCO at x=0.10, 0.16 \cite{PhysRevLett.93.147002}, LBCO at x=0.125 \cite{Tranquada2004}, and YBa$_2$Cu$_3$O$_{6+x}$ at x=0.5, 0.6 \cite{PhysRevB.71.024522, Hayden2004}.
+These experiments indicate that in order to write down a low-energy model for the cuprates, one has to generate effective degrees of freedom and interactions which are complicated combinations of the microscopic lattice, charge, and spin degrees of freedom.
+The strong coupling between the microscopic degrees of freedom indicate that these combinations cannot be approached in a perturbative fashion from either the weak or very-strong coupling limit.
 
-Many theoretical approaches to generating a low energy model for the cuprates which can account for the strong correlations between magnetic, lattice and charge degrees of freedom have been attempted with varying degrees of success.
-For the undoped cuprates a nearest neighbor Heisenberg model can reproduce the magnetic dispersions measured in inelastic neutron scattering experiments accurate away from the magnetic Brillouin zone boundary, but fail to capture the small effects of anomalous dispersion near the boundary \cite{PhysRevB.79.155114, PhysRevLett.75.553}.
+\textbf{Various models have been proposed and studied as candidates for effective theories of the cuprates, however these models were neither developed nor validated in a systematic way.}
+For the undoped cuprates a nearest neighbor Heisenberg model can reproduce the magnetic dispersions measured in inelastic neutron scattering experiments accurately away from the magnetic Brillouin zone boundary, but fail to capture the small effects of anomalous dispersion near the boundary \cite{PhysRevB.79.155114, PhysRevLett.75.553}.
 The simplest model for the hole-doped cuprates was suggested by Anderson and is a 2D single-band Hubbard model which only includes bands of Cu d$_{x^2-y^2}$ character, which will be hybridized with the oxygen bands to some degree.
@@
 This model exhibits superconductivity at J/t $\sim$ 3 with a density of $\langle n \rangle$ = 1/2 \cite{PhysRevB.45.5744, PhysRevLett.70.682}.
-While these models have fewer degrees of freedom and thus allow for quick numerical computations, it has been shown in accurate \textit{ab initio} Quantum Monte Carlo calculations that holes move to the oxygen bands under doping, indicating that an effective theory should include the oxygen bands explicitly not implicity inclusion via hybridization.
+While these models have fewer degrees of freedom and thus allow for quick numerical computations, it has been shown in accurate \textit{ab initio} Quantum Monte Carlo calculations that holes move to the oxygen bands under doping, indicating that an effective theory should include the oxygen bands explicitly, not implicity via hybridization.
 This leads to a 2D 3-band Hubbard model which includes the Cu 3$d_{x^2-y^2}$ and O p bands \cite{PhysRevLett.58.2794, VARMA1987681} and exhibits qualitatively similar behavior to the 1-band model. 
-However, these approaches to generating a low-energy model have two inherent flaws. 
-First, the model parameters are not specified with the model, meaning that seeing whether the model can accurately describe the cuprates involves mapping the entire parameter space. 
-Second, there is no standard measure of effectiveness of the models under question: some cherry-picked qualitative and quantiative features of the model are compared to reality.
+However, these approaches to generating a low-energy model have multiple issues.
+First, generating the model - specifically the effective degrees of freedom, interactions and model parameters - was not done systematically, rather the choice of effective model was \textit{ad hoc}.
+Second, there is no standard measure of effectiveness of the models under question. 
+Typically, just a few qualitative and quantitative features of the model are compared to reality as a form of validation.
 
-We propose that a density matrix downfolding (DMD) \cite{10.3389/fphy.2018.00043, doi:10.1063/1.4927664} using \textit{ab initio} quantum Monte Carlo calculations (QMC) can generate an effective model which can accurately describe low-energy properties and energetics for the infinite layer electron-doped cuprates at zero temperature and dopings of x=0, 0.125, 0.25.
-We choose to study the electron-doped cuprates because while they do not exhibit the exact same features as the hole-doped materials, they do have AFM,  superconducting, and "normal" metallic phases. 
-Further, the electron-doped materials have fewer relevant degrees of freedom to worry, as electrons added to the x=0 CuO$_2$ plane can only fall into the unoccupied Cu 3d orbitals, allowing us to ignore the explicit inclusion of O p bands in our study.
+\textbf{We propose that a density matrix downfolding (DMD) \cite{10.3389/fphy.2018.00043, doi:10.1063/1.4927664} technique using \textit{ab initio} quantum Monte Carlo calculations (QMC) can systematically generate an effective model that accurately describes the low-energy properties of cuprate materials, which we will test on the electron-doped cuprate SrCuO$_2$ at T=0 and x=0, 0.125, 0.25.
+}
+We choose to study the electron-doped cuprates because while they do not exhibit the exact same features as the hole-doped materials, they do have AFM,  superconducting, and pseudo-gap phases.
+Further, the electron-doped materials have fewer relevant degrees of freedom, as electrons added to the x=0 CuO$_2$ plane can only fall into the unoccupied Cu 3d orbitals, allowing us to ignore the explicit inclusion of O p bands in our study.
 The choice of x=0, 0.125 and 0.25 at T=0 allows us to probe the most robust parts of the AFM, superconducting and metallic phases respectively, ignoring any thermal fluctuations or phase transitions like the LTO to LTT transition described earlier.
-The DMD downfolding approach allows us to map in a systematic way the \textit{ab initio} Hamiltonian to an effective model Hamiltonian, with specified model parameters and basis elements, in a way which ensures the model accurately reproduces the expectation value of the \textit{ab initio} Hamiltonian for states in a low-energy subspace of the full Hilbert space.
-In order to conduct the DMD procedure we require states in the low-energy subspace of the full \textit{ab initio} Hilbert space. 
-These states will be sampled using fixed-node diffusion Monte Carlo, a QMC algorithm which can project out low-energy states starting with appropriate trial wave functions \cite{RevModPhys.73.33}.
+In order to reduce the computational cost we look at the infinite-layer materials which have unit cells with the fewest number of electrons within the cuprate family.
+The DMD approach allows us to map in a systematic way the \textit{ab initio} Hamiltonian to an effective model Hamiltonian, with specified model parameters and basis elements, while ensuring the model accurately reproduces the expectation value of the \textit{ab initio} Hamiltonian for states in a low-energy subspace of the full Hilbert space.
+The DMD approach also has a validation procedure which allows us to assess the effectiveness of the low-energy model in a standardized way.
+In order to conduct the DMD procedure we require states in the low-energy subspace of the full \textit{ab initio} Hilbert space, which will be sampled using fixed-node diffusion Monte Carlo, a QMC algorithm which can project out low-energy states starting with appropriate trial wave functions \cite{RevModPhys.73.33}.
 
-The density matrix downfolding method (DMD) allows us to downfold a first-principles Hamiltonian into a low-energy effective theory by mapping the downfolding problem to a linear regression problem which uses ab-initio energies and reduced density matrices of wave functions sampled from a low-energy subspace of the full Hilbert space \cite{10.3389/fphy.2018.00043}.
+\textbf{The density matrix downfolding method (DMD) allows us to downfold a first-principles Hamiltonian into a low-energy effective theory by mapping the downfolding problem to a linear regression problem which uses ab-initio energies and reduced density matrices of wave functions sampled from a low-energy subspace of the full Hilbert space \cite{10.3389/fphy.2018.00043}.
+}
 Consider a Hamiltonian H which acts on vectors in a Hilbert space $\mathcal{H}$ and a subset of the Hilbert space $\mathcal{LE}$ which is spanned by the lowest N energy eigenvectors of H. 
@@
 
-We will use fixed node diffusion Monte Carlo (FN-DMC) to generate
-wave functions in our chosen low-energy subspace and to accurately calculate ab-initio energies and reduced density matrices. 
+\textbf{We will use fixed node diffusion Monte Carlo (FN-DMC) to generate
+wave functions in our chosen low-energy subspace and to accurately calculate ab-initio energies and reduced density matrices. }
 Diffusion Monte Carlo (DMC) is a quantum Monte Carlo method which projects out the ground state of a Hamiltonian given some initial trial wave function. 

### 2018-09-19 prelim/draft.tex
Introduction cleaned, need to add DMC RDMs and mixed estimator

@@
 The next step is to assess whether the set of descriptors we chose and the set of states sampled are complete or not. 
-For example, we might find that we have two states $\Psi_1, \Psi_2$ which have very similar descriptor values but very different energies (but both within the low-energy space), then it is clear that our descriptor set does not capture the variation of the energy within the space $\mathcal{LE}$ and a different descriptor must be included.
+For example, we might find that we have two states $\Psi_1, \Psi_2$ which have very similar descriptor values but very different energies (within the low-energy space), then it is clear that our descriptor set does not capture the variation of the energy within the space $\mathcal{LE}$ and a different descriptor must be included.
 If instead we find that we have many low-energy states with very similar energies and descriptor sets then our sampling of the low-energy space may be incomplete as we are not capturing the full variation of the descriptors we are interested in.
 In either case we may have to return to the low-energy state sampling or descriptor choosing step until we are satisfied.
-Once we have all of our low-energy states and important descriptors, we can simply conduct a linear regression to fit the coefficients of descriptors $f_i$, although other fitting approaches such as a LASSO fit can also be used \cite{10.2307/2346178}.
+Once we have all of our low-energy states and important descriptors, we can simply conduct a linear regression to fit the optimal coefficients $f_j^*$ by minimizing a mean-square error (MSE) cost function:
+\begin{equation}
+f^{*} = argmin \Big[ \sum_{i=1}^{N} ( E[\Psi_i] - \sum_j f_j d_j[\Psi_i])^2  \Big],
+\end{equation}
+although other fitting approaches such as a LASSO fit can also be used \cite{10.2307/2346178}.
+The $R^2$ of the fit can be used to validate the fit if using the MSE cost function, whereas different measures of goodness-of-fit are appropriate for other cost functions.
 \ref{fig2} shows the workflow of the DMD procedure.
-We can increase the number of data points per wave function sample $\Psi_i$ by considering derivatives of the wave function and descriptors as well. 
-Insofar each wave function provides one data point for linear regression, however if we parameterize the wave function $\Psi_i(\vec{p})$ then we can generate N data points for the fitting where N is the number of parameters by simply taking a derivative of the left and right hand sides of equation (1) with respect to the parameters $p_i$.
-Therefore including parameter derivatives in our fitting procedure can increase the efficiency N fold, decreasing the number of low-energy states that need to be sampled. 
+Insofar each wave function provides one data point for linear regression, however if we parameterize the wave function $\Psi_i(\vec{p})$, where $\vec{p}$ are some parameters within the wave function that can be varied without moving out of $\mathcal{LE}$, then we can generate N$_p$+1 data points per wave function where N$_p$ is the number of parameters.
+This is accomplished by taking a derivative of the left and right hand sides of equation (1) with respect to the parameters $p_i$, and then minimizing a cost function like:
+\begin{equation}
+f^{*} = argmin \Bigg[ \sum_{i=1}^{N} \Big(\sum_{p=0}^{N_p} ( E^{(p)}[\Psi_i] - \sum_j f_j d_j^{(p)}[\Psi_i])^2 \Big) \Bigg],
+\end{equation}
+where $E^{(0)}[\Psi] = E[\Psi], d^{(0)}[\Psi]= d[\Psi], E^{(p)}[\Psi]=\frac{\partial E[\Psi]}{\partial p_p}, d^{(p)}[\Psi]=\frac{\partial d[\Psi]}{\partial p_p}, p\in [1,N_p].$
+Therefore including parameter derivatives in our fitting procedure can increase the efficiency N$_p$ fold, decreasing the number of low-energy states that need to be sampled. 
 For our situation the Hamiltonian H is the \textit{ab initio} Hamiltonian 
@@
 where $i,j$ are electron indices, $\alpha$ is a nuclear index, with a clamped nucleus approximation and psuedo-potentials for core electrons.
-The DMD method allows us to generate an effective model for materials in a systematic way starting from the \textit{ab-initio} Hamiltonian with very little guess work, ensuring that each step has a physically motivated validation step.
-Also, the method comes with a built in measure of effectiveness of the low-energy model, namely the $R^2$ coefficient of determination between the \textit{ab initio} energies of low-energy states and the model energies.
-Finally, the DMD method not only generates a model, but also gives the best values for the model parameters and forms for basis elements in the model.
 
@@
 Fixed-node error can be reduced by using optimized many-body trial wave functions of the (multi-)Slater-Jastrow form seen in \cite{PhysRevLett.98.110201}.
+\textbf{Need to add RDMs in DMC, mixed estimator error.}
 

### 2018-09-21 prelim/draft.tex
added section on DMC RDMs and mixed estimator

@@
 Fixed-node error can be reduced by using optimized many-body trial wave functions of the (multi-)Slater-Jastrow form seen in \cite{PhysRevLett.98.110201}.
-\textbf{Need to add RDMs in DMC, mixed estimator error.}
+We can use the final FN-DMC state to calculate the expectation values of operators like the Hamiltonian or reduced density matrices.
+For an operator $\hat{O}$ we will use a mixed estimator to calculate the expectation value $\langle \Psi_{DMC} |\hat{O} | \Psi_T \rangle/\langle \Psi_{DMC} | \Psi_T \rangle$ where $\Psi_{DMC}$ is the projected FN-DMC state starting with the trial wave function $\Psi_T$, as this estimator allows us to use the importance sampled distribution $f = \Psi_{DMC}\Psi_T$ for our Monte Carlo estimates.
+For operators which do not commute with the Hamiltonian H the mixed estimator has an error which can be corrected to first order by subtracting twice the VMC estimate of the expectation value \cite{ceperley_kalos_1979}.
+Wagner provides the details for calculating reduced density matrix elements in QMC \cite{doi:10.1063/1.4793531}.
 

### 2018-09-25 prelim/draft.tex
cleaned up draft, just need to add timeline?

@@
 }
-We choose to study the electron-doped cuprates because while they do not exhibit the exact same features as the hole-doped materials, they do have AFM,  superconducting, and pseudo-gap phases.
+We choose to study the electron-doped cuprates because while they do not exhibit the exact same features as the hole-doped materials, they do have AFM,  superconducting, pseudo-gap, and metallic phases.
 Further, the electron-doped materials have fewer relevant degrees of freedom, as electrons added to the x=0 CuO$_2$ plane can only fall into the unoccupied Cu 3d orbitals, allowing us to ignore the explicit inclusion of O p bands in our study.
@@
 \section{Preliminary results}
-In order to become acquainted with our code QWalk \cite{WAGNER20093390} and QMC algorithms in general I worked on implementing and testing multi-Slater-Jastrow trial functions with optimized non-orthogonal determinants (MSJ+NO) in FN-DMC \cite{Pathak2018}.
+\textbf{In order to become acquainted with our code QWalk \cite{WAGNER20093390} and QMC algorithms in general I worked on implementing and testing multi-Slater-Jastrow trial functions with optimized non-orthogonal determinants (MSJ+NO) in FN-DMC \cite{Pathak2018}.}
 We assessed the efficiency and compactness of this new trial function by calculating the ground state energy and single particle densities of a C$_2$ molecule using FN-DMC and comparing to the results when using multi-Slater-Jastrow trial functions with optimized orthogonal determinant trial functions (MSJ+O).
@@
 
-Before moving on to the computationally expensive DMD with FN-DMC calculations on SrCuO$_2$, we attempted an \textit{ad hoc} model fitting procedure using only eigenvalues and total energies from density functional theory (DFT) to get a grasp on the relevant energy scales, model terms, and values for model parameters.
+\textbf{Before moving on to the computationally expensive DMD with FN-DMC calculations on SrCuO$_2$, we attempted an \textit{ad hoc} model fitting procedure using only eigenvalues and total energies from density functional theory (DFT) to get a grasp on the relevant energy scales, model terms, and values for model parameters.
+}
 A single DFT calculation provides us three pieces of information: a Slater determinant wave function with occupied single particle orbitals $|\Psi_{DFT}\rangle$, a single particle band structure which represents the DFT eigenvalues $\epsilon(\vec{k})_{DFT}$, and a total DFT energy $E_{DFT}$.
@@
 where the sum over $i$ is over a sample of low-energy DFT states. 
-The first term is the cost function for a least squares fit of the single particle eigenvalues calculated using our model $\epsilon(\vec{k})_m$ and the DFT state $|\Psi_{DFT,i}\rangle$ to the DFT eigenvalues.
-The second term is a cost function for a least squares fit of the total energy calculated using our model to the DFT total energy. 
-The term $w_E$ controls the importance of minimizing the total energy cost relative to the eigenvalue cost, and is a variable parameter. 
+The first term is the mean squared error (MSE) evaluated on the single particle eigenvalues calculated using our model $\epsilon(\vec{k})_m$ with the DFT state $|\Psi_{DFT,i}\rangle$ and the DFT eigenvalues.
+The second term is the MSE between the total energy calculated using our model and the DFT total energy. 
+The term is a variable parameter and $w_E$ controls the importance of minimizing the total energy cost relative to the eigenvalue cost.
 The accuracy of the fit was assessed by looking at the $R^2$ value between the total energies, $R^2_E$, and between the eigenvalues, $R^2_\epsilon$. 
@@
 
-We conducted this \textit{ad hoc} fitting procedure for SrCuO$_2$ under three different dopings x=0, 0.125, and 0.25 using the PBE0 functional in DFT on a 2$\sqrt{2}$x2$\sqrt{2}$x1 unit cell. 
+\textbf{We conducted this \textit{ad hoc} fitting procedure for SrCuO$_2$ under three different dopings x=0, 0.125, and 0.25 using the PBE0 functional in DFT on a 2$\sqrt{2}$x2$\sqrt{2}$x1 unit cell.
+}
 The PBE0 functional has been used within QMC in the past to yield accurate results for low-energy properties and energies on the hole-doped cuprates \cite{Wagner2015,Narayan2017,Wagner2014}. 
-The eight unit cell calculation was chosen since it is small enough to be computationally feasible even when moving to QMC, but large enough that the finite size effects are not too large. 
-For the undoped calculations, the PBE0 ground state was a checkerboard AFM state, and the six low-energy states we considered were states with spins flipped relative to this ground state. 
+The eight unit cell calculation was chosen since it is small enough to be computationally feasible even when moving to QMC, but large enough to reduce finite size errors. 
+For the undoped calculations, the lowest energy PBE0 state was a checkerboard antiferromagnetic (AFM) state, and the six low-energy states we considered were states with spins flipped relative to the AFM state.
 This choice was made since the lowest energy excitations of the undoped cuprates are spin excitations as they are charge-transfer insulators. 
@@
 The bands below this gap never cross the Fermi level, and can be thought of as bands which contribute only to the fixed spin moments on copper sites. 
-Therefore we can treat the quantities $\vec{S_i}$ as fixed variables, the values of which are dictated by the bands below the gap for a given PBE0 calculation. 
+Therefore, we can treat the quantities $\vec{S_i}$ as fixed variables, the values of which are dictated by the bands below the gap for a given PBE0 calculation. 
 In doing so, the Kondo term becomes a 1-body term and the Heinsenberg term becomes a constant value, leaving the model Hamiltonian as a 1-body Hamiltonian which we can exactly diagonalize to get the total energy and eigenvalues.
 
-We find that the four term model above can accurately describe the PBE0 band structures and total energies of low-energy states of SrCuO$_2$ for x=0, 0.125, and 0.25. 
+\textbf{We find that the four term model above can accurately describe the PBE0 band structures and total energies of low-energy states of SrCuO$_2$ for x=0, 0.125, and 0.25 at T=0.}
 \ref{fig4} shows the results of our \textit{ad hoc} fitting procedure.
@@
 The other five insets show the fits to the bands and total energies from DFT using our model with the Pareto optimal parameters. 
-For the x=0.125 calculation the optimal parameters were with $t,t^\prime,K,J$=1.15, 0.39, -0.29, 0.18 eV $R^2_E$=0.98 and $R^2_\epsilon$=0.96. 
+For the x=0.125 calculation the optimal parameters were $t,t^\prime,K,J$=1.15, 0.39, -0.29, 0.18 eV with $R^2_E$=0.98 and $R^2_\epsilon$=0.96. 
 For the x=0.25 calculation the optimal parameters were $t,t^\prime,K,J$=1.04, 0.53, -0.15, 0.18 eV with $R^2_E$=0.91 and $R^2_\epsilon$=0.94. 
 In both our model and PBE0, the bands which cross the Fermi level are antibonding Cu 3d$_{x^2-y^2}$ orbitals which have been relaxed via small contributions from nearest neighbor oxygen p orbitals. 
-In PBE0 the net spin moments comprised of the bands below the Fermi level also reside on the Cu 3d$_{x^2-y^2}$ orbital, indicating that unlike the hole-doped cuprates where oxygen and copper orbitals both play an important role in the effective theories, the electron-doped cuprates may be simpler since the major players is just the Cu 3d$_{x^2-y^2}$ orbital.
-Therefore the fact that $t, t^\prime$ have the same sign makes sense as this is a feature arising from the symmetry of the 3d$_{x^2-y^2}$ orbital. 
+In PBE0 the net spin moments comprised of the bands below the Fermi level also reside on the Cu 3d$_{x^2-y^2}$ orbital, indicating that unlike the hole-doped cuprates where oxygen and copper orbitals both play an important role in the effective theories, the electron-doped cuprates may be simpler since the major players are just the Cu 3d$_{x^2-y^2}$ orbital.
+The fact that $t, t^\prime$ have the same sign makes sense as this is a feature arising from the symmetry of the 3d$_{x^2-y^2}$ orbital. 
 The positive sign of $J$ indicates a preference of nearest neighbor spin moments to be anti-ferromagnetically aligned, whereas the negative sign of $K$ shows a preference for itinerant electrons to ferromagnetically align with nearby spin moments.
-The opposite signs of J and K, and the fact that K is larger in magnitude than J when x=0.125 can lead to the stabilization of a flip state instead of a checkerboard one in PBE0.
+The opposite signs of J and K, and the fact that K is larger in magnitude than J when x=0.125, can lead to the stabilization of a flip state instead of a checkerboard one in PBE0.
 
-Our first step into DMD with FN-DMC was the generation of appropriate basis elements for our effective model Hamiltonian which we handled for all three dopings using intrinsic atomic orbitals. 
+\textbf{Our first step into DMD with FN-DMC was the generation of appropriate basis elements for our effective model Hamiltonian which we handled for all three dopings using intrinsic atomic orbitals.
+}
 The \textit{ad hoc} fitting procedure we conducted provided us with a starting point for generating low-energy states for the DMD calculation, the terms in our model Hamiltonian, and parameter values, but gave us no headway on understanding which basis elements to use.
-Using MOs in our model is not feasible because the interactions we are looking at are local and are nearest neighbor spatially. 
+Using molecular orbitals (MOs) in our model is not feasible because the interactions we are looking at are local and are nearest neighbor spatially. 
 If our interaction terms were more easily written in a momentum representation then MOs from PBE0 would be a useful basis to use. 
-We could start with atomic orbitals, AOs, which are the building blocks of the MOs in our PBE0 calculation, but AOs in general are not orthogonal to each other. 
+We could start with atomic orbitals (AOs) which are the building blocks of the MOs in our PBE0 calculation, but AOs in general are not orthogonal to each other. 
 This complicates our model representation because we typically work with models where creation and annihilation operators generate orthogonal states. 
-Therefore, what we are looking for are orbitals that are maximally localized and still orthogonal to one another, and this is precisely what the IAO is \cite{doi:10.1021/ct400687b}. 
+Therefore, what we are looking for are orbitals that are maximally localized and still orthogonal to one another, and this is precisely what the Intrinsic Atomic Orbital (IAO) is \cite{doi:10.1021/ct400687b}.
 In order to test whether the IAO basis is sufficient at spanning the space of excitations we are interested in, we looked at the 1-body reduced density matrix (1RDM) relative to the IAO basis for each x=0, 0.125 and 0.25 low-energy state chosen above.
 We found that the total number of electrons in the system is accounted for up to three decimal places using just the trace of the 1RDM over the minimal IAO basis. 
-Further, we found that the primary variation between low energy states at a fixed doping was in occupation of the IAOs was of the 3$d_{x^2-y^2}$ IAO. 
+Further, we found that the primary variation between low energy states at a fixed doping was in the occupation of the 3$d_{x^2-y^2}$ IAO. 
 For the undoped calculations the only variation in IAO occupation among the various states was the relative occupation of the spin-up or spin-down 3$d_{x^2-y^2}$ orbital on particular copper sites. 
@@
 This makes sense as the only place the added electron can go is in the 3$d_{x^2-y^2}$ orbital in the spin channel opposite to the local moment on the site. 
-\ref{fig5} shows the IAOs for the majority spin IAO, which has the higher occupation, and the minority spin IAO, which has the lower spin, for a low-energy state at x=0.125. 
+\ref{fig5} shows the IAOs for the majority and minority spin IAOs, for a low-energy PBE0 state at x=0.125. 
 It is clear that the majority spin IAO is more tightly localized on site whereas the minority spin IAO spreads across the unit cell with contributions from oxygen p-orbitals. 
@@
 \section{Proposed work}
-In order to generate an effective low-energy model using the DMD technique we need to generate low-energy wave functions within the full \textit{ab initio} Hilbert space. 
+\textbf{In order to generate an effective low-energy model using the DMD technique we need to generate low-energy wave functions within the full \textit{ab initio} Hilbert space.} 
 We will be using optimized multi-Slater-Jastrow (MSJ) as trial wave functions in FN-DMC to generate the low-energy states we are interested in. 
@@
 
-After the data generation phase above from which we have all the information required to do our fitting, relevant descriptors have to be chosen for our low-energy model. 
+\textbf{After the data generation phase above from which we have all the information required to do our fitting, relevant descriptors have to be chosen for our low-energy model. }
 The first tool in reducing the space of relevant descriptors is through symmetry considerations.
@@
 
-Since our initial set of calculations will be on an eight unit cell calculation cell with periodic boundary conditions, it is important to account for possible finite size errors in our FN-DMC calculations.
+\textbf{Since our initial set of calculations will be on an eight unit cell calculation cell with periodic boundary conditions, it is important to account for possible finite size errors in our FN-DMC calculations.
+}
 If these finite size errors (FSEs) are not accounted for in FN-DMC then the model we generated may suffer from the same finite size effects as the QMC calculations. 
@@
 
-Further, we will use the DMD procedure to attempt to describe the differences between the isostructural nickelate and cuprate materials. 
+\textbf{Further, we will use the DMD procedure to attempt to describe the differences between the isostructural nickelate and cuprate materials. }
 Shown in \ref{fig6} are the conventional unit cells of the cuprate La$_2$CuO$_4$ and the nickelate La$_2$NiO$_4$, which are identical except that the copper atom within the cell is replaced by a nickel atom.

### 2018-09-27 prelim/draft.tex
Prelim draft ready for Lucas!

@@
 \usepackage{amsfonts}
+\usepackage{titling}
+\title{Development of an effective model for SrCuO$_2$ using \textit{ab-initio} quantum Monte Carlo density-matrix downfolding}
+\author{Shivesh Pathak, Advisor: Lucas Wagner}
+\date{TBD}
 
 \begin{document}
+\maketitle
+\begin{abstract}
+\normalsize
+Understanding the low energy behavior of the cuprate superconductors has been an open question in theoretical condensed matter physics for over thirty years.
+Various model Hamiltonians have been proposed and tested to describe different phases under variation in doping and temperature, but the development and validation of these models have not been systematic.
+We propose that a density matrix downfolding approach \cite{10.3389/fphy.2018.00043, doi:10.1063/1.4927664} using \textit{ab-initio} quantum Monte Carlo can generate and validate an accurate low-energy model for the electron-doped cuprate SrCuO$_2$ at zero temperature and dopings of x=0, 0.125, 0.25 in a systematic way beginning directly from the \textit{ab-initio} Hamiltonian.
+By conducting a similar downfolding for the isostructural non-superconducting nickelate SrNiO$_2$, and comparing to the effective model for SrCuO$_2$, we hope to develop a better understanding of the mechanisms for superconductivity present in the cuprates.
+\end{abstract}
+\pagebreak
+
 \section{Introduction} 
@@
 \centering
-\includegraphics[width=0.9\textwidth]{Figures/R2-pareto.pdf}
+\includegraphics[width=0.7\textwidth]{Figures/R2-pareto.pdf}
 \caption{\label{fig4} Results of the \textit{ad hoc} fitting procedure just using the DFT eigenvalues and total energies for three different dopings.}
@@
 \centering
-\includegraphics[width=0.9\textwidth]{Figures/R3-iao_basis.pdf}
+\includegraphics[width=0.7\textwidth]{Figures/R3-iao_basis.pdf}
 \caption{\label{fig5} Relaxation of the IAOs for the spin majority and minority channel under doping for the eighth doped flip state.
@@
 
+\textbf{An approximate timeline for accomplishing each goal follows.} Generation of low-energy states and a complete descriptor space for the cuprate calculation will take the most time in the model fitting process as it requires multiple revisions and will require about two semesters.
+Studying finite size effects and implementing a similar downfolding to the nickelate material should take a sum total of one semester.
+Finite size corrections are time-gated only by computational hours (easier to come by than human hours) and the nickelate downfolding should be much easier given the work already done on the isostructural cuprate.
+Therefore we expect the proposed work to take another three semesters to complete.
+
 \begin{figure}[H]
 \centering
-\includegraphics[width=0.9\textwidth]{Figures/P2-Ni_Cu.pdf}
+\includegraphics[width=0.7\textwidth]{Figures/P2-Ni_Cu.pdf}
 \caption{\label{fig6} The primitive unit cells of the isostructural materials LNCO \cite{PhysRevB.92.205114} and LSCO \cite{Scalapino2012}, the prior which is not super conducting all the way to temperatures of 30mK.}

### 2019-04-04 doped_fv/PBE0/scf/analyze_line_mo.py
workgin on t-U model;

@@ -14,7 +14,7 @@ E=[-9.2092669022287E+02]*2+\
   [-9.2091264054414E+02]*2
 basestate=[0,0,1,1,2,2,3,3]
 df=None
-for name in ['FLP_up','FLP_dn','COL_up','COL_dn','COL2_up','COL2_dn','FM_up','FM_dn']:
+for name in ['FLP_up','FLP_dn']:#,'COL_up','COL_dn','COL2_up','COL2_dn']:#,'FM_up','FM_dn']:
   d=pd.read_pickle('pickles/'+name+'_line_gosling_g.pickle')
   d['energy']+=E[zz]
   d['energy']*=27.2114
@@ -22,25 +22,20 @@ for name in ['FLP_up','FLP_dn','COL_up','COL_dn','COL2_up','COL2_dn','FM_up','FM
   if(df is None): df=d
   else: df=pd.concat((df,d),axis=0)
   zz+=1
+df['tr']=0
+for i in range(5):
+  df['tr']+=df['sigN_'+str(i)+'_'+str(i)]
 
-'''
-plt.plot(np.arange(df.shape[0]),df['energy'],'o')
-plt.show()
+var=df.var()
+ind=np.argsort(var)
+print(var.iloc[ind])
 
-print(max(df['energy'])-min(df['energy']))
-exit(0)
-'''
-
-'''
-#PAIRPLOT: On small data set, Nd + Nps + N4s is constant,
-#there is a strong negative correlation with Nd + Nps and N4s,
-#implying that we would want to trace cut Nd + Nps, hence not
-#including states which have too much N4s occupation!
-#sns.pairplot(df,vars=['energy','sigT','sigNps','sigNd','sigU'],hue='rem')
-#sns.pairplot(df,vars=['energy','n'],hue='name',markers='.')
+#PAIRPLOT
+#sns.pairplot(df,vars=['energy','sigN_0_0','sigN_1_1','sigN_2_2','sigN_3_3','sigN_4_4'],hue='basestate')
 #plt.show()
 #exit(0)
 
+'''
 #APPLYING THE CUTOFFS:
 ind=np.where(df['energy']==min(df['energy']))[0][0]
 
@@ -76,12 +71,17 @@ y=select_df['energy']
 #plt.show()
 #exit(0)
 
[…]

### 2019-04-04 doped_fv/PBE0/scf/analyze_sd_mo.py

@@ -5,29 +5,38 @@ import pandas as pd
 import statsmodels.api as sm
 from statsmodels.sandbox.regression.predstd import wls_prediction_std
 from sklearn.decomposition import PCA
+from functools import reduce 
 
-df=pd.read_pickle('pickles/sd_gosling_mo.pickle')
+df=pd.read_pickle('pickles/sd_gosling_mo.pickle')#.iloc[[0,1,6,7,12,13,18,19,20]]
 var=df.var()
 ind=np.argsort(var.values)
-print(var.iloc[ind])
+#print(var.iloc[ind])
 #exit(0)
 #plt.matshow(df[['energy','sigN_0','sigN_1','sigN_2','sigN_3','sigN_4','sigN_5','sigN_6','sigN_7','sigU','sigJ']].corr(),vmax=1,vmin=-1,cmap=plt.cm.bwr)
 #plt.show()
 #exit(0)
 
+'''
 #REGRESSION
 select_df=df
 y=select_df['energy']
 #plt.plot(df['sigN_0_0'],df['energy'],'o')
-plt.plot(select_df['sigU'],select_df['energy'],'o')
-plt.show()
-exit(0)
+#plt.plot(select_df['sigU'],select_df['energy'],'o')
+#plt.show()
+#exit(0)
 
 #X=select_df[['sigN_1_1','sigN_2_2','sigN_3_3','sigN_4_4','sigN_5_5','sigN_6_6','sigN_7_7',
 #'sigN_0_1','sigN_0_2','sigN_1_2','sigN_1_4','sigN_5_6','sigN_5_7','sigN_6_7','sigU']]
 #X=select_df[['sigN_1_1','sigN_2_2','sigN_3_3','sigN_4_4','sigN_5_5','sigN_6_6','sigN_7_7','sigN_6_7','sigU']]
-X=select_df[['sigN_1_1','sigN_2_2','sigN_3_3','sigN_4_4','sigN_5_5','sigN_6_6','sigN_7_7','sigU']]
+#X=select_df[['sigN_1_1','sigN_2_2','sigN_3_3','sigN_4_4','sigN_5_5','sigN_6_6','sigN_7_7','sigU']]
 #X=select_df.drop(columns=['energy','basestate','sigJ'])  #Do t and U have to be divided by stuff because of the super cell?
[…]

### 2019-04-04 doped_fv/PBE0/scf/gather_col2_dn_line.py

@@ -38,7 +38,7 @@ def mo_rdm(mo_occ1,mo_occ2,w):
       dl[1,i1[1],i1[0]]+=w[0]*w[n]
   return dl
 
-def get_df_row(obdm,sigU,e):
+def get_df_row(obdm,sigU,sigUp,e):
   #1-body terms
   orb1=np.array([0,1,2,3,4,5,6,7,0,0,0,0,0,0,0,1,1,1,1,1,1,2,2,2,2,2,3,3,3,3,4,4,4,5,5,6])
   orb2=np.array([0,1,2,3,4,5,6,7,1,2,3,4,5,6,7,2,3,4,5,6,7,3,4,5,6,7,4,5,6,7,5,6,7,6,7,7])
@@ -46,8 +46,8 @@ def get_df_row(obdm,sigU,e):
   sigN_labels=['sigN_'+str(orb1[i])+'_'+str(orb2[i]) for i in range(len(orb1))]
   #print("Mo Tr: "+str(sum(sigN)))
 
-  data=np.array([e]+list(sigN)+[sigU])
-  d=pd.DataFrame(data[:,np.newaxis].T,columns=['energy']+sigN_labels+['sigU'],index=[0])
+  data=np.array([e]+list(sigN)+[sigU,sigUp])
+  d=pd.DataFrame(data[:,np.newaxis].T,columns=['energy']+sigN_labels+['sigU','sigUp'],index=[0])
   return d 
 
 #Generate sigU for a sum of two determinants 
@@ -58,15 +58,18 @@ def get_U(mo_occ1,mo_occ2,w,M0,M1):
   mo_dm=np.array([mo_dm1,mo_dm2])
   
   sigU=[]
+  sigUp=[]
   for dl in mo_dm:
     R=np.einsum('ij,jk->ik',dl[0],M0.T)
     dm_u=np.einsum('ij,jk->ik',M0,R)
     R=np.einsum('ij,jk->ik',dl[1],M1.T)
     dm_d=np.einsum('ij,jk->ik',M1,R)
     sigU.append(np.sum(dm_u[[13,23,33,43],[13,23,33,43]]*dm_d[[13,23,33,43],[13,23,33,43]]))
+    sigUp.append(np.sum(dm_u[[45,49,53,57,62,66,70,74],[45,49,53,57,62,66,70,74]]*dm_d[[45,49,53,57,62,66,70,74],[45,49,53,57,62,66,70,74]]))
 
[…]

### 2019-04-04 doped_fv/PBE0/scf/gather_col2_up_line.py

@@ -38,7 +38,7 @@ def mo_rdm(mo_occ1,mo_occ2,w):
       dl[1,i1[1],i1[0]]+=w[0]*w[n]
   return dl
 
-def get_df_row(obdm,sigU,e):
+def get_df_row(obdm,sigU,sigUp,e):
   #1-body terms
   orb1=np.array([0,1,2,3,4,5,6,7,0,0,0,0,0,0,0,1,1,1,1,1,1,2,2,2,2,2,3,3,3,3,4,4,4,5,5,6])
   orb2=np.array([0,1,2,3,4,5,6,7,1,2,3,4,5,6,7,2,3,4,5,6,7,3,4,5,6,7,4,5,6,7,5,6,7,6,7,7])
@@ -46,8 +46,8 @@ def get_df_row(obdm,sigU,e):
   sigN_labels=['sigN_'+str(orb1[i])+'_'+str(orb2[i]) for i in range(len(orb1))]
   #print("Mo Tr: "+str(sum(sigN)))
 
-  data=np.array([e]+list(sigN)+[sigU])
-  d=pd.DataFrame(data[:,np.newaxis].T,columns=['energy']+sigN_labels+['sigU'],index=[0])
+  data=np.array([e]+list(sigN)+[sigU,sigUp])
+  d=pd.DataFrame(data[:,np.newaxis].T,columns=['energy']+sigN_labels+['sigU','sigUp'],index=[0])
   return d 
 
 #Generate sigU for a sum of two determinants 
@@ -58,15 +58,18 @@ def get_U(mo_occ1,mo_occ2,w,M0,M1):
   mo_dm=np.array([mo_dm1,mo_dm2])
   
   sigU=[]
+  sigUp=[]
   for dl in mo_dm:
     R=np.einsum('ij,jk->ik',dl[0],M0.T)
     dm_u=np.einsum('ij,jk->ik',M0,R)
     R=np.einsum('ij,jk->ik',dl[1],M1.T)
     dm_d=np.einsum('ij,jk->ik',M1,R)
     sigU.append(np.sum(dm_u[[13,23,33,43],[13,23,33,43]]*dm_d[[13,23,33,43],[13,23,33,43]]))
+    sigUp.append(np.sum(dm_u[[45,49,53,57,62,66,70,74],[45,49,53,57,62,66,70,74]]*dm_d[[45,49,53,57,62,66,70,74],[45,49,53,57,62,66,70,74]]))
 
[…]

### 2019-04-04 doped_fv/PBE0/scf/gather_col_dn_line.py

@@ -38,7 +38,7 @@ def mo_rdm(mo_occ1,mo_occ2,w):
       dl[1,i1[1],i1[0]]+=w[0]*w[n]
   return dl
 
-def get_df_row(obdm,sigU,e):
+def get_df_row(obdm,sigU,sigUp,e):
   #1-body terms
   orb1=np.array([0,1,2,3,4,5,6,7,0,0,0,0,0,0,0,1,1,1,1,1,1,2,2,2,2,2,3,3,3,3,4,4,4,5,5,6])
   orb2=np.array([0,1,2,3,4,5,6,7,1,2,3,4,5,6,7,2,3,4,5,6,7,3,4,5,6,7,4,5,6,7,5,6,7,6,7,7])
@@ -46,8 +46,8 @@ def get_df_row(obdm,sigU,e):
   sigN_labels=['sigN_'+str(orb1[i])+'_'+str(orb2[i]) for i in range(len(orb1))]
   #print("Mo Tr: "+str(sum(sigN)))
 
-  data=np.array([e]+list(sigN)+[sigU])
-  d=pd.DataFrame(data[:,np.newaxis].T,columns=['energy']+sigN_labels+['sigU'],index=[0])
+  data=np.array([e]+list(sigN)+[sigU,sigUp])
+  d=pd.DataFrame(data[:,np.newaxis].T,columns=['energy']+sigN_labels+['sigU','sigUp'],index=[0])
   return d 
 
 #Generate sigU for a sum of two determinants 
@@ -58,15 +58,18 @@ def get_U(mo_occ1,mo_occ2,w,M0,M1):
   mo_dm=np.array([mo_dm1,mo_dm2])
   
   sigU=[]
+  sigUp=[]
   for dl in mo_dm:
     R=np.einsum('ij,jk->ik',dl[0],M0.T)
     dm_u=np.einsum('ij,jk->ik',M0,R)
     R=np.einsum('ij,jk->ik',dl[1],M1.T)
     dm_d=np.einsum('ij,jk->ik',M1,R)
     sigU.append(np.sum(dm_u[[13,23,33,43],[13,23,33,43]]*dm_d[[13,23,33,43],[13,23,33,43]]))
+    sigUp.append(np.sum(dm_u[[45,49,53,57,62,66,70,74],[45,49,53,57,62,66,70,74]]*dm_d[[45,49,53,57,62,66,70,74],[45,49,53,57,62,66,70,74]]))
 
[…]

### 2019-04-04 doped_fv/PBE0/scf/gather_col_up_line.py

@@ -38,7 +38,7 @@ def mo_rdm(mo_occ1,mo_occ2,w):
       dl[1,i1[1],i1[0]]+=w[0]*w[n]
   return dl
 
-def get_df_row(obdm,sigU,e):
+def get_df_row(obdm,sigU,sigUp,e):
   #1-body terms
   orb1=np.array([0,1,2,3,4,5,6,7,0,0,0,0,0,0,0,1,1,1,1,1,1,2,2,2,2,2,3,3,3,3,4,4,4,5,5,6])
   orb2=np.array([0,1,2,3,4,5,6,7,1,2,3,4,5,6,7,2,3,4,5,6,7,3,4,5,6,7,4,5,6,7,5,6,7,6,7,7])
@@ -46,8 +46,8 @@ def get_df_row(obdm,sigU,e):
   sigN_labels=['sigN_'+str(orb1[i])+'_'+str(orb2[i]) for i in range(len(orb1))]
   #print("Mo Tr: "+str(sum(sigN)))
 
-  data=np.array([e]+list(sigN)+[sigU])
-  d=pd.DataFrame(data[:,np.newaxis].T,columns=['energy']+sigN_labels+['sigU'],index=[0])
+  data=np.array([e]+list(sigN)+[sigU,sigUp])
+  d=pd.DataFrame(data[:,np.newaxis].T,columns=['energy']+sigN_labels+['sigU','sigUp'],index=[0])
   return d 
 
 #Generate sigU for a sum of two determinants 
@@ -58,15 +58,18 @@ def get_U(mo_occ1,mo_occ2,w,M0,M1):
   mo_dm=np.array([mo_dm1,mo_dm2])
   
   sigU=[]
+  sigUp=[]
   for dl in mo_dm:
     R=np.einsum('ij,jk->ik',dl[0],M0.T)
     dm_u=np.einsum('ij,jk->ik',M0,R)
     R=np.einsum('ij,jk->ik',dl[1],M1.T)
     dm_d=np.einsum('ij,jk->ik',M1,R)
     sigU.append(np.sum(dm_u[[13,23,33,43],[13,23,33,43]]*dm_d[[13,23,33,43],[13,23,33,43]]))
+    sigUp.append(np.sum(dm_u[[45,49,53,57,62,66,70,74],[45,49,53,57,62,66,70,74]]*dm_d[[45,49,53,57,62,66,70,74],[45,49,53,57,62,66,70,74]]))
 
[…]

### 2019-04-04 doped_fv/PBE0/scf/gather_flp_up_line.py

@@ -36,9 +36,17 @@ def mo_rdm(mo_occ1,mo_occ2,w):
     if(i1.shape[0]>0):
       dl[1,i1[0],i1[1]]+=w[0]*w[n]
       dl[1,i1[1],i1[0]]+=w[0]*w[n]
+
+  #2rdms
+  dl2=np.zeros((mo_dm.shape[1],mo_dm.shape[1],mo_dm.shape[1],mo_dm.shape[1]))
+  Ndet=mo_dm.shape[0]
+  for n in range(Ndet):
+    diag=np.arange(dl2.shape[0])
+    dl2[diag,diag,diag,diag]=
+
   return dl
 
-def get_df_row(obdm,sigU,e):
+def get_df_row(obdm,sigU,sigUp,e):
   #1-body terms
   orb1=np.array([0,1,2,3,4,5,6,7,0,0,0,0,0,0,0,1,1,1,1,1,1,2,2,2,2,2,3,3,3,3,4,4,4,5,5,6])
   orb2=np.array([0,1,2,3,4,5,6,7,1,2,3,4,5,6,7,2,3,4,5,6,7,3,4,5,6,7,4,5,6,7,5,6,7,6,7,7])
@@ -46,8 +54,8 @@ def get_df_row(obdm,sigU,e):
   sigN_labels=['sigN_'+str(orb1[i])+'_'+str(orb2[i]) for i in range(len(orb1))]
   #print("Mo Tr: "+str(sum(sigN)))
 
-  data=np.array([e]+list(sigN)+[sigU])
-  d=pd.DataFrame(data[:,np.newaxis].T,columns=['energy']+sigN_labels+['sigU'],index=[0])
+  data=np.array([e]+list(sigN)+[sigU,sigUp])
+  d=pd.DataFrame(data[:,np.newaxis].T,columns=['energy']+sigN_labels+['sigU','sigUp'],index=[0])
   return d 
 
 #Generate sigU for a sum of two determinants 
@@ -58,15 +66,18 @@ def get_U(mo_occ1,mo_occ2,w,M0,M1):
   mo_dm=np.array([mo_dm1,mo_dm2])
   
   sigU=[]
+  sigUp=[]
   for dl in mo_dm:
     R=np.einsum('ij,jk->ik',dl[0],M0.T)
     dm_u=np.einsum('ij,jk->ik',M0,R)
     R=np.einsum('ij,jk->ik',dl[1],M1.T)
     dm_d=np.einsum('ij,jk->ik',M1,R)
[…]

### 2019-04-04 doped_fv/PBE0/scf/gather_fm_dn_line.py

@@ -122,9 +122,10 @@ def gather_line(rem,add,gsws):
 
 if __name__=='__main__':
   #Smallest sample set, sigma only, no pi or dz2,4s
-  rem_list=[64]*7
-  add_list=[65,66,67,68,69,70,71]
+  rem_list=[64]*4
+  add_list=[65,66,67,68]#,69,70,71]
   gsws=np.arange(-1.00,1.10,0.1)
+  #gsws=[-1.00,-0.95,-0.90,0.90,0.95,1.00]
   print(gsws)
 
   full_df=None

### 2019-04-04 doped_fv/PBE0/scf/gather_fm_up_line.py

@@ -122,9 +122,10 @@ def gather_line(rem,add,gsws):
 
 if __name__=='__main__':
   #Smallest sample set, sigma only, no pi or dz2,4s
-  rem_list=[67]*4
-  add_list=[68,69,70,71]
+  rem_list=[67]*1
+  add_list=[68]#,69,70,71]
   gsws=np.arange(-1.00,1.10,0.1)
+  #gsws=[-1.00,-0.95,-0.90,0.90,0.95,1.00]
   print(gsws)
 
   full_df=None

### 2019-04-04 doped_fv/PBE0/scf/gather_sd.py

@@ -10,7 +10,8 @@ from functools import reduce
 from downfold_tools import gen_slater_tbdm,sum_onebody,sum_J,sum_U
 import seaborn as sns 
 
-a=np.load('pickles/iao_g.pickle')
+#a=np.load('pickles/iao_g.pickle')
+a=np.load('pickles/UNPOL_mo_coeff_g.pickle')[:,:72]
 
 df=None
 direcs=['FLP']*12+['COL']*12+['COL2']*12+['FM']*12
@@ -128,8 +129,14 @@ for run in range(len(direcs)):
       mo_rdm[add[run][spin]]=1
       e+=(mo_energy[spin][add[run][spin]]-mo_energy[spin][rem[run][spin]])*27.2114
     obdm[spin]=reduce(np.dot,(mo_to_iao,np.diag(mo_rdm),mo_to_iao.T))
-  tbdm,__=gen_slater_tbdm(obdm)
+  #tbdm,__=gen_slater_tbdm(obdm)
+  
+  orb1=np.arange(72)
+  sigN=sum_onebody(obdm,orb1,orb1)
+  sigNlabels=['sigN_'+str(i) for i in range(len(orb1))]
+  d=pd.DataFrame(
 
+  '''
   #Hopping
   orb1=np.array([14,14,14,14,24,24,24,24,34,34,34,34,44,44,44,44])-1
   orb2=np.array([46,63,54,67,50,67,58,63,54,71,46,75,58,75,50,71])-1
@@ -180,6 +187,8 @@ for run in range(len(direcs)):
   d=pd.DataFrame({'energy':e,'sigTd':sigTd,'sigT':sigT,'sigNdz':sigNdz,'sigNdpi':sigNdpi,'sigNpz':sigNpz,'sigNdz2':sigNdz2,
   'sigN4s':sigN4s,'sigN2s':sigN2s,'sigNps':sigNps,'sigNpp':sigNpp,'sigNd':sigNd,'sigU':sigU,'sigJ':sigJ,
   'basestate':direcs[run]},index=[0])
+  '''
+
   if(df is None): df=d
   else: df=pd.concat((df,d),axis=0)
 

### 2019-04-04 doped_fv/PBE0/scf/gather_sd_mo.py

@@ -11,7 +11,7 @@ from downfold_tools import gen_slater_tbdm,sum_onebody,sum_J,sum_U
 import seaborn as sns 
 
 a=np.load('pickles/UNPOL_mo_coeff_g.pickle')[0]
-a=a[:,[55,65,66,67,68,69,70,71]]
+a=a[:,:72]
 b=np.load('pickles/iao_g.pickle')
 
 df=None
@@ -143,11 +143,20 @@ for run in range(len(direcs)):
   tbdm,__=gen_slater_tbdm(obdm2)
 
   #1-body terms
-  orb1=np.array([0,1,2,3,4,5,6,7,0,0,0,0,0,0,0,1,1,1,1,1,1,2,2,2,2,2,3,3,3,3,4,4,4,5,5,6])
-  orb2=np.array([0,1,2,3,4,5,6,7,1,2,3,4,5,6,7,2,3,4,5,6,7,3,4,5,6,7,4,5,6,7,5,6,7,6,7,7])
+  #orb1=np.array([0,1,2,3,4,5,6,7,0,0,0,0,0,0,0,1,1,1,1,1,1,2,2,2,2,2,3,3,3,3,4,4,4,5,5,6])
+  #orb2=np.array([0,1,2,3,4,5,6,7,1,2,3,4,5,6,7,2,3,4,5,6,7,3,4,5,6,7,4,5,6,7,5,6,7,6,7,7])
+  orb1=np.arange(72)
+  orb2=orb1
   sigN=sum_onebody(obdm,orb1,orb2)
   sigN_labels=['sigN_'+str(orb1[i])+'_'+str(orb2[i]) for i in range(len(orb1))]
   #print("Mo Tr: "+str(sum(sigN)))
+
+  obdm=obdm[:,[55,65,66,67,68,69,70,71],:]
+  obdm=obdm[:,:,[55,65,66,67,68,69,70,71]]
+  orb1=np.array([0,0,0,0,0,0,0,1,1,1,1,1,1,2,2,2,2,2,3,3,3,3,4,4,4,5,5,6])
+  orb2=np.array([1,2,3,4,5,6,7,2,3,4,5,6,7,3,4,5,6,7,4,5,6,7,5,6,7,6,7,7])
+  sigT=sum_onebody(obdm,orb1,orb2)
+  sigT_labels=['sigT_'+str(orb1[i])+'_'+str(orb2[i]) for i in range(len(orb1))]
 
   #2-body terms
   orb=np.array([14,24,34,44])-1
[…]

### 2019-04-04 doped_fv/PBE0/scf/project_unpol.py

@@ -3,53 +3,53 @@ import pandas as pd
 from functools import reduce 
 import matplotlib.pyplot as plt
 
+
+#Project active pol onto unpolarized
+zz=0
+base_coeff=pd.read_pickle('pickles/FLP_mo_coeff_g.pickle')
+s=pd.read_pickle('pickles/FLP_s_g.pickle')
+comp = ['FLP','COL','COL2','FM']
+for spin in [0,1]:
+  zz=0
+  for comp_f in comp:
+    zz+=1
+    comp_coeff=pd.read_pickle('pickles/'+comp_f+'_mo_coeff_g.pickle')
+    M=np.einsum('ij,sjk->sik',s,base_coeff)
+    comp_matrix=np.einsum('sji,sjk->sik',comp_coeff,M) #[s, pol, FLP]
+
+    if(spin==0):
+      act=np.arange(67,73)-1
+      if(comp_f=='FM'): act=np.arange(68,73)-1
+    else:
+      act=np.arange(66,73)-1
+      if(comp_f=='FM'): act=np.arange(65,73)-1
+    plt.subplot(410+zz)
+    plt.matshow(comp_matrix[spin,act,:72],vmax=1,vmin=-1,cmap=plt.cm.bwr,fignum=False)
+    plt.ylabel(comp_f)
+    plt.xlabel('FLP')
+  plt.suptitle('Active bands S='+str(spin))
+  plt.show()
+  #plt.savefig('plots/act_unpol_s'+str(spin)+'.pdf',bbox_inches='tight')
+
+'''
+#Project active unpol to polarized
 zz=0
 base_coeff=pd.read_pickle('pickles/UNPOL_mo_coeff_g.pickle')
 s=pd.read_pickle('pickles/UNPOL_s_g.pickle')
 comp = ['FLP','COL','COL2','FM']
-for comp_f in comp:
-  comp_coeff=pd.read_pickle('pickles/'+comp_f+'_mo_coeff_g.pickle')
-  M=np.einsum('ij,sjk->sik',s,base_coeff)
-  comp_matrix=np.einsum('sji,sjk->sik',comp_coeff,M) #[s, pol, unpol]
- 
-  '''
-  #No block plots
-  plt.matshow(comp_matrix[0,:72,:72],vmax=2,vmin=-2,cmap=plt.cm.bwr)
-  plt.xlabel('Polarized')
[…]

### 2019-04-06 doped_fv/PBE0/scf/notes/notes.tex
finished up notes part 1, have some ideas on what to do next

\documentclass{article}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{float}
\usepackage{amsmath}

\begin{document}
\section{Well understood concepts}
\subsection{SCF spin states and band structures}
For the 4 unit cell doped calculation there are 4 unique spin states that we end up with in SCF. These states are what I call FLP, COL, COL2 and FM, with energies respectively 0 eV, 0.16 eV, 0.19 eV, and 0.38 eV. The spin densities for these states are shown in Figure \ref{fig:SpinDens}. The directories which contain the calculation outputs, plotting files, etc are suffixed with \texttt{\_ns} to indicate that it's a symmetry broken calculation.

\begin{figure}[H]
\centering
\includegraphics[width=\linewidth]{ALL_spin.pdf}
\caption{Spin densities of the different SCF ground states used in this calculation.}
\label{fig:SpinDens}
\end{figure}

We also calculated the band structure for these different states. The band structures can be seen in Figure \ref{fig:Bands}. All of the band structures have similar features. The bands are broken into three clusters: 1) A set of bands which have relatively small bandwidth, and start around -2.5 eV below the Fermi level, 2) A set of bands above 7.5 eV which are nearly spin degenerate and look almost identical regardless of spin state, 3) A set of bands in a window -2.5 to 5 eV around the Fermi level. I will name the bands as follows, 1) "Core" bands as they look like nearly localized core states, 2) "Strontium" bands since they have large Sr occupation, and 3) "Active" bands as these are the bands which cross the Fermi level. The active bands for the FLP, COL, and COL2 states are therefore bands 67 - 72 in the up channel and 66 - 72 in the down channel. For the FM state the active bands are 68 - 72 and 65 - 72 in the up and down channels respectively.

\begin{figure}[H]
\centering
\includegraphics[width=\linewidth]{ALL_bands.pdf}
\caption{Band structures of the different SCF ground states used in this calculation.}
\label{fig:Bands}
\end{figure}

\subsection{Goal 1: Internal consistency}
Before moving onto matching experimental evidence, we would like to have a model which is at least internally consistent. Namely, we want a model which can describe a chosen active space accurately. From the results above it is clear that our \textbf{active space should be the four different SCF spin states and excitations upon those SCF states within the respective active bands.}

\subsection{Structure of the active space}
Before generating any type of model, it is necessary to understand what varies within our chosen active space. I looked at the 1-rdm elements of the different single determinant states in our active space evaluated on an IAO basis constructed on the active space. Only singles excitations were chosen in our sample set, but this will not affect the results since we are only looking at occupation descriptor for this section. From here, we see that the major variations in number occupations within the active space are $n_{d_{x^2-y^2}}, n_{p_\sigma}, n_{4s}$. The variations in these parameters are O(0.1). The next smallest variation in occupations are O(0.001), nearly 100 times smaller, and correspond to $n_{d_{z^2}}$. \textbf{This indicates our active space is going to be primarily spanned by the orbitals $\text{Cu}{d_{x^2-y^2}}, \text{O}{p_\sigma}, \text{and Cu}{4s}$}. These variances can were calculated using the \texttt{analyze\_sd.py} script, and the data was gathered using \texttt{gather\_sd.py}. IAOs were calculated using the script \texttt{build\_pickles.py}. These text files are all present in the directory \texttt{scf/}.

\section{In progress}
\subsection{Possible models: Hubbard model}
The Hubbard model is pretty versatile and can capture a lot of behavior, including spin-charge coupling. The simplest Hubbard-like model which could accurately describe our active space would require the following terms:

$$\epsilon_{d},\epsilon_{p}, \epsilon_{s}, t_{ds}, t_{dp}, t_{ps}, U_d, U_p, U_s$$

Here d, p, and s correspond to $d_{x^2-y2}, p_\sigma, 4s$ respectively. Since we know that the total number of electrons in fixed, and that variation outside of the d, p, s space is small, we can drop one of the occupation energies. It's beneficial to drop $\epsilon_d$ since this correlates strongly with $U_d$. Further, $t_{ds}$ cannot occur on-site due to symmetry, and we will be ignoring non-nearest neighbor hopping for now. Therefore our minimal, NN Hubbard-like model for this system should take this form:

\begin{equation}
\boxed{\text{NN-Hubbard model: }\epsilon_{p}, \epsilon_{s}, t_{dp}, t_{ps}, U_d, U_p, U_s}
\end{equation}

A pairplot showing the (co)-variations of these parameters evaluated using our IAO basis, as calculated in SCF, is shown in Figure \ref{fig:HubbardPPIAO}. Only singles excitations on the different spin states are included, and therefore \textbf{does not include the full active space}. Apart from the strong correlations between $n \propto U$, which are because we are not sampling doubles/triples/etc, there is a pretty strong correlation between $n_p, t_{dp}$ parameters. Additionally, the descriptor related to $U_s$ does not change much within this data set, indicating that this parameter may not be relevant. However, we have not yet studied the full active space so it is hard to say which parameters are irrelevant and whether the correlations shown here are present in the full active space data set or not. Plots generated using \texttt{analyze\_sd.py}.

\pagebreak
\paragraph{Next steps}

\begin{enumerate}
\item \textbf{Include the full active space into our sample set, i.e. include doubles, triples, etc.} This may resolve the correlation between parameters, but also increases the energy scale for regression enormously. Maybe a weighted linear regression can deal with this.
\item \textbf{If including higher order excitations cannot remove the correlations in the data (correlations are inherent to low-energy space), consider a different basis for the 1-body parameters}. For example the unpolarized active orbitals, which we know span the active space.
\item \textbf{If we can figure out the above and the regression still does not look good enough, we can extend the Hubbard model}. This can be done by including longer-range hopping or density-density interactions between different orbitals, $V$. 
\end{enumerate}

\begin{figure}[H]
\centering
\includegraphics[width=\linewidth]{HubbardPPIAO.pdf}
\caption{Pairplot of parameters in equation (1) using singles excitations in the active space defined in section 1.2.}
\label{fig:HubbardPPIAO}
\end{figure}

\subsection{Possible models: Spin-fermion model}
A spin-fermion model may be a nice alternative to the Hubbard model, since it explicitly encodes the spin-charge coupling in the system. However, fitting a spin-fermion model would require sample states which are separable, namely states $|\Psi\rangle = |\Psi_s\rangle |\Psi_f\rangle$, where the spaces for the different parts of the wave functions are independent. The SCF spin states that we have do not have a simple separation into two different spaces, one for the localized spins and one for the conduction fermions. This is because in the cuprates the $d_{x^2-y^2}$ orbitals host both the localized spins and conduction electrons. Therefore, a band which is in the active space for COL may have contributions from some core and some active bands of the FLP state. This concept is shown in Figure \ref{fig:Proj_FLP}. Here we show the projection of the active orbitals at the gamma point for the different SCF spin states onto the full set of core and active orbitals of the FLP calculation. Bright red corresponds to +1, and bright blue to -1, whereas white is a value of zero. For a given non-FLP state active orbital there are clearly contributions from core FLP orbitals, indicating that these SCF states are not separable into spin- and fermion- spaces in the MO basis.

\begin{figure}[H]
\centering
\includegraphics[width=\linewidth]{Proj_FLP.pdf}
\caption{Projection of active gamma-point MOs for different spin states onto the FLP core + active orbitals.}
\label{fig:Proj_FLP}
\end{figure}
\pagebreak
\paragraph{Next steps}
\begin{enumerate}
\item \textbf{Consider how to generate low-energy states which are separable into spin- and fermion- spaces}. Just because our current SCF states don't have this property does not remove the possibility that low-energy states which are separable exist.
\end{enumerate}
\end{document}

### 2019-04-06 doped_fv/PBE0/scf/analyze_sd.py

@@ -8,12 +8,10 @@ from sklearn.decomposition import PCA
 
 df=pd.read_pickle('pickles/sd_gosling.pickle')
 print(df)
-exit(0)
-#df=df.iloc[[0,12,24,36]]
 var=df.var()
 ind=np.argsort(var.values)
 print(var.iloc[ind])
-
+'''
 def plot_parm(parm):
   for i in range(12):
     plt.plot(df.iloc[[0,i]][parm],df.iloc[[0,i]]['energy'],'bo-')
@@ -27,6 +25,7 @@ def plot_parm(parm):
   return 
 plot_parm('sigNps')
 exit(0)
+'''
 
 #PAIRPLOTS
 #sns.pairplot(df,vars=['energy','sigNdpi','sigNdz','sigNpp','sigNpz'],hue='basestate')
@@ -34,8 +33,10 @@ exit(0)
 #sns.pairplot(df,vars=['energy','sigNps','sigNd','sigN4s'],hue='basestate')
 #sns.pairplot(df,vars=['energy','sigTd','sigT','sigU','sigJ'],hue='basestate')
 #sns.pairplot(df,vars=['energy','sigT','sigTd','sigJ','sigNps'],hue='basestate')
-sns.pairplot(df,vars=['energy','sigN4s','sigU','sigNd'],hue='basestate')
-plt.show()
+#sns.pairplot(df,vars=['energy','sigN4s','sigU','sigNd'],hue='basestate')
+sns.pairplot(df,vars=['sigNps','sigN4s','sigTdp','sigTps','sigUd','sigUp','sigUs'],hue='basestate')
+plt.savefig('HubbardPPIAO.pdf',bbox_inches='tight')
+#plt.show()
 exit(0)
 
 '''

### 2019-04-06 doped_fv/PBE0/scf/analyze_sd_mo.py

@@ -6,40 +6,87 @@ import statsmodels.api as sm
 from statsmodels.sandbox.regression.predstd import wls_prediction_std
 from sklearn.decomposition import PCA
 from functools import reduce 
+from sklearn.linear_model import OrthogonalMatchingPursuit
 
-df=pd.read_pickle('pickles/sd_gosling_mo.pickle')#.iloc[[0,1,6,7,12,13,18,19,20]]
-var=df.var()
-ind=np.argsort(var.values)
-#print(var.iloc[ind])
-#exit(0)
-#plt.matshow(df[['energy','sigN_0','sigN_1','sigN_2','sigN_3','sigN_4','sigN_5','sigN_6','sigN_7','sigU','sigJ']].corr(),vmax=1,vmin=-1,cmap=plt.cm.bwr)
-#plt.show()
-#exit(0)
+#########################################################################################
+#REDUCING
+df=pd.read_pickle('pickles/sd_gosling_mo.pickle')
+#df=df.iloc[[0,1,2,6,7,8,12,13,14,18,16,20,24,25,26,30,31,32,36,37,41,42,43,44]] #No 70,71,72
+#df=df.iloc[[0,12,24,36]] #Spin states only
+
+df['sigN_65_65']+=df['sigN_66_66']
+df['sigN_69_69']+=df['sigN_70_70']
+df=df.drop(columns=['sigN_66_66','sigN_70_70'])
+
+df['sigT_0_1']+=df['sigT_0_2']
+df['sigT_0_5']+=df['sigT_0_6']
+df['sigT_1_3']+=df['sigT_2_3']
+df['sigT_1_4']+=df['sigT_2_4']
+df['sigT_1_5']+=df['sigT_1_6']+df['sigT_2_5']+df['sigT_2_6']
+df['sigT_1_7']+=df['sigT_2_7']
+df['sigT_3_5']+=df['sigT_3_6']
+df['sigT_4_5']+=df['sigT_4_6']
+df['sigT_5_7']+=df['sigT_6_7']
+df=df.drop(columns=['sigT_1_2','sigT_5_6','sigT_0_2','sigT_0_6','sigT_2_3',
+'sigT_2_4','sigT_1_6','sigT_2_5','sigT_2_6','sigT_2_7','sigT_3_6','sigT_4_6','sigT_6_7'])
 
 '''
-#REGRESSION
-select_df=df
-y=select_df['energy']
-#plt.plot(df['sigN_0_0'],df['energy'],'o')
[…]

### 2019-04-06 doped_fv/PBE0/scf/gather_sd.py

@@ -10,8 +10,7 @@ from functools import reduce
 from downfold_tools import gen_slater_tbdm,sum_onebody,sum_J,sum_U
 import seaborn as sns 
 
-#a=np.load('pickles/iao_g.pickle')
-a=np.load('pickles/UNPOL_mo_coeff_g.pickle')[:,:72]
+a=np.load('pickles/iao_g.pickle')
 
 df=None
 direcs=['FLP']*12+['COL']*12+['COL2']*12+['FM']*12
@@ -129,20 +128,20 @@ for run in range(len(direcs)):
       mo_rdm[add[run][spin]]=1
       e+=(mo_energy[spin][add[run][spin]]-mo_energy[spin][rem[run][spin]])*27.2114
     obdm[spin]=reduce(np.dot,(mo_to_iao,np.diag(mo_rdm),mo_to_iao.T))
-  #tbdm,__=gen_slater_tbdm(obdm)
-  
-  orb1=np.arange(72)
-  sigN=sum_onebody(obdm,orb1,orb1)
-  sigNlabels=['sigN_'+str(i) for i in range(len(orb1))]
-  d=pd.DataFrame(
+  tbdm,__=gen_slater_tbdm(obdm)
 
-  '''
   #Hopping
   orb1=np.array([14,14,14,14,24,24,24,24,34,34,34,34,44,44,44,44])-1
   orb2=np.array([46,63,54,67,50,67,58,63,54,71,46,75,58,75,50,71])-1
   sign=np.array([-1,1,1,-1]*4)
-  sigT=sum_onebody(obdm,orb1,orb2)
-  sigT=2*np.dot(sign,sigT)
+  sigTdp=sum_onebody(obdm,orb1,orb2)
+  sigTdp=2*np.dot(sign,sigTdp)
+
+  orb1=np.array([ 6, 6, 6, 6,16,16,16,16,26,26,26,26,36,36,36,36])-1
+  orb2=np.array([46,63,54,67,50,67,58,63,54,71,46,75,58,75,50,71])-1
+  sign=np.array([-1,-1,1,1]*4)
+  sigTps=sum_onebody(obdm,orb1,orb2)
+  sigTps=2*np.dot(sign,sigTps)
 
   orb1=np.array([14,14,24,24,34,34,44,44])-1
   orb2=np.array([24,34,14,44,14,44,24,34])-1
[…]

### 2019-04-09 doped_fv/PBE0/scf/analyze_sd.py
gathered using gather_sd.py the full number occupation on MOs and IAOs

@@ -6,69 +6,39 @@ import statsmodels.api as sm
 from statsmodels.sandbox.regression.predstd import wls_prediction_std
 from sklearn.decomposition import PCA
 
-df=pd.read_pickle('pickles/sd_gosling.pickle')
-print(df)
+df=pd.read_pickle('pickles/full_sd_gosling.pickle')
+df['tr']=df['Nd']+df['Ns']+df['Np']
+df['tr_group']=0
+df['tr_group'][df['tr']<=20.7]=-1
+df['tr_group'][df['tr']>=21]=1
+
+for g in [-1,0,1]:
+  ind=np.where(df['tr_group'].values==g)[0]
+  print(ind)
+exit(0)
+
 var=df.var()
 ind=np.argsort(var.values)
 print(var.iloc[ind])
-'''
-def plot_parm(parm):
-  for i in range(12):
-    plt.plot(df.iloc[[0,i]][parm],df.iloc[[0,i]]['energy'],'bo-')
-  for i in range(12,24):
-    plt.plot(df.iloc[[12,i]][parm],df.iloc[[12,i]]['energy'],'go-')
-  for i in range(24,36):
-    plt.plot(df.iloc[[24,i]][parm],df.iloc[[24,i]]['energy'],'ro-')
-  for i in range(36,48):
-    plt.plot(df.iloc[[36,i]][parm],df.iloc[[36,i]]['energy'],'ko-')
-  plt.show()
-  return 
-plot_parm('sigNps')
-exit(0)
-'''
+#exit(0)
 
 #PAIRPLOTS
-#sns.pairplot(df,vars=['energy','sigNdpi','sigNdz','sigNpp','sigNpz'],hue='basestate')
-#sns.pairplot(df,vars=['energy','sigN2s','sigNdz2'],hue='basestate')
-#sns.pairplot(df,vars=['energy','sigNps','sigNd','sigN4s'],hue='basestate')
-#sns.pairplot(df,vars=['energy','sigTd','sigT','sigU','sigJ'],hue='basestate')
-#sns.pairplot(df,vars=['energy','sigT','sigTd','sigJ','sigNps'],hue='basestate')
-#sns.pairplot(df,vars=['energy','sigN4s','sigU','sigNd'],hue='basestate')
-sns.pairplot(df,vars=['sigNps','sigN4s','sigTdp','sigTps','sigUd','sigUp','sigUs'],hue='basestate')
[…]

### 2019-04-09 doped_fv/PBE0/scf/gather_sd.py

@@ -9,125 +9,99 @@ from pyscf import lo
 from functools import reduce 
 from downfold_tools import gen_slater_tbdm,sum_onebody,sum_J,sum_U
 import seaborn as sns 
+import itertools 
 
 a=np.load('pickles/iao_g.pickle')
-
+b=np.load('pickles/UNPOL_mo_coeff_g.pickle')[0][[55,65,66,67,68,69,70,71]].T
 df=None
-direcs=['FLP']*12+['COL']*12+['COL2']*12+['FM']*12
-base_energy=[0]*12+[0.16]*12+[0.19]*12+[0.38]*12
-rem=[[[],[]],
-     [[66],[]],
-     [[66],[]],
-     [[66],[]],
-     [[66],[]],
-     [[66],[]],
-     [[],[65]],
-     [[],[65]],
-     [[],[65]],
-     [[],[65]],
-     [[],[65]],
-     [[],[65]],
-     [[],[]],
-     [[66],[]],
-     [[66],[]],
-     [[66],[]],
-     [[66],[]],
-     [[66],[]],
-     [[],[65]],
-     [[],[65]],
-     [[],[65]],
-     [[],[65]],
-     [[],[65]],
-     [[],[65]],
-     [[],[]],
-     [[66],[]],
-     [[66],[]],
-     [[66],[]],
-     [[66],[]],
-     [[66],[]],
-     [[],[65]],
-     [[],[65]],
-     [[],[65]],
-     [[],[65]],
-     [[],[65]],
-     [[],[65]],
-     [[],[]],
-     [[67],[]],
-     [[67],[]],
-     [[67],[]],
-     [[67],[]],
-     [[],[64]],
-     [[],[64]],
-     [[],[64]],
-     [[],[64]],
-     [[],[64]],
-     [[],[64]],
-     [[],[64]]]
-add=[[[],[]],
-     [[67],[]],
-     [[68],[]],
-     [[69],[]],
-     [[70],[]],
-     [[71],[]],
-     [[],[66]],
-     [[],[67]],
-     [[],[68]],
-     [[],[69]],
-     [[],[70]],
-     [[],[71]],
-     [[],[]], 
-     [[67],[]],
-     [[68],[]],
-     [[69],[]],
-     [[70],[]],
-     [[71],[]],
-     [[],[66]],
-     [[],[67]],
[…]

### 2019-04-09 doped_fv/PBE0/scf/project_unpol.py

@@ -6,7 +6,7 @@ import matplotlib.pyplot as plt
 
 #Project active pol onto unpolarized
 zz=0
-base_coeff=pd.read_pickle('pickles/FLP_mo_coeff_g.pickle')
+base_coeff=pd.read_pickle('pickles/UNPOL_mo_coeff_g.pickle')
 s=pd.read_pickle('pickles/FLP_s_g.pickle')
 comp = ['FLP','COL','COL2','FM']
 for spin in [0,1]:
@@ -24,12 +24,12 @@ for spin in [0,1]:
       act=np.arange(66,73)-1
       if(comp_f=='FM'): act=np.arange(65,73)-1
     plt.subplot(410+zz)
-    plt.matshow(comp_matrix[spin,act,:72],vmax=1,vmin=-1,cmap=plt.cm.bwr,fignum=False)
+    plt.matshow(comp_matrix[spin,act,:],vmax=1,vmin=-1,cmap=plt.cm.bwr,fignum=False)
     plt.ylabel(comp_f)
-    plt.xlabel('FLP')
+    plt.xlabel('Unpol')
   plt.suptitle('Active bands S='+str(spin))
-  plt.show()
-  #plt.savefig('plots/act_unpol_s'+str(spin)+'.pdf',bbox_inches='tight')
+  #plt.show()
+  plt.savefig('plots/act_unpol_s'+str(spin)+'_full.pdf',bbox_inches='tight')
 
 '''
 #Project active unpol to polarized

### 2019-04-09 doped_fv/PBE0/COL_ns/plot_bands2.py
re-running gather_sd,  had a bug in unpol basis

@@ -40,15 +40,26 @@ for p in panels:
   ax.annotate(p[1],xy=(p[0],0.0),ha='center',fontsize=9)
 ax.axhline(0.0,color='gray',linestyle="--")
 conv=27.2116
-for b in range(65,70):
-  ax.plot(range(1,nkpt+1),conv*bands[0][:,b],color='k')
-  ax.plot(range(1,nkpt+1),conv*bands[1][:,b],color='r')
-  print(conv*bands[1][:,b])
-'''
-P.ylim([-2,2])
+for b in range(1,80):
+  if(bands[0][0,b]<0): print(b,"spin up")
+  if(bands[1][0,b]<0): print(b,"spin down")
+  ax.annotate(str(b), xy=(0, conv*bands[0][0,b]),fontsize=14, color='k')
+  ax.annotate(str(b), xy=(120, conv*bands[1][-1,b]),fontsize=14, color='r')
+  #ax.annotate(0, conv*bands[1][0,b], str(b), transform=ax.transAxes, fontsize=14,
+  #        verticalalignment='top', color='r')
+  ax.plot(range(1,nkpt+1),conv*bands[0][:,b],color='k')#,ls='--')
+  ax.plot(range(1,nkpt+1),conv*bands[1][:,b],color='r')#,ls='--')
+  '''
+  if(b==66): ax.plot(range(1,nkpt+1),conv*bands[1][:,b],color='r')
+  if(b==67): 
+    ax.plot(range(1,nkpt+1),conv*bands[0][:,b],color='k')
+    ax.plot(range(1,nkpt+1),conv*bands[1][:,b],color='r')
+  if(b==68): ax.plot(range(1,nkpt+1),conv*bands[0][:,b],color='k')
+  if(b==69): ax.plot(range(1,nkpt+1),conv*bands[1][:,b],color='r')
+  '''
+P.ylim([-10,10])
 P.ylabel("Energy (eV) ")
 if len(sys.argv) < 2: 
   P.show()
 else:
   P.savefig(sys.argv[1])
-'''

### 2019-04-09 doped_fv/PBE0/FLP_ns/plot_bands2.py

@@ -40,13 +40,26 @@ for p in panels:
   ax.annotate(p[1],xy=(p[0],0.0),ha='center',fontsize=9)
 ax.axhline(0.0,color='gray',linestyle="--")
 conv=27.2116
-for b in range(66,nband):
-  ax.plot(range(1,nkpt+1),conv*bands[0][:,b],color='k')
-  ax.plot(range(1,nkpt+1),conv*bands[1][:,b],color='r')
-P.ylim([-2,2])
+for b in range(1,80):
+  if(bands[0][0,b]<0): print(b,"spin up")
+  if(bands[1][0,b]<0): print(b,"spin down")
+  ax.annotate(str(b), xy=(0, conv*bands[0][0,b]),fontsize=14, color='k')
+  ax.annotate(str(b), xy=(120, conv*bands[1][-1,b]),fontsize=14, color='r')
+  #ax.annotate(0, conv*bands[1][0,b], str(b), transform=ax.transAxes, fontsize=14,
+  #        verticalalignment='top', color='r')
+  ax.plot(range(1,nkpt+1),conv*bands[0][:,b],color='k')#,ls='--')
+  ax.plot(range(1,nkpt+1),conv*bands[1][:,b],color='r')#,ls='--')
+  '''
+  if(b==66): ax.plot(range(1,nkpt+1),conv*bands[1][:,b],color='r')
+  if(b==67): 
+    ax.plot(range(1,nkpt+1),conv*bands[0][:,b],color='k')
+    ax.plot(range(1,nkpt+1),conv*bands[1][:,b],color='r')
+  if(b==68): ax.plot(range(1,nkpt+1),conv*bands[0][:,b],color='k')
+  if(b==69): ax.plot(range(1,nkpt+1),conv*bands[1][:,b],color='r')
+  '''
+P.ylim([-10,10])
 P.ylabel("Energy (eV) ")
 if len(sys.argv) < 2: 
   P.show()
 else:
   P.savefig(sys.argv[1])
-

### 2019-04-09 doped_fv/PBE0/scf/analyze_sd.py

@@ -7,31 +7,36 @@ from statsmodels.sandbox.regression.predstd import wls_prediction_std
 from sklearn.decomposition import PCA
 
 df=pd.read_pickle('pickles/full_sd_gosling.pickle')
+
+#TRACE CHECK
 df['tr']=df['Nd']+df['Ns']+df['Np']
 df['tr_group']=0
 df['tr_group'][df['tr']<=20.7]=-1
 df['tr_group'][df['tr']>=21]=1
 
-for g in [-1,0,1]:
-  ind=np.where(df['tr_group'].values==g)[0]
-  print(ind)
-exit(0)
+df['tr_unp']=df['N0']+df['N1']+df['N2']+df['N3']+df['N4']+df['N5']+df['N6']+df['N7']
 
+#"BAD" EXCITATIONS
+#for g in [-1,0,1]:
+#  ind=np.where(df['tr_group'].values==g)[0]
+#  print(ind)
+#exit(0)
+
+#VARIANCES
 var=df.var()
 ind=np.argsort(var.values)
 print(var.iloc[ind])
 #exit(0)
 
 #PAIRPLOTS
-#sns.pairplot(df,vars=['energy','tr'],hue='tr_group')
+sns.pairplot(df,vars=['energy','tr','tr_unp'],hue='tr_group')
 #sns.pairplot(df,vars=['energy','tr','Ndz2','Ndz','Ndpi','Npz','Npp','N2s'],hue='tr_group')
-#df['tr2']=df['tr']+df['Ndz2']
-#sns.pairplot(df,vars=['energy','tr','tr2'],hue='tr_group')
 #sns.pairplot(df,vars=['energy','Np','Ns','sigTdp','sigTps','sigTds','sigUd','sigUp','sigUs'],hue='basestate')
 #plt.savefig('HubbardPPIAO_full.pdf',bbox_inches='tight')
-#plt.show()
-#exit(0)
+plt.show()
+exit(0)
 
+'''
 #REGRESSION
 select_df=df
 y=select_df['energy']
@@ -54,9 +59,4 @@ g.map(plt.errorbar, "pred", "energy", "energy_err",fmt='o').add_legend()
 plt.plot(select_df['energy'],select_df['energy'],'k--')
 plt.show()
 exit(0)
-
-#plt.plot(ols.predict(),y,'bo')
-#for i in range(len(y)):
[…]

### 2019-04-09 doped_fv/PBE0/scf/analyze_sd_mo.py

@@ -1,117 +1,0 @@
-import numpy as np 
-import seaborn as sns
-import matplotlib.pyplot as plt 
-import pandas as pd
-import statsmodels.api as sm
-from statsmodels.sandbox.regression.predstd import wls_prediction_std
-from sklearn.decomposition import PCA
-from functools import reduce 
-from sklearn.linear_model import OrthogonalMatchingPursuit
-
-#########################################################################################
-#REDUCING
-df=pd.read_pickle('pickles/sd_gosling_mo.pickle')
-#df=df.iloc[[0,1,2,6,7,8,12,13,14,18,16,20,24,25,26,30,31,32,36,37,41,42,43,44]] #No 70,71,72
-#df=df.iloc[[0,12,24,36]] #Spin states only
-
-df['sigN_65_65']+=df['sigN_66_66']
-df['sigN_69_69']+=df['sigN_70_70']
-df=df.drop(columns=['sigN_66_66','sigN_70_70'])
-
-df['sigT_0_1']+=df['sigT_0_2']
-df['sigT_0_5']+=df['sigT_0_6']
-df['sigT_1_3']+=df['sigT_2_3']
-df['sigT_1_4']+=df['sigT_2_4']
-df['sigT_1_5']+=df['sigT_1_6']+df['sigT_2_5']+df['sigT_2_6']
-df['sigT_1_7']+=df['sigT_2_7']
-df['sigT_3_5']+=df['sigT_3_6']
-df['sigT_4_5']+=df['sigT_4_6']
-df['sigT_5_7']+=df['sigT_6_7']
-df=df.drop(columns=['sigT_1_2','sigT_5_6','sigT_0_2','sigT_0_6','sigT_2_3',
-'sigT_2_4','sigT_1_6','sigT_2_5','sigT_2_6','sigT_2_7','sigT_3_6','sigT_4_6','sigT_6_7'])
-
-'''
-#for i in [0,3,4,7]:
-#  df['sigT_'+str(i)+'_1']+=df['sigT_'+str(i)+'_2']
-#  df['sigT_'+str(i)+'_5']+=df['sigT_'+str(i)+'_6']
-#  df=df.drop(columns=['sigT_'+str(i)+'_2','sigT_'+str(i)+'_6'])
-
-##########################################################################################
-#ANALYSIS
[…]

### 2019-04-09 doped_fv/PBE0/scf/gather_sd.py

@@ -12,7 +12,7 @@ import seaborn as sns
 import itertools 
 
 a=np.load('pickles/iao_g.pickle')
-b=np.load('pickles/UNPOL_mo_coeff_g.pickle')[0][[55,65,66,67,68,69,70,71]].T
+b=np.load('pickles/UNPOL_mo_coeff_g.pickle')[0][:,[55,65,66,67,68,69,70,71]]
 df=None
 
 #Generates doubles excitations given 

### 2019-04-09 doped_fv/PBE0/scf/gather_sd_mo.py

@@ -1,181 +1,0 @@
-#Collect single determinant excitations
-import numpy as np 
-import pandas as pd
-import matplotlib.pyplot as plt
-from crystal2pyscf import crystal2pyscf_cell
-from pyscf2qwalk import print_qwalk_pbc
-from basis import basis, minbasis, basis_order
-from pyscf import lo
-from functools import reduce 
-from downfold_tools import gen_slater_tbdm,sum_onebody,sum_J,sum_U
-import seaborn as sns 
-
-a=np.load('pickles/UNPOL_mo_coeff_g.pickle')[0]
-a=a[:,:72]
-b=np.load('pickles/iao_g.pickle')
-
-df=None
-basestate=[0]*12+[1]*12+[2]*12+[3]*12
-direcs=['FLP']*12+['COL']*12+['COL2']*12+['FM']*12
-base_energy=[0]*12+[0.16]*12+[0.19]*12+[0.38]*12
-rem=[[[],[]],
-     [[66],[]],
-     [[66],[]],
-     [[66],[]],
-     [[66],[]],
-     [[66],[]],
-     [[],[65]],
-     [[],[65]],
-     [[],[65]],
-     [[],[65]],
-     [[],[65]],
-     [[],[65]],
-     [[],[]],
-     [[66],[]],
-     [[66],[]],
-     [[66],[]],
-     [[66],[]],
-     [[66],[]],
-     [[],[65]],
-     [[],[65]],
-     [[],[65]],
-     [[],[65]],
-     [[],[65]],
-     [[],[65]],
-     [[],[]],
-     [[66],[]],
-     [[66],[]],
-     [[66],[]],
-     [[66],[]],
-     [[66],[]],
-     [[],[65]],
-     [[],[65]],
-     [[],[65]],
-     [[],[65]],
-     [[],[65]],
-     [[],[65]],
-     [[],[]],
-     [[67],[]],
-     [[67],[]],
-     [[67],[]],
-     [[67],[]],
-     [[],[64]],
-     [[],[64]],
-     [[],[64]],
-     [[],[64]],
-     [[],[64]],
-     [[],[64]],
-     [[],[64]]]
-add=[[[],[]],
-     [[67],[]],
[…]
